---
output:
  pdf_document:
     latex_engine: xelatex
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

---

# **Supplement Section A: Descriptive Statistics**

## **• A1: Stimuli acquisition participant demographics**
## **• A2: Rating session participant demographics**
## **• A3: Effect Size Interpretation Guidelines**

#### **In the .Pdf output file you may find only the outputs generated by the analysis code, in order to keep the supplementary files as concise as possible. However the full code is available on https://github.com/Rezvani-S/Costly-Beauty-ShoeStudy.git**
---

```{r libraries, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

## **Part I: Stimuli acquisition Participant Demographics**

```{r Stimuli acquisition-load}
# Load Study 1 data
df1 <- read.csv("Stimuli acquisition participant demographics.csv", sep = ";", stringsAsFactors = FALSE, skip = 1)

colnames(df1) <- c("recruitment", "age", "height", "weight", "nationality", 
                   "sex", "gender", "education", "municipality", "income", 
                   "sexual_orientation", "relationship_status")

# Clean data
df1$age <- as.numeric(df1$age)
df1$height <- as.numeric(df1$height)
df1$height[df1$height < 100] <- NA
df1$weight <- as.numeric(df1$weight)
df1$nationality <- trimws(df1$nationality)
df1$nationality[grepl("Ukrainain", df1$nationality)] <- "Ukrainian"
df1$relationship_status[grepl("NeCommitted", df1$relationship_status)] <- "Non-committed relationship"
df1$sexual_orientation <- iconv(df1$sexual_orientation, from = "UTF-8", to = "ASCII", sub = "")
df1$sexual_orientation[grepl("Homosex", df1$sexual_orientation)] <- "Homosexual"
df1$bmi <- df1$weight / ((df1$height / 100) ^ 2)
```

### Table A1.1: Stimuli acquisition Participant Characteristics

```{r Stimuli acquisition-demographics}
# Create comprehensive demographics table
demo_table1 <- data.frame(
  Variable = c(
    "Sample size",
    "Age (years)",
    "Height (cm)",
    "Weight (kg)",
    "BMI",
    "Sex - Female",
    "Sex - Male",
    "Nationality - Czech",
    "Nationality - Slovak",
    "Nationality - Other",
    "Education - Secondary school",
    "Education - Bachelor's degree",
    "Education - Master's degree",
    "Education - Basic",
    "Sexual Orientation - Heterosexual",
    "Sexual Orientation - Bisexual",
    "Sexual Orientation - Homosexual",
    "Sexual Orientation - Other/Unknown",
    "Relationship - Committed relationship",
    "Relationship - Single",
    "Relationship - Marriage/Partnership",
    "Relationship - Non-committed",
    "Municipality - City >100k",
    "Municipality - Other",
    "Income - Up to 15k CZK",
    "Income - 15-30k CZK",
    "Income - 30-50k CZK"
  ),
  
  `N or M` = c(
    nrow(df1),
    round(mean(df1$age, na.rm = TRUE), 2),
    round(mean(df1$height, na.rm = TRUE), 2),
    round(mean(df1$weight, na.rm = TRUE), 2),
    round(mean(df1$bmi, na.rm = TRUE), 2),
    sum(df1$sex == "Female", na.rm = TRUE),
    sum(df1$sex == "Male", na.rm = TRUE),
    sum(df1$nationality == "Czech", na.rm = TRUE),
    sum(df1$nationality == "Slovak", na.rm = TRUE),
    sum(!df1$nationality %in% c("Czech", "Slovak") & !is.na(df1$nationality)),
    sum(grepl("Secondary school", df1$education, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("bachelor", df1$education, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("master", df1$education, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("Basic", df1$education, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("Heterosexual", df1$sexual_orientation, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("Bisexual", df1$sexual_orientation, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("Homosexual", df1$sexual_orientation, ignore.case = TRUE), na.rm = TRUE),
    sum(!grepl("Heterosexual|Bisexual|Homosexual", df1$sexual_orientation, ignore.case = TRUE) | 
        is.na(df1$sexual_orientation) | df1$sexual_orientation == ""),
    sum(grepl("Committed", df1$relationship_status) & !grepl("Non-committed", df1$relationship_status), na.rm = TRUE),
    sum(grepl("Single", df1$relationship_status), na.rm = TRUE),
    sum(grepl("Marriage|partnership", df1$relationship_status, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("Non-committed", df1$relationship_status), na.rm = TRUE),
    sum(grepl("100 000", df1$municipality), na.rm = TRUE),
    sum(!grepl("100 000", df1$municipality) & !is.na(df1$municipality)),
    sum(grepl("up to 15", df1$income, ignore.case = TRUE), na.rm = TRUE),
    sum(grepl("15,000-30,000", df1$income), na.rm = TRUE),
    sum(grepl("30,000-50,000", df1$income), na.rm = TRUE)
  ),
  
  `% or SD` = c(
    "",
    paste0("(", round(sd(df1$age, na.rm = TRUE), 2), ")"),
    paste0("(", round(sd(df1$height, na.rm = TRUE), 2), ")"),
    paste0("(", round(sd(df1$weight, na.rm = TRUE), 2), ")"),
    paste0("(", round(sd(df1$bmi, na.rm = TRUE), 2), ")"),
    paste0(round(sum(df1$sex == "Female", na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(df1$sex == "Male", na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(df1$nationality == "Czech", na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(df1$nationality == "Slovak", na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(!df1$nationality %in% c("Czech", "Slovak") & !is.na(df1$nationality))/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Secondary school", df1$education, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("bachelor", df1$education, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("master", df1$education, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Basic", df1$education, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Heterosexual", df1$sexual_orientation, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Bisexual", df1$sexual_orientation, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Homosexual", df1$sexual_orientation, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(!grepl("Heterosexual|Bisexual|Homosexual", df1$sexual_orientation, ignore.case = TRUE) | 
        is.na(df1$sexual_orientation) | df1$sexual_orientation == "")/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Committed", df1$relationship_status) & !grepl("Non-committed", df1$relationship_status), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Single", df1$relationship_status), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Marriage|partnership", df1$relationship_status, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("Non-committed", df1$relationship_status), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("100 000", df1$municipality), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(!grepl("100 000", df1$municipality) & !is.na(df1$municipality))/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("up to 15", df1$income, ignore.case = TRUE), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("15,000-30,000", df1$income), na.rm = TRUE)/nrow(df1)*100, 1), "%"),
    paste0(round(sum(grepl("30,000-50,000", df1$income), na.rm = TRUE)/nrow(df1)*100, 1), "%")
  ),
  
  Range = c(
    "",
    paste0(min(df1$age, na.rm = TRUE), "-", max(df1$age, na.rm = TRUE)),
    paste0(min(df1$height, na.rm = TRUE), "-", max(df1$height, na.rm = TRUE)),
    paste0(min(df1$weight, na.rm = TRUE), "-", max(df1$weight, na.rm = TRUE)),
    paste0(round(min(df1$bmi, na.rm = TRUE), 2), "-", round(max(df1$bmi, na.rm = TRUE), 2)),
    rep("", 22)
  )
)

kable(demo_table1, 
      col.names = c("Variable", "N or M", "% or SD", "Range"),
      caption = "Stimuli acquisition Participant Demographics (N = 60)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), latex_options = "hold_position") %>%
  pack_rows("Demographics", 1, 5) %>%
  pack_rows("Sex", 6, 7) %>%
  pack_rows("Nationality", 8, 10) %>%
  pack_rows("Education", 11, 14) %>%
  pack_rows("Sexual Orientation", 15, 18) %>%
  pack_rows("Relationship Status", 19, 22) %>%
  pack_rows("Municipality", 23, 24) %>%
  pack_rows("Income", 25, 27)
```

### Table A1.2: Stimuli acquisition Missing Data

```{r Stimuli acquisition-missing}
missing1 <- df1 %>%
  summarise_all(~sum(is.na(.) | . == "")) %>%
  gather(key = "Variable", value = "Missing_Count") %>%
  mutate(Missing_Percentage = round((Missing_Count / nrow(df1)) * 100, 2)) %>%
  filter(Missing_Count > 0) %>%
  arrange(desc(Missing_Count))

if(nrow(missing1) == 0) {
  missing1 <- data.frame(Variable = "No missing data", Missing_Count = 0, Missing_Percentage = 0)
}

kable(missing1, caption = "Stimuli acquisition Missing Data Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), latex_options = "hold_position")
```

\newpage

## **Part II: Rating session Participant Demographics**

```{r Rating session-load}
# Load Study 2 data
df2 <- read.csv("Rating session participant demographics.csv", sep = ";", stringsAsFactors = FALSE)

# Clean partnership status
df2$partnershipstatus_clean <- df2$partnershipstatus
df2$partnershipstatus_clean[is.na(df2$partnershipstatus_clean) | 
                          df2$partnershipstatus_clean == "" | 
                          df2$partnershipstatus_clean == "NA"] <- NA

df2$partnershipstatus_clean <- case_when(
  is.na(df2$partnershipstatus_clean) ~ NA_character_,
  grepl("Single.*no partner", df2$partnershipstatus_clean, ignore.case = TRUE) ~ "Single (no partner)",
  grepl("Serious relationship", df2$partnershipstatus_clean, ignore.case = TRUE) ~ "Serious relationship", 
  grepl("Marriage.*registered", df2$partnershipstatus_clean, ignore.case = TRUE) ~ "Marriage/registered partnership",
  grepl("non-binding", df2$partnershipstatus_clean, ignore.case = TRUE) ~ "Non-binding relationship",
  grepl("Nez", df2$partnershipstatus_clean) | grepl("vztah", df2$partnershipstatus_clean) ~ "Non-binding relationship",
  TRUE ~ "Other"
)
```

### Table A2.1: Rating session Participant Characteristics

```{r Rating session-demographics}
# Create comprehensive demographics table
demo_table2 <- data.frame(
  Variable = c(
    "Sample size",
    "Age (years)",
    "Sex - Female",
    "Sex - Male",
    "Nationality - Czech",
    "Nationality - Slovak",
    "Nationality - Other",
    "Education - High school",
    "Education - Bachelor's degree",
    "Education - Master's degree",
    "Education - Ph.D. degree",
    "Education - Elementary school",
    "Education - Other",
    "Sexual Orientation - Exclusively heterosexual",
    "Sexual Orientation - Predominantly heterosexual",
    "Sexual Orientation - Bisexual",
    "Sexual Orientation - Rather heterosexual",
    "Sexual Orientation - Exclusively homosexual",
    "Sexual Orientation - Rather homosexual",
    "Sexual Orientation - Predominantly homosexual",
    "Partnership - Serious relationship",
    "Partnership - Single (no partner)",
    "Partnership - Non-binding relationship",
    "Partnership - Marriage/registered partnership",
    "Partnership - Other",
    "Residence - Large city (>100k)",
    "Residence - Other",
    "Income - Up to 15k CZK",
    "Income - 15-30k CZK",
    "Income - 30-50k CZK",
    "Income - Over 50k CZK",
    "Survey Duration (minutes)"
  ),
  
  `N or M` = c(
    nrow(df2),
    round(mean(df2$age_clean, na.rm = TRUE), 2),
    sum(df2$sex_clean == "Female", na.rm = TRUE),
    sum(df2$sex_clean == "Male", na.rm = TRUE),
    sum(df2$Nationality == "Czech", na.rm = TRUE),
    sum(df2$Nationality == "Slovak", na.rm = TRUE),
    sum(!df2$Nationality %in% c("Czech", "Slovak") & !is.na(df2$Nationality)),
    sum(df2$education_clean == "High school", na.rm = TRUE),
    sum(df2$education_clean == "Bachelor's degree", na.rm = TRUE),
    sum(df2$education_clean == "Master's degree", na.rm = TRUE),
    sum(df2$education_clean == "Ph.D. degree", na.rm = TRUE),
    sum(df2$education_clean == "Elementary school", na.rm = TRUE),
    sum(df2$education_clean == "Other", na.rm = TRUE),
    sum(df2$sexualorientation == "Exclusively heterosexual", na.rm = TRUE),
    sum(df2$sexualorientation == "Predominantly heterosexual", na.rm = TRUE),
    sum(df2$sexualorientation == "Bisexual", na.rm = TRUE),
    sum(df2$sexualorientation == "Rather heterosexual", na.rm = TRUE),
    sum(df2$sexualorientation == "Exclusively homosexual", na.rm = TRUE),
    sum(df2$sexualorientation == "Rather homosexual", na.rm = TRUE),
    sum(df2$sexualorientation == "Predominantly homosexual", na.rm = TRUE),
    sum(df2$partnershipstatus_clean == "Serious relationship", na.rm = TRUE),
    sum(df2$partnershipstatus_clean == "Single (no partner)", na.rm = TRUE),
    sum(df2$partnershipstatus_clean == "Non-binding relationship", na.rm = TRUE),
    sum(df2$partnershipstatus_clean == "Marriage/registered partnership", na.rm = TRUE),
    sum(df2$partnershipstatus_clean == "Other", na.rm = TRUE),
    sum(grepl("100 000", df2$residence), na.rm = TRUE),
    sum(!grepl("100 000", df2$residence) & !is.na(df2$residence)),
    sum(df2$monthlyincome == "up to 15 000 CZK/month", na.rm = TRUE),
    sum(df2$monthlyincome == "15 000-30 000 CZK/month", na.rm = TRUE),
    sum(df2$monthlyincome == "30 000-50 000 CZK/month", na.rm = TRUE),
    sum(df2$monthlyincome == "over 50 000 CZK/month", na.rm = TRUE),
    round(mean(df2$Durationinseconds, na.rm = TRUE) / 60, 2)
  ),
  
  `% or SD` = c(
    "",
    paste0("(", round(sd(df2$age_clean, na.rm = TRUE), 2), ")"),
    paste0(round(sum(df2$sex_clean == "Female", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sex_clean == "Male", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$Nationality == "Czech", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$Nationality == "Slovak", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(!df2$Nationality %in% c("Czech", "Slovak") & !is.na(df2$Nationality))/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$education_clean == "High school", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$education_clean == "Bachelor's degree", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$education_clean == "Master's degree", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$education_clean == "Ph.D. degree", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$education_clean == "Elementary school", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$education_clean == "Other", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sexualorientation == "Exclusively heterosexual", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sexualorientation == "Predominantly heterosexual", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sexualorientation == "Bisexual", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sexualorientation == "Rather heterosexual", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sexualorientation == "Exclusively homosexual", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sexualorientation == "Rather homosexual", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$sexualorientation == "Predominantly homosexual", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$partnershipstatus_clean == "Serious relationship", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$partnershipstatus_clean == "Single (no partner)", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$partnershipstatus_clean == "Non-binding relationship", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$partnershipstatus_clean == "Marriage/registered partnership", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$partnershipstatus_clean == "Other", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(grepl("100 000", df2$residence), na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(!grepl("100 000", df2$residence) & !is.na(df2$residence))/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$monthlyincome == "up to 15 000 CZK/month", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$monthlyincome == "15 000-30 000 CZK/month", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$monthlyincome == "30 000-50 000 CZK/month", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0(round(sum(df2$monthlyincome == "over 50 000 CZK/month", na.rm = TRUE)/nrow(df2)*100, 1), "%"),
    paste0("(", round(sd(df2$Durationinseconds, na.rm = TRUE) / 60, 2), ")")
  ),
  
  Range = c(
    "",
    paste0(min(df2$age_clean, na.rm = TRUE), "-", max(df2$age_clean, na.rm = TRUE)),
    rep("", 30)
  )
)

kable(demo_table2, 
      col.names = c("Variable", "N or M", "% or SD", "Range"),
      caption = "Rating session Participant Demographics (N = 279)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), latex_options = "hold_position", 
                font_size = 10) %>%
  pack_rows("Demographics", 1, 2) %>%
  pack_rows("Sex", 3, 4) %>%
  pack_rows("Nationality", 5, 7) %>%
  pack_rows("Education", 8, 13) %>%
  pack_rows("Sexual Orientation", 14, 20) %>%
  pack_rows("Partnership Status", 21, 25) %>%
  pack_rows("Residence", 26, 27) %>%
  pack_rows("Income", 28, 31) %>%
  pack_rows("Survey Completion", 32, 32)
```

### Table A2.2: Rating session Missing Data

```{r Rating session-missing}
missing2 <- df2 %>%
  summarise_all(~sum(is.na(.) | . == "")) %>%
  gather(key = "Variable", value = "Missing_Count") %>%
  mutate(Missing_Percentage = round((Missing_Count / nrow(df2)) * 100, 2)) %>%
  filter(Missing_Count > 0) %>%
  arrange(desc(Missing_Count))

if(nrow(missing2) == 0) {
  missing2 <- data.frame(Variable = "No missing data", Missing_Count = 0, Missing_Percentage = 0)
}

kable(missing2, caption = "Rating session Missing Data Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), latex_options = "hold_position")
```

\newpage

## **Part III: Effect Size Interpretation Guidelines**

### Effect Size Interpretation

Effect size interpretations in this study follow empirically-derived guidelines from individual differences research rather than Cohen's (1988) conventional benchmarks. Cohen's original thresholds (*d* = 0.20/0.50/0.80 for small/medium/large) were based on subjective impression rather than empirical data and have been shown to overestimate typical effect sizes in psychological research (Lovakov & Agadullina, 2021).

We adopted the guidelines proposed by Gignac and Szodorai (2016), who analyzed 708 effect sizes from individual differences research and recommended interpreting correlations of *r* = 0.10, 0.20, and 0.30 as small, medium, and large, respectively. Converting these correlation benchmarks to Cohen's *d* using the formula *d* = 2*r*/√(1-*r*²), we interpret effect sizes as follows: *d* = 0.22-0.39 as small, *d* = 0.40-0.59 as medium, and *d* ≥ 0.60 as large. Effect sizes below *d* = 0.22 are characterized as "very small."

This choice of guidelines is particularly appropriate given that our study examines individual differences in perceptual ratings. Gignac and Szodorai's (2016) benchmarks reflect the magnitude of effects commonly observed when measuring stable individual differences in psychological constructs, which aligns with our investigation of how individuals differ in their perceptions of attractiveness and wealth based on appearance cues.

Additionally, as our study was pre-registered, it is important to contextualize our findings within the broader literature on publication bias and effect size inflation. Schäfer and Schwarz (2019) demonstrated that studies without pre-registration show substantially inflated effect sizes (median *r* = 0.36) compared to pre-registered studies (median *r* = 0.16), suggesting that publication bias approximately doubles observed effects. Our pre-registered design likely yields more accurate estimates, and the relatively small effects we observed should be interpreted as more reliable indicators of true effect magnitudes.

```{r effect-size-table, echo=FALSE}
# Create effect size interpretation table
effect_size_table <- data.frame(
  `Effect Size (d)` = c("< 0.22", "0.22 - 0.39", "0.40 - 0.59", "≥ 0.60"),
  `Interpretation` = c("Very small", "Small", "Medium", "Large"),
  `Equivalent r` = c("< 0.11", "0.11 - 0.19", "0.20 - 0.29", "≥ 0.30"),
  `Basis` = c(
    "Below Gignac & Szodorai (2016) small threshold",
    "Gignac & Szodorai (2016) small effect",
    "Gignac & Szodorai (2016) medium effect",
    "Gignac & Szodorai (2016) large effect"
  )
)

kable(effect_size_table, 
      col.names = c("Effect Size (d)", "Interpretation", "Equivalent r", "Basis"),
      caption = "Effect Size Interpretation Guidelines for Individual Differences Research") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), latex_options = "hold_position")
```

### References

Cohen, J. (1988). *Statistical power analysis for the behavioral sciences* (2nd ed.). Lawrence Erlbaum Associates.

Gignac, G. E., & Szodorai, E. T. (2016). Effect size guidelines for individual differences researchers. *Personality and Individual Differences*, *102*, 74–78. https://doi.org/10.1016/j.paid.2016.06.069

Lovakov, A., & Agadullina, E. R. (2021). Empirically derived guidelines for effect size interpretation in social psychology. *European Journal of Social Psychology*, *51*(3), 485–504. https://doi.org/10.1002/ejsp.2752

Schäfer, T., & Schwarz, M. A. (2019). The meaningfulness of effect sizes in psychological research: Differences between sub-disciplines and the impact of potential biases. *Frontiers in Psychology*, *10*, 813. https://doi.org/10.3389/fpsyg.2019.00813
