---
output:
  pdf_document:
     latex_engine: xelatex
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
```

---

# **Supplement Secion A: Descriptive Statistics**
## In this document;

## **•	A1:** Study 1 (stimuli generation) participant demographics
## **•	A2:** Study 2 (raning session) participant demographics

#### **In the .Pdf output file you may find only the outputs generated by the analysis code, in order to keep the supplementary files as concise as possible. However the full code is available on https://github.com/Rezvani-S/Costly-Beauty-ShoeStudy.git**


1. ### loading required packages

```{r libraries}
# Load required libraries
library(tidyverse)
library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)
library(plotly)
library(corrplot)
library(VIM)
library(psych)
library(gridExtra)

# Set theme for plots
theme_set(theme_minimal() + 
          theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
                axis.text = element_text(size = 10),
                legend.position = "bottom"))
```


## **Part I: Supplementary	A1: Descriptive statistics of the demographic data of Study 1 (stimuli generation) participants **

### 2. Loading and preparing the data 
```{r}
# Load the dataset
df <- read.csv("Study 1 Demographics.csv", sep = ";", stringsAsFactors = FALSE, skip = 1)

# Rename columns for easier handling
colnames(df) <- c("recruitment", "age", "height", "weight", "nationality", 
                  "sex", "gender", "education", "municipality", "income", 
                  "sexual_orientation", "relationship_status")
# Display basic dataset information
cat("Dataset Dimensions:", nrow(df), "rows x", ncol(df), "columns\n")

# Data Structure
str(df)
```

### 3. Missing data
```{r}
# Calculate missing values
missing_summary <- df %>%
  summarise_all(~sum(is.na(.) | . == "")) %>%
  gather(key = "Variable", value = "Missing_Count") %>%
  mutate(Missing_Percentage = round((Missing_Count / nrow(df)) * 100, 2)) %>%
  arrange(desc(Missing_Count))

# Display missing data table
kable(missing_summary, caption = "Missing Data Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualize missing data pattern
VIM::aggr(df, col = c('navyblue','red'), numbers = TRUE, sortVars = TRUE)

```

### 4. Cleaning data

```{r}
# Clean age data
df$age <- as.numeric(df$age)

# Clean height data (fix obvious errors)
df$height <- as.numeric(df$height)
df$height[df$height < 100] <- NA  # Remove impossible values

# Clean weight data
df$weight <- as.numeric(df$weight)

# Clean nationality (standardize spelling)
df$nationality <- trimws(df$nationality)
df$nationality[grepl("Ukrainain", df$nationality)] <- "Ukrainian"

# Clean relationship status (standardize categories)
df$relationship_status[grepl("NeCommitted", df$relationship_status)] <- "Non-committed relationship"
df$relationship_status <- gsub("\\(without a partner\\)", "(no partner)", df$relationship_status)

# Clean sexual orientation (handle UTF-8 issues)
df$sexual_orientation <- iconv(df$sexual_orientation, from = "UTF-8", to = "ASCII", sub = "")
df$sexual_orientation[grepl("Homosex", df$sexual_orientation)] <- "Homosexual"
```

### 5. Demographics

### Age
```{r}
# Age statistics
age_stats <- df %>%
  summarise(
    Mean = round(mean(age, na.rm = TRUE), 2),
    Median = median(age, na.rm = TRUE),
    SD = round(sd(age, na.rm = TRUE), 2),
    Min = min(age, na.rm = TRUE),
    Max = max(age, na.rm = TRUE),
    Q1 = quantile(age, 0.25, na.rm = TRUE),
    Q3 = quantile(age, 0.75, na.rm = TRUE)
  )

kable(age_stats, caption = "Age Distribution Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Age distribution plot
ggplot(df, aes(x = age)) +
  geom_histogram(bins = 15, fill = "steelblue", alpha = 0.7, color = "white") +
  geom_vline(aes(xintercept = mean(age, na.rm = TRUE)), 
             color = "red", linetype = "dashed", size = 1) +
  labs(title = "Age Distribution", x = "Age", y = "Frequency") +
  annotate("text", x = mean(df$age, na.rm = TRUE) + 2, 
           y = max(table(df$age)) * 0.8,
           label = paste("Mean:", round(mean(df$age, na.rm = TRUE), 1)), 
           color = "red")
```

### Sex and Gender
```{r}
# Gender distribution
gender_dist <- df %>%
  count(gender) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(gender_dist, col.names = c("Gender", "Count", "Percentage (%)"),
      caption = "Gender Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Gender identity vs biological sex comparison
gender_comparison <- df %>%
  count(gender, sex) %>%
  spread(sex, n, fill = 0)

kable(gender_comparison, caption = "Gender Identity vs Biological Sex") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
ggplot(df, aes(x = sex, fill = sex)) +
  geom_bar(alpha = 0.8) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Sex Distribution", x = "Sex", y = "Count") +
  scale_fill_manual(values = c("Female" = "#E69F00", "Male" = "#56B4E9")) +
  theme(legend.position = "none")
```

### Nationality

```{r}
# Nationality distribution
nationality_dist <- df %>%
  count(nationality) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(nationality_dist, col.names = c("Nationality", "Count", "Percentage (%)"),
      caption = "Nationality Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
ggplot(df, aes(x = reorder(nationality, -table(nationality)[nationality]))) +
  geom_bar(fill = "coral", alpha = 0.8) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Nationality Distribution", x = "Nationality", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Education 
```{r}
# Education distribution
education_dist <- df %>%
  count(education) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(education_dist, col.names = c("Education Level", "Count", "Percentage (%)"),
      caption = "Education Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Sexual Orientation
```{r}
# Sexual orientation distribution
orientation_dist <- df %>%
  filter(!is.na(sexual_orientation) & sexual_orientation != "") %>%
  count(sexual_orientation) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(orientation_dist, col.names = c("Sexual Orientation", "Count", "Percentage (%)"),
      caption = "Sexual Orientation Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
df_filtered <- df %>% 
  filter(!is.na(sexual_orientation) & sexual_orientation != "")

ggplot(df_filtered, aes(x = reorder(sexual_orientation, 
                                    -table(sexual_orientation)[sexual_orientation]))) +
  geom_bar(fill = "mediumpurple", alpha = 0.8) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Sexual Orientation Distribution",
       x = "Sexual Orientation", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Relationship Status
```{r}
# Relationship status distribution
relationship_dist <- df %>%
  filter(!is.na(relationship_status) & relationship_status != "") %>%
  count(relationship_status) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(relationship_dist, col.names = c("Relationship Status", "Count", "Percentage (%)"),
      caption = "Relationship Status Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

### Municipality

```{r}
# Municipality distribution
municipality_dist <- df %>%
  count(municipality) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(municipality_dist, col.names = c("Municipality Type", "Count", "Percentage (%)"),
      caption = "Municipality Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
ggplot(df, aes(x = reorder(municipality, -table(municipality)[municipality]))) +
  geom_bar(fill = "darkgreen", alpha = 0.7) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Municipality Type Distribution",
       x = "Municipality Type", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Income

```{r}
# Income distribution
income_dist <- df %>%
  filter(!is.na(income) & income != "") %>%
  count(income) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(income_dist, col.names = c("Monthly Income", "Count", "Percentage (%)"),
      caption = "Monthly Income Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 6. Anthropometric Data

```{r}
# Height statistics
height_stats <- df %>%
  summarise(
    Mean = round(mean(height, na.rm = TRUE), 2),
    Median = median(height, na.rm = TRUE),
    SD = round(sd(height, na.rm = TRUE), 2),
    Min = min(height, na.rm = TRUE),
    Max = max(height, na.rm = TRUE)
  )

kable(height_stats, caption = "Height Distribution Statistics (cm)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Weight statistics
weight_stats <- df %>%
  summarise(
    Mean = round(mean(weight, na.rm = TRUE), 2),
    Median = median(weight, na.rm = TRUE),
    SD = round(sd(weight, na.rm = TRUE), 2),
    Min = min(weight, na.rm = TRUE),
    Max = max(weight, na.rm = TRUE)
  )

kable(weight_stats, caption = "Weight Distribution Statistics (kg)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# BMI calculation
df$bmi <- df$weight / ((df$height / 100) ^ 2)

# BMI statistics
bmi_stats <- df %>%
  summarise(
    Mean = round(mean(bmi, na.rm = TRUE), 2),
    Median = round(median(bmi, na.rm = TRUE), 2),
    SD = round(sd(bmi, na.rm = TRUE), 2),
    Min = round(min(bmi, na.rm = TRUE), 2),
    Max = round(max(bmi, na.rm = TRUE), 2)
  )

kable(bmi_stats, caption = "BMI Distribution Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 7. Recruitment Source

```{r}
# Recruitment distribution
recruitment_dist <- df %>%
  count(recruitment) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(recruitment_dist, col.names = c("Recruitment Source", "Count", "Percentage (%)"),
      caption = "Recruitment Source Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 8. Summary

```{r}
# Overall summary
cat("\n=== SAMPLE SUMMARY ===\n")
cat("Total Participants:", nrow(df), "\n")
cat("Age Range:", min(df$age, na.rm = TRUE), "-", max(df$age, na.rm = TRUE), "years\n")
cat("Mean Age:", round(mean(df$age, na.rm = TRUE), 1), "years (SD =", 
    round(sd(df$age, na.rm = TRUE), 2), ")\n")
cat("Female:", sum(df$sex == "Female", na.rm = TRUE), 
    "(", round(sum(df$sex == "Female", na.rm = TRUE)/nrow(df)*100, 1), "%)\n")
cat("Czech nationality:", sum(df$nationality == "Czech", na.rm = TRUE), 
    "(", round(sum(df$nationality == "Czech", na.rm = TRUE)/nrow(df)*100, 1), "%)\n")
```


## **Part II:	A2: Descriptive statistics of the demographic data of Study 2 (rating session) participants **

### 9. Loading the data
```{r data-loading}
# Load the dataset
df <- read.csv("Study 2 Demographics.csv", sep = ";", stringsAsFactors = FALSE)

# Display basic dataset information
cat("Dataset Dimensions:", dim(df)[1], "rows x", dim(df)[2], "columns\n")
cat("Survey Period:", min(df$StartDate), "to", max(df$StartDate), "\n")

# Display dataset structure
str(df)
```


### 10. Missing Data

```{r missing-data}
# Calculate missing values
missing_summary <- df %>%
  summarise_all(~sum(is.na(.) | . == "")) %>%
  gather(key = "Variable", value = "Missing_Count") %>%
  mutate(Missing_Percentage = round((Missing_Count / nrow(df)) * 100, 2)) %>%
  arrange(desc(Missing_Count))

# Display missing data table
kable(missing_summary, caption = "Missing Data Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualize missing data pattern
VIM::aggr(df, col = c('navyblue','red'), numbers = TRUE, sortVars = TRUE)
```

### 11. Data Quality Assessment

```{r data-quality}
# Survey completion metrics
completion_metrics <- data.frame(
  Metric = c("Total Responses", "Complete Responses", "Progress Rate", "Consent Rate", 
             "Average Duration (minutes)", "Min Duration (minutes)", "Max Duration (minutes)"),
  Value = c(nrow(df), 
            sum(df$Finished == TRUE),
            paste0(mean(df$Progress), "%"),
            paste0(round(sum(df$Consent == "Agreed")/nrow(df)*100, 1), "%"),
            round(mean(df$Durationinseconds)/60, 1),
            round(min(df$Durationinseconds)/60, 1),
            round(max(df$Durationinseconds)/60, 1))
)

kable(completion_metrics, caption = "Survey Quality Metrics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### 12. Demographic

### Age

```{r age-analysis}
# Age statistics
age_stats <- df %>%
  summarise(
    Mean = round(mean(age_clean, na.rm = TRUE), 2),
    Median = median(age_clean, na.rm = TRUE),
    SD = round(sd(age_clean, na.rm = TRUE), 2),
    Min = min(age_clean, na.rm = TRUE),
    Max = max(age_clean, na.rm = TRUE),
    Q1 = quantile(age_clean, 0.25, na.rm = TRUE),
    Q3 = quantile(age_clean, 0.75, na.rm = TRUE)
  )

kable(age_stats, caption = "Age Distribution Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Age distribution plots
ggplot(df, aes(x = age_clean)) +
  geom_histogram(bins = 15, fill = "steelblue", alpha = 0.7, color = "white") +
  geom_vline(aes(xintercept = mean(age_clean)), color = "red", linetype = "dashed", size = 1) +
  labs(title = "Age Distribution", x = "Age", y = "Frequency") +
  annotate("text", x = mean(df$age_clean) + 2, y = max(table(df$age_clean)) * 0.8, 
           label = paste("Mean:", round(mean(df$age_clean), 1)), color = "red")

```

### Sex and Gender 

```{r gender-analysis}
# Gender distribution using cleaned variable
gender_dist <- df %>%
  count(sex_clean) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(gender_dist, col.names = c("Gender", "Count", "Percentage (%)"), 
      caption = "Gender Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Gender identity vs biological sex comparison
gender_comparison <- df %>%
  count(gender, sex) %>%
  spread(sex, n, fill = 0)

kable(gender_comparison, caption = "Gender Identity vs Biological Sex") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
ggplot(df, aes(x = sex_clean, fill = sex_clean)) +
  geom_bar(alpha = 0.8) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Gender Distribution", x = "Gender", y = "Count") +
  scale_fill_manual(values = c("Female" = "#E69F00", "Male" = "#56B4E9")) +
  theme(legend.position = "none")
```

### Nationality 

```{r nationality-analysis}
# Nationality distribution
nationality_dist <- df %>%
  count(Nationality) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(nationality_dist, col.names = c("Nationality", "Count", "Percentage (%)"), 
      caption = "Nationality Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
ggplot(df, aes(x = reorder(Nationality, -table(Nationality)[Nationality]))) +
  geom_bar(fill = "coral", alpha = 0.8) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Nationality Distribution", x = "Nationality", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Education

```{r education-analysis}
# Education distribution
education_dist <- df %>%
  count(education_clean) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(education_dist, col.names = c("Education Level", "Count", "Percentage (%)"), 
      caption = "Education Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

### Sexual Orientation 

```{r sexual-orientation}
# Sexual orientation distribution
orientation_dist <- df %>%
  count(sexualorientation) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(orientation_dist, col.names = c("Sexual Orientation", "Count", "Percentage (%)"), 
      caption = "Sexual Orientation Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
ggplot(df, aes(x = reorder(sexualorientation, -table(sexualorientation)[sexualorientation]))) +
  geom_bar(fill = "mediumpurple", alpha = 0.8) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Sexual Orientation Distribution", 
       x = "Sexual Orientation", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Partnership Status

```{r}
#raw partnership status data
cat("Unique partnership status values:\n")
print(unique(df$partnershipstatus))

# Clean and standardize partnership status data
df$partnershipstatus_clean <- df$partnershipstatus

# Handle missing/empty values
df$partnershipstatus_clean[is.na(df$partnershipstatus_clean) | 
                          df$partnershipstatus_clean == "" | 
                          df$partnershipstatus_clean == "NA"] <- NA

# Clean UTF-8 issues and standardize categories
df$partnershipstatus_clean <- case_when(
  is.na(df$partnershipstatus_clean) ~ NA_character_,
  grepl("Single.*no partner", df$partnershipstatus_clean, ignore.case = TRUE) ~ "Single (no partner)",
  grepl("Serious relationship", df$partnershipstatus_clean, ignore.case = TRUE) ~ "Serious relationship", 
  grepl("Marriage.*registered", df$partnershipstatus_clean, ignore.case = TRUE) ~ "Marriage/registered partnership",
  grepl("non-binding", df$partnershipstatus_clean, ignore.case = TRUE) ~ "Non-binding relationship",
  # Handle the problematic UTF-8 string
  grepl("Nez", df$partnershipstatus_clean) | grepl("vztah", df$partnershipstatus_clean) ~ "Non-binding relationship",
  TRUE ~ "Other"
)

# Remove rows with missing partnership status 
df_partnership <- df %>% 
  filter(!is.na(partnershipstatus_clean))

cat("Sample size for partnership analysis:", nrow(df_partnership), "out of", nrow(df), "\n")

# Partnership status distribution
partnership_dist <- df_partnership %>%
  count(partnershipstatus_clean) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(partnership_dist, col.names = c("Partnership Status", "Count", "Percentage (%)"), 
      caption = "Partnership Status Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Partnership status by age group
df_partnership <- df_partnership %>%
  mutate(age_group = cut(age_clean, 
                        breaks = c(17, 20, 25, 30, 40), 
                        labels = c("18-20", "21-25", "26-30", "31-40"),
                        include.lowest = TRUE))

partnership_age <- df_partnership %>%
  filter(!is.na(age_group)) %>%
  count(age_group, partnershipstatus_clean) %>%
  group_by(age_group) %>%
  mutate(percentage = round(n/sum(n)*100, 1))

# Summary statistics
partnership_summary <- df_partnership %>%
  group_by(partnershipstatus_clean) %>%
  summarise(
    Count = n(),
    Mean_Age = round(mean(age_clean, na.rm = TRUE), 1),
    Median_Age = median(age_clean, na.rm = TRUE),
    Age_Range = paste(min(age_clean, na.rm = TRUE), "-", max(age_clean, na.rm = TRUE))
  )

kable(partnership_summary, caption = "Partnership Status Summary by Age") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```


### Residence

```{r residence-analysis}
# Residence distribution
residence_dist <- df %>%
  count(residence) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(residence_dist, col.names = c("Residence Type", "Count", "Percentage (%)"), 
      caption = "Residence Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Visualization
ggplot(df, aes(x = reorder(residence, -table(residence)[residence]))) +
  geom_bar(fill = "darkgreen", alpha = 0.7) +
  geom_text(stat = 'count', aes(label = after_stat(count)), vjust = -0.5) +
  labs(title = "Residence Type Distribution", 
       x = "Residence Type", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Income

```{r income-analysis}
# Income distribution (handling missing values)
income_dist <- df %>%
  filter(!is.na(monthlyincome) & monthlyincome != "") %>%
  count(monthlyincome) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(income_dist, col.names = c("Monthly Income", "Count", "Percentage (%)"), 
      caption = "Monthly Income Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```


### 13. Survey Completion

```{r response-time}
# Duration statistics
duration_stats <- df %>%
  mutate(duration_minutes = Durationinseconds / 60) %>%
  summarise(
    Mean_Minutes = round(mean(duration_minutes), 2),
    Median_Minutes = round(median(duration_minutes), 2),
    SD_Minutes = round(sd(duration_minutes), 2),
    Min_Minutes = round(min(duration_minutes), 2),
    Max_Minutes = round(max(duration_minutes), 2),
    Q1_Minutes = round(quantile(duration_minutes, 0.25), 2),
    Q3_Minutes = round(quantile(duration_minutes, 0.75), 2)
  )

kable(duration_stats, caption = "Survey Duration Statistics (Minutes)") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Duration distribution
df$duration_minutes <- df$Durationinseconds / 60

ggplot(df, aes(x = duration_minutes)) +
  geom_histogram(bins = 20, fill = "skyblue", alpha = 0.7, color = "white") +
  geom_vline(aes(xintercept = mean(duration_minutes)), color = "red", linetype = "dashed") +
  labs(title = "Survey Completion Time Distribution", 
       x = "Duration (Minutes)", y = "Frequency") +
  annotate("text", x = mean(df$duration_minutes) + 10, y = 20, 
           label = paste("Mean:", round(mean(df$duration_minutes), 1), "min"), color = "red")
```

### 14. Block Analysis

```{r block-analysis}
# Block distribution
block_dist <- df %>%
  count(Block) %>%
  mutate(percentage = round(n/sum(n)*100, 1)) %>%
  arrange(desc(n))

kable(block_dist, col.names = c("Block", "Count", "Percentage (%)"), 
      caption = "Survey Block Distribution") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Duration by block
duration_by_block <- df %>%
  group_by(Block) %>%
  summarise(
    Count = n(),
    Mean_Duration = round(mean(duration_minutes), 2),
    Median_Duration = round(median(duration_minutes), 2),
    SD_Duration = round(sd(duration_minutes), 2)
  ) %>%
  arrange(Mean_Duration)

kable(duration_by_block, caption = "Duration Statistics by Survey Block") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```