---
output:
  pdf_document:
     latex_engine: xelatex
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  out.width = "100%")
```

# **Supplement Secion B: Inferrential statistics**

## In this document;

##  **• B1:** Comprehensive models with exploratory variables and variable exclusion process
##  **•	B2:** Unsplit models (without stimulus type separation) 
##  **•	B3:** Complete models including control condition 
##  **•	B4:** Factorial 2x2 models


#### **In the .Pdf output file you may find only the outputs generated by the analysis code, in order to keep the supplementary files as concise as possible. However the full code is available on https://github.com/Rezvani-S/Costly-Beauty-ShoeStudy.git**


## 1. Required Packages

```{r}
library(haven)         
library(lme4)           
library(lmerTest)       
library(emmeans)       
library(ggplot2)        
library(dplyr)          
library(ggsignif)
library(MuMIn)          
library(reshape2)
library(gridExtra)
library(effectsize)  
library(ggpattern)
library(gridExtra)
library(grid)
library(insight)
library(car) 
```

## 2. Data Import and Preparation

```{r}
# Reading data file
body_data <-  read.csv("Body_11Block_Long.csv")

# converting to data frame
body_data <- as.data.frame(body_data)

# Condition (5 levels) converted to factor
body_data$Condition <- factor(body_data$Condition,
                              levels = 1:5,
                              labels = c("Control", 
                                         "Economy Flat",
                                         "Economy Heel", 
                                         "Luxury Flat",
                                         "Luxury Heel"))

# Dimension (2 levels) converted to factor
body_data$Dimension <- factor(body_data$Dimension,
                              levels = 1:2,
                              labels = c("Attractiveness",
                                         "Wealth"))

# Stimuli_Type (2 levels) converted to factor
body_data$Stimuli_Type <- factor(body_data$Stimuli_Type,
                                levels = 1:2,
                                labels = c("Image", 
                                           "Video"))

# Converting empty Income strings to NA
body_data$monthlyincome[body_data$monthlyincome == ""] <- NA
# Then convert to ordered factor with the existing labels
body_data$monthlyincome <- factor(body_data$monthlyincome,
                                 levels = c("up to 15 000 CZK/month",
                                           "15 000-30 000 CZK/month", 
                                           "30 000-50 000 CZK/month",
                                           "over 50 000 CZK/month"),
                                 ordered = TRUE)

# Sex converted to factor
body_data$sex <- factor(body_data$sex,
                        labels = c("Female", "Male"))

# Fixing variable names
names(body_data)[names(body_data) == "rating"] <- "Rating"
names(body_data)[names(body_data) == "Block"] <- "block"
names(body_data)[names(body_data) == "Code"] <- "code"

# The Brand scores were read
# Using the merged knowledge scores
bscore_df <- read.csv("merged_knowledge_scores.csv")

# Only the variables needed were selected from bscore
bscore_subset <- bscore_df[, c("code", "consistency_score", 
                               "merged_score_zscore")]

# The variable "code" was renamed to "Code" to match in both datasets
names(bscore_subset)[names(bscore_subset) == "code"] <- "code"

# The datasets were merged by code
body_data <- merge(body_data, bscore_subset, by = "code", all.x = TRUE)
```

## **PART I:  Supplement B1: Comprehensive models with exploratory variables and variable exclusion process **

## 3. Data Cleaning and Preparation
```{r}
# Rows with NA in relevant columns were removed
body_df_clean <- body_data[complete.cases(body_data[, c("Rating", "Dimension", "Condition", 
                                            "Model", "block", "code", "sex", 
                                            "monthlyincome", "merged_score_zscore", 
                                            "Stimuli_Type")]), ]

# Factors were properly formatted
body_df_clean$Model <- as.factor(body_df_clean$Model)
body_df_clean$block <- as.factor(body_df_clean$block)
body_df_clean$code <- as.factor(body_df_clean$code)

# Block:model interaction for nested structure was created
body_df_clean$block_model <- interaction(body_df_clean$block, body_df_clean$Model)

# Data was split into two dimensions
body_df_attract <- body_df_clean[body_df_clean$Dimension == "Attractiveness", ]
body_df_wealth <- body_df_clean[body_df_clean$Dimension == "Wealth", ]
```

## 4. Comprehensive Attractiveness Model

A comprehensive linear mixed-effects model for attractiveness was constructed, including all potential variables:

```{r}
# Comprehensive model for attractiveness including additional variables
model_attract_comp <- lmer(Rating ~ Condition + sex + monthlyincome + 
                           merged_score_zscore + Stimuli_Type + 
                           (1|block/Model) + (1|code), 
                          data = body_df_attract)

# Model summary was generated
summary(model_attract_comp)
```

### ANOVA for Fixed Effects in Attractiveness Model

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_comp)
```

### Random Effects for Attractiveness Model

```{r}
# Random effects variance was extracted
cat("Random Effects Variance for Comprehensive Attractiveness Model:\n")
print(VarCorr(model_attract_comp))
```

## 5. Comprehensive Wealth Model

A comprehensive linear mixed-effects model for wealth was constructed, including all potential variables:

```{r}
# Comprehensive model for wealth including additional variables
model_wealth_comp <- lmer(Rating ~ Condition + sex + monthlyincome + 
                          merged_score_zscore + Stimuli_Type + 
                          (1|block/Model) + (1|code), 
                         data = body_df_wealth)

# Model summary was generated
summary(model_wealth_comp)
```

### ANOVA for Fixed Effects in Wealth Model

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_comp)
```

### Random Effects for Wealth Model

```{r}
# Random effects variance was extracted
cat("Random Effects Variance for Comprehensive Wealth Model:\n")
print(VarCorr(model_wealth_comp))
```

## 6. Model Comparison: Testing Variable Contributions

To assess the contribution of each additional variable, stepwise comparisons were conducted by removing one variable at a time:

### 6.1 Testing Sex Contribution

```{r}
# Models without sex
model_attract_no_sex <- lmer(Rating ~ Condition + monthlyincome + 
                             merged_score_zscore + Stimuli_Type + 
                             (1|block/Model) + (1|code), 
                            data = body_df_attract)

model_wealth_no_sex <- lmer(Rating ~ Condition + monthlyincome + 
                           merged_score_zscore + Stimuli_Type + 
                           (1|block/Model) + (1|code), 
                          data = body_df_wealth)

# Model comparison for attractiveness
cat("Sex contribution to Attractiveness model:\n")
anova(model_attract_no_sex, model_attract_comp)

# Model comparison for wealth
cat("\nSex contribution to Wealth model:\n")
anova(model_wealth_no_sex, model_wealth_comp)
```

### 6.2 Testing Monthly Income Contribution

```{r}
# Models without monthly income
model_attract_no_income <- lmer(Rating ~ Condition + sex + 
                               merged_score_zscore + Stimuli_Type + 
                               (1|block/Model) + (1|code), 
                              data = body_df_attract)

model_wealth_no_income <- lmer(Rating ~ Condition + sex + 
                              merged_score_zscore + Stimuli_Type + 
                              (1|block/Model) + (1|code), 
                             data = body_df_wealth)

# Model comparison for attractiveness
cat("Monthly Income contribution to Attractiveness model:\n")
anova(model_attract_no_income, model_attract_comp)

# Model comparison for wealth
cat("\nMonthly Income contribution to Wealth model:\n")
anova(model_wealth_no_income, model_wealth_comp)
```

### 6.3 Testing Brand Knowledge Score Contribution

```{r}
# Models without brand knowledge score
model_attract_no_brand <- lmer(Rating ~ Condition + sex + monthlyincome + 
                              Stimuli_Type + (1|block/Model) + (1|code), 
                             data = body_df_attract)

model_wealth_no_brand <- lmer(Rating ~ Condition + sex + monthlyincome + 
                             Stimuli_Type + (1|block/Model) + (1|code), 
                            data = body_df_wealth)

# Model comparison for attractiveness
cat("Brand Knowledge Score contribution to Attractiveness model:\n")
anova(model_attract_no_brand, model_attract_comp)

# Model comparison for wealth
cat("\nBrand Knowledge Score contribution to Wealth model:\n")
anova(model_wealth_no_brand, model_wealth_comp)
```

### 6.4 Testing Stimuli Type Contribution

```{r}
# Models without stimuli type
model_attract_no_stimuli <- lmer(Rating ~ Condition + sex + monthlyincome + 
                                merged_score_zscore + (1|block/Model) + (1|code), 
                               data = body_df_attract)

model_wealth_no_stimuli <- lmer(Rating ~ Condition + sex + monthlyincome + 
                               merged_score_zscore + (1|block/Model) + (1|code), 
                              data = body_df_wealth)

# Model comparison for attractiveness
cat("Stimuli Type contribution to Attractiveness model:\n")
anova(model_attract_no_stimuli, model_attract_comp)

# Model comparison for wealth
cat("\nStimuli Type contribution to Wealth model:\n")
anova(model_wealth_no_stimuli, model_wealth_comp)
```

### 6.5 Testing Model (nested in block) Contribution

```{r}
# Models with only block (without nested Model)
model_attract_no_nested <- lmer(Rating ~ Condition + sex + monthlyincome + 
                               merged_score_zscore + Stimuli_Type + 
                               (1|block) + (1|code), 
                              data = body_df_attract)

model_wealth_no_nested <- lmer(Rating ~ Condition + sex + monthlyincome + 
                              merged_score_zscore + Stimuli_Type + 
                              (1|block) + (1|code), 
                             data = body_df_wealth)

# Model comparison for attractiveness
cat("Nested Model contribution to Attractiveness model:\n")
anova(model_attract_no_nested, model_attract_comp)

# Model comparison for wealth
cat("\nNested Model contribution to Wealth model:\n")
anova(model_wealth_no_nested, model_wealth_comp)
```

## 7. AIC and BIC Comparison for Model Selection

To further evaluate model selection, AIC and BIC values were compared between the comprehensive and simplified models:

```{r}
# Simplified models
model_attract_simple <- lmer(Rating ~ Condition + (1|block) + (1|code), 
                            data = body_df_attract)

model_wealth_simple <- lmer(Rating ~ Condition + (1|block) + (1|code), 
                           data = body_df_wealth)

# AIC and BIC comparison for attractiveness
cat("AIC and BIC comparison for Attractiveness models:\n")
AIC_BIC_attract <- data.frame(
  Model = c("Comprehensive", "Simple"),
  AIC = c(AIC(model_attract_comp), AIC(model_attract_simple)),
  BIC = c(BIC(model_attract_comp), BIC(model_attract_simple))
)
print(AIC_BIC_attract)

# AIC and BIC comparison for wealth
cat("\nAIC and BIC comparison for Wealth models:\n")
AIC_BIC_wealth <- data.frame(
  Model = c("Comprehensive", "Simple"),
  AIC = c(AIC(model_wealth_comp), AIC(model_wealth_simple)),
  BIC = c(BIC(model_wealth_comp), BIC(model_wealth_simple))
)
print(AIC_BIC_wealth)
```

## **PART II:  Supplement B2: Unsplit models (without stimulus type separation)**

### Data Cleaning and Preparation
```{r}
# Rows with NA in relevant columns were removed
body_df_clean <- body_data[complete.cases(body_data[, c("Rating", "Dimension", "Condition", 
                                            "Model", "block", "code", "Stimuli_Type")]), ]

# Factors were properly formatted
body_df_clean$Model <- as.factor(body_df_clean$Model)
body_df_clean$block <- as.factor(body_df_clean$block)
body_df_clean$code <- as.factor(body_df_clean$code)

# Data was split into two dimensions
body_df_attract <- body_df_clean[body_df_clean$Dimension == "Attractiveness", ]
body_df_wealth <- body_df_clean[body_df_clean$Dimension == "Wealth", ]
```

## 8. Attractiveness Model with Interaction

A linear mixed-effects model for attractiveness was constructed including the interaction between Condition and Stimuli_Type:

```{r}
# Model for attractiveness with interaction
model_attract_interact <- lmer(Rating ~ Condition * Stimuli_Type + 
                              (1|block/Model) + (1|code), 
                              data = body_df_attract)

# Model summary was generated
summary(model_attract_interact)
```

### ANOVA for Fixed Effects in Attractiveness Model with Interaction

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_interact)
```

### Estimated Marginal Means for Condition by Stimuli_Type in Attractiveness Model

```{r}
# Estimated marginal means for Condition by Stimuli_Type interaction
emmeans_attract_interact <- emmeans(model_attract_interact, ~ Condition | Stimuli_Type)
print(emmeans_attract_interact)
```

### Calculate R-squared values for the attractiveness model
```{r}
r_squared_attract <- r.squaredGLMM(model_attract_interact)
print(r_squared_attract)

# Extract specific values
R2m_attract <- r_squared_attract[1, "R2m"]  # Marginal R²
R2c_attract <- r_squared_attract[1, "R2c"]  # Conditional R²

# Display results
cat("Attractiveness Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract, 4), "\n")
cat("Random effects contribution:", round(R2c_attract - R2m_attract, 4), "\n")
```

### Visualizing Attractiveness Results by Condition and Stimuli_Type

```{r, fig.width=10, fig.height=6}
# The results for Condition by Stimuli_Type interaction were plotted
attract_interact_results <- as.data.frame(emmeans_attract_interact)
p_attract_interact <- ggplot(attract_interact_results, aes(x=Condition, y=emmean, color=Stimuli_Type, group=Stimuli_Type)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Interaction of Condition and Stimuli Type on Attractiveness Ratings") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_attract_interact)
```
Figure B2.1. Interaction between footwear condition and stimulus type (image vs. video) on attractiveness ratings. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition by Stimuli_Type in Attractiveness Model

```{r}
# Pairwise comparisons for Condition within each Stimuli_Type
pairs(emmeans_attract_interact, adjust = "tukey")
```

## 9. Wealth Model with Interaction

A linear mixed-effects model for wealth was constructed including the interaction between Condition and Stimuli_Type:

```{r}
# Model for wealth with interaction
model_wealth_interact <- lmer(Rating ~ Condition * Stimuli_Type + 
                            (1|block/Model) + (1|code), 
                            data = body_df_wealth)

# Model summary was generated
summary(model_wealth_interact)
```

### ANOVA for Fixed Effects in Wealth Model with Interaction

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_interact)
```

### Estimated Marginal Means for Condition by Stimuli_Type in Wealth Model

```{r}
# Estimated marginal means for Condition by Stimuli_Type interaction
emmeans_wealth_interact <- emmeans(model_wealth_interact, ~ Condition | Stimuli_Type)
print(emmeans_wealth_interact)
```
### Calculate R-squared values for the wealth model
```{r}
r_squared_wealth <- r.squaredGLMM(model_wealth_interact)
print(r_squared_wealth)

# Extract specific values
R2m_wealth <- r_squared_wealth[1, "R2m"]  # Marginal R²
R2c_wealth <- r_squared_wealth[1, "R2c"]  # Conditional R²

# Display results
cat("Wealth Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth - R2m_wealth, 4), "\n")
```


### Visualizing Wealth Results by Condition and Stimuli_Type

```{r, fig.width=10, fig.height=6}
# The results for Condition by Stimuli_Type interaction were plotted
wealth_interact_results <- as.data.frame(emmeans_wealth_interact)
p_wealth_interact <- ggplot(wealth_interact_results, aes(x=Condition, y=emmean, color=Stimuli_Type, group=Stimuli_Type)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Interaction of Condition and Stimuli Type on Wealth Ratings") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_wealth_interact)
```
Figure B2.2. Interaction between footwear condition and stimulus type (image vs. video) on wealth perception ratings. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition by Stimuli_Type in Wealth Model

```{r}
# Pairwise comparisons for Condition within each Stimuli_Type
pairs(emmeans_wealth_interact, adjust = "tukey")
```

## 10. Combined Plot: Condition × Dimension × Stimuli_Type

A combined plot was created to visualize the interaction between Condition, Dimension, and Stimuli_Type:

```{r, fig.width=12, fig.height=8}
# Combine results from attractiveness and wealth models
combined_interact_results <- rbind(
  transform(attract_interact_results, Dimension = "Attractiveness"),
  transform(wealth_interact_results, Dimension = "Wealth")
)

# Create a comprehensive plot
p_combined_interact <- ggplot(combined_interact_results, aes(x=Condition, y=emmean, color=Dimension, group=interaction(Dimension, Stimuli_Type), linetype=Stimuli_Type)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_line(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), position = position_dodge(width = 0.5), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "right") +
  ggtitle("Condition × Dimension × Stimuli Type Interaction") +
  xlab("Condition") +
  ylab("Estimated Mean Rating") +
  scale_linetype_manual(values = c("solid", "dashed")) +
  scale_color_manual(values = c("blue", "red"))

print(p_combined_interact)
```
Figure B2.3. Three-way interaction between footwear condition, dimension (attractiveness vs. wealth), and stimulus type. Solid lines represent image stimuli; dashed lines represent video stimuli. Error bars represent 95% confidence intervals.





## **PART III:  Supplement	B3: Complete models including control condition (Split by StimuliType)**

## 11. Models for Image Stimuli Only

```{r}
# Filter data for Image stimuli only
body_df_attract_image <- body_df_attract[body_df_attract$Stimuli_Type == "Image", ]
body_df_wealth_image <- body_df_wealth[body_df_wealth$Stimuli_Type == "Image", ]
```

### Attractiveness Model for Image Stimuli

```{r}
# Model for attractiveness - Image stimuli only
model_attract_image <- lmer(Rating ~ Condition + 
                           (1|block/Model) + (1|code), 
                           data = body_df_attract_image)

# Model summary was generated
summary(model_attract_image)
```

### ANOVA for Fixed Effects in Attractiveness Model (Image Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_image)
```

### Estimated Marginal Means for Condition in Attractiveness Model (Image Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_attract_image <- emmeans(model_attract_image, ~ Condition)
print(emmeans_attract_image)
```
### Calculate R-squared values for the attractiveness model
```{r}
r_squared_attract <- r.squaredGLMM(model_attract_image)
print(r_squared_attract)

# Extract specific values
R2m_attract <- r_squared_attract[1, "R2m"]  # Marginal R²
R2c_attract <- r_squared_attract[1, "R2c"]  # Conditional R²

# Display results
cat("Attractiveness Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract, 4), "\n")
cat("Random effects contribution:", round(R2c_attract - R2m_attract, 4), "\n")
```

### Visualizing Attractiveness Results for Image Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
attract_image_results <- as.data.frame(emmeans_attract_image)
p_attract_image <- ggplot(attract_image_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Attractiveness Ratings (Image Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_attract_image)
```
Figure B3.1. Effect of footwear conditions on attractiveness ratings for image stimuli, including control condition. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition in Attractiveness Model (Image Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_attract_image, adjust = "tukey")
```

### Wealth Model for Image Stimuli

```{r}
# Model for wealth - Image stimuli only
model_wealth_image <- lmer(Rating ~ Condition + 
                          (1|block/Model) + (1|code), 
                          data = body_df_wealth_image)

# Model summary was generated
summary(model_wealth_image)
```

### ANOVA for Fixed Effects in Wealth Model (Image Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_image)
```

### Estimated Marginal Means for Condition in Wealth Model (Image Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_wealth_image <- emmeans(model_wealth_image, ~ Condition)
print(emmeans_wealth_image)
```
### Calculate R-squared values for the wealth model
```{r}
r_squared_wealth <- r.squaredGLMM(model_wealth_image)
print(r_squared_wealth)

# Extract specific values
R2m_wealth <- r_squared_wealth[1, "R2m"]  # Marginal R²
R2c_wealth <- r_squared_wealth[1, "R2c"]  # Conditional R²

# Display results
cat("Wealth Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth - R2m_wealth, 4), "\n")
```

### Visualizing Wealth Results for Image Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
wealth_image_results <- as.data.frame(emmeans_wealth_image)
p_wealth_image <- ggplot(wealth_image_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Wealth Ratings (Image Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_wealth_image)
```
Figure B3.2. Effect of footwear conditions on wealth perception ratings for image stimuli, including control condition. Error bars represent 95% confidence intervals.


### Pairwise Comparisons for Condition in Wealth Model (Image Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_wealth_image, adjust = "tukey")
```

### Comparison Between Dimensions for Image Stimuli

```{r, fig.width=10, fig.height=6}
# Results from both dimensions were combined
combined_image_results <- rbind(
  transform(attract_image_results, Dimension = "Attractiveness"),
  transform(wealth_image_results, Dimension = "Wealth")
)

# The comparison plot was created
p_combined_image <- ggplot(combined_image_results, aes(x = Condition, y = emmean, color = Dimension, group = Dimension)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Comparison of Condition Effects Between Dimensions (Image Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_combined_image)
```
Figure B3.3. Comparison of footwear condition effects between attractiveness and wealth dimensions for image stimuli. Error bars represent 95% confidence intervals.


## 12. Models for Video Stimuli Only

Next, the data was filtered to include only Video stimuli:

```{r}
# Filter data for Video stimuli only
body_df_attract_video <- body_df_attract[body_df_attract$Stimuli_Type == "Video", ]
body_df_wealth_video <- body_df_wealth[body_df_wealth$Stimuli_Type == "Video", ]
```

### Attractiveness Model for Video Stimuli

```{r}
# Model for attractiveness - Video stimuli only
model_attract_video <- lmer(Rating ~ Condition + 
                           (1|block/Model) + (1|code), 
                           data = body_df_attract_video)

# Model summary was generated
summary(model_attract_video)
```

### ANOVA for Fixed Effects in Attractiveness Model (Video Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_video)
```

### Estimated Marginal Means for Condition in Attractiveness Model (Video Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_attract_video <- emmeans(model_attract_video, ~ Condition)
print(emmeans_attract_video)
```
### Calculate R-squared values for the attractiveness model
```{r}
r_squared_attract <- r.squaredGLMM(model_attract_video)
print(r_squared_attract)

# Extract specific values
R2m_attract <- r_squared_attract[1, "R2m"]  # Marginal R²
R2c_attract <- r_squared_attract[1, "R2c"]  # Conditional R²

# Display results
cat("Attractiveness Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract, 4), "\n")
cat("Random effects contribution:", round(R2c_attract - R2m_attract, 4), "\n")
```

### Visualizing Attractiveness Results for Video Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
attract_video_results <- as.data.frame(emmeans_attract_video)
p_attract_video <- ggplot(attract_video_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Attractiveness Ratings (Video Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_attract_video)
```
Figure B3.4. Effect of footwear conditions on attractiveness ratings for video stimuli, including control condition. Error bars represent 95% confidence intervals.


### Pairwise Comparisons for Condition in Attractiveness Model (Video Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_attract_video, adjust = "tukey")
```

### Wealth Model for Video Stimuli

```{r}
# Model for wealth - Video stimuli only
model_wealth_video <- lmer(Rating ~ Condition + 
                          (1|block/Model) + (1|code), 
                          data = body_df_wealth_video)

# Model summary was generated
summary(model_wealth_video)
```

### ANOVA for Fixed Effects in Wealth Model (Video Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_video)
```

### Estimated Marginal Means for Condition in Wealth Model (Video Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_wealth_video <- emmeans(model_wealth_video, ~ Condition)
print(emmeans_wealth_video)
```
### Calculate R-squared values for the wealth model
```{r}
r_squared_wealth <- r.squaredGLMM(model_wealth_video)
print(r_squared_wealth)

# Extract specific values
R2m_wealth <- r_squared_wealth[1, "R2m"]  # Marginal R²
R2c_wealth <- r_squared_wealth[1, "R2c"]  # Conditional R²

# Display results
cat("Wealth Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth - R2m_wealth, 4), "\n")
```

### Visualizing Wealth Results for Video Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
wealth_video_results <- as.data.frame(emmeans_wealth_video)
p_wealth_video <- ggplot(wealth_video_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Wealth Ratings (Video Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_wealth_video)
```
Figure B3.5. Effect of footwear conditions on wealth perception ratings for video stimuli, including control condition. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition in Wealth Model (Video Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_wealth_video, adjust = "tukey")
```

### Comparison Between Dimensions for Video Stimuli

```{r, fig.width=10, fig.height=6}
# Results from both dimensions were combined
combined_video_results <- rbind(
  transform(attract_video_results, Dimension = "Attractiveness"),
  transform(wealth_video_results, Dimension = "Wealth")
)

# The comparison plot was created
p_combined_video <- ggplot(combined_video_results, aes(x = Condition, y = emmean, color = Dimension, group = Dimension)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Comparison of Condition Effects Between Dimensions (Video Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_combined_video)
```
Figure B3.6. Comparison of footwear condition effects between attractiveness and wealth dimensions for video stimuli. Error bars represent 95% confidence intervals.


Creating comparison plot for Dimention x StimuliType
```{r fig.width=7, fig.height=6, out.width="100%", fig.align='center'}
# Extract data from the emmeans objects for the interaction models
attract_interact_data <- as.data.frame(emmeans_attract_interact)
wealth_interact_data <- as.data.frame(emmeans_wealth_interact)

# Add dimension labels
attract_interact_data$Dimension <- "Attractiveness"
wealth_interact_data$Dimension <- "Wealth"

# Combine the data
combined_plot_data <- rbind(attract_interact_data, wealth_interact_data)

# Ensure proper factor levels
combined_plot_data$Condition <- factor(combined_plot_data$Condition,
                                     levels = c("Control", "Economy Flat", "Economy Heel", 
                                              "Luxury Flat", "Luxury Heel"))
combined_plot_data$Stimuli_Type <- factor(combined_plot_data$Stimuli_Type, 
                                        levels = c("Image", "Video"))
combined_plot_data$Dimension <- factor(combined_plot_data$Dimension,
                                     levels = c("Attractiveness", "Wealth"))

# Create the plot
p_interaction_comparison <- ggplot(combined_plot_data, 
                                 aes(x = Condition, y = emmean, 
                                     color = Stimuli_Type, 
                                     linetype = Stimuli_Type,
                                     shape = Stimuli_Type,
                                     group = Stimuli_Type)) +
  geom_line(size = .8, position = position_dodge(width = 0.1)) +
  geom_point(size = 3, position = position_dodge(width = 0.1)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0.2, size = 0.5, 
                position = position_dodge(width = 0.1)) +
  scale_color_manual(values = c("Image" = "black", "Video" = "black"),
                     name = "Stimulus Type") +
  scale_linetype_manual(values = c("Image" = "solid", "Video" = "dashed"),
                        name = "Stimulus Type") +
  scale_shape_manual(values = c("Image" = 16, "Video" = 15),  # 16 = circle, 15 = square
                     name = "Stimulus Type") +
  scale_x_discrete(labels = c("Control" = "Control",
                             "Economy Flat" = "Economy\nFlat",
                             "Economy Heel" = "Economy\nHeel",
                             "Luxury Flat" = "Luxury\nFlat",
                             "Luxury Heel" = "Luxury\nHeel")) +
  scale_y_continuous(limits = c(4.0, 5.8), 
                     breaks = seq(4.0, 5.8, by = 0.4)) +
  facet_wrap(~ Dimension, ncol = 2, scales = "free_y") +
  labs(x = "Condition",
       y = "Estimated Mean Rating",
       caption = "Error bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    # Panel styling
    panel.grid.major = element_line(color = "grey94", size = 0.4),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    
    # Strip (facet label) styling
    strip.background = element_rect(fill = "white", color = "black", size = 0.8),
    strip.text = element_text(size = 12, face = "bold"),
    
    # Axis styling
    axis.title = element_text(size = 8),
    axis.text = element_text(size = 8, color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks = element_line(color = "black", size = 0.5),
    
    # Legend styling
    legend.position = "top",
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    legend.key.width = unit(1.5, "cm"),
    legend.margin = margin(b = 10),
    
    # Caption styling
    plot.caption = element_text(size = 8, hjust = 1, 
                           color = "grey30",
                           margin = margin(t = 10)),
    
    # Overall margins
    plot.margin = margin(10, 10, 10, 10)
  )

# Display the plot
print(p_interaction_comparison)

# Save high-quality version
ggsave("condition_stimulus_interaction.png", p_interaction_comparison,
       width = 12, height = 6, dpi = 300, bg = "white")
ggsave("condition_stimulus_interaction.pdf", p_interaction_comparison,
       width = 12, height = 6, bg = "white")
```
Figure B3.7. Comparison of footwear condition effects across stimulus types (image vs. video) and dimensions (attractiveness vs. wealth). Error bars represent 95% confidence intervals.


## **PART IV:  Supplement B4: 2×2 Factorial Analysis (Excluding Control Condition)**


## 13. Data Preparation for 2×2 Factorial Design
```{r}

# Filter out Control condition and create factorial variables
body_df_attract_factorial <- body_df_attract[body_df_attract$Condition != "Control", ]
body_df_wealth_factorial <- body_df_wealth[body_df_wealth$Condition != "Control", ]

# Create Trait_Exaggeration factor (Heel vs Flat)
body_df_attract_factorial$Trait_Exaggeration <- factor(
  ifelse(grepl("Heel", body_df_attract_factorial$Condition), "Heel", "Flat"),
  levels = c("Flat", "Heel")
)

body_df_wealth_factorial$Trait_Exaggeration <- factor(
  ifelse(grepl("Heel", body_df_wealth_factorial$Condition), "Heel", "Flat"),
  levels = c("Flat", "Heel")
)

# Create Cost factor (Economy vs Luxury)
body_df_attract_factorial$Cost <- factor(
  ifelse(grepl("Economy", body_df_attract_factorial$Condition), "Economy", "Luxury"),
  levels = c("Economy", "Luxury")
)

body_df_wealth_factorial$Cost <- factor(
  ifelse(grepl("Economy", body_df_wealth_factorial$Condition), "Economy", "Luxury"),
  levels = c("Economy", "Luxury")
)

# Set sum coding (effects coding) for both factors
contrasts(body_df_attract_factorial$Trait_Exaggeration) <- contr.sum(2)
contrasts(body_df_attract_factorial$Cost) <- contr.sum(2)
contrasts(body_df_wealth_factorial$Trait_Exaggeration) <- contr.sum(2)
contrasts(body_df_wealth_factorial$Cost) <- contr.sum(2)

# Split by Stimuli_Type
body_df_attract_factorial_image <- body_df_attract_factorial[body_df_attract_factorial$Stimuli_Type == "Image", ]
body_df_attract_factorial_video <- body_df_attract_factorial[body_df_attract_factorial$Stimuli_Type == "Video", ]
body_df_wealth_factorial_image <- body_df_wealth_factorial[body_df_wealth_factorial$Stimuli_Type == "Image", ]
body_df_wealth_factorial_video <- body_df_wealth_factorial[body_df_wealth_factorial$Stimuli_Type == "Video", ]
```

## 14. Attractiveness Models - 2×2 Factorial Design

### 14.1 Attractiveness Model for Image Stimuli (2×2)
```{r}
# Model for attractiveness - Image stimuli (2×2 factorial)
model_attract_factorial_image <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                      (1|block/Model) + (1|code), 
                                      data = body_df_attract_factorial_image)

# Model summary
summary(model_attract_factorial_image)
```

ANOVA for 2×2 Factorial Model (Attractiveness - Image)
```{r}
# Type III ANOVA table for factorial effects
anova(model_attract_factorial_image)
```

Estimated Marginal Means (Attractiveness - Image)
```{r}
# Main effect of Trait_Exaggeration
emmeans_attract_fact_img_trait <- emmeans(model_attract_factorial_image, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_attract_fact_img_trait)

# Main effect of Cost
emmeans_attract_fact_img_cost <- emmeans(model_attract_factorial_image, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_attract_fact_img_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_attract_fact_img_interact <- emmeans(model_attract_factorial_image, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_attract_fact_img_interact)
```

Pairwise Comparisons (Attractiveness - Image)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_attract_fact_img_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_attract_fact_img_interact2 <- emmeans(model_attract_factorial_image, ~ Cost | Trait_Exaggeration)
pairs(emmeans_attract_fact_img_interact2, adjust = "tukey")
```

R-squared for Attractiveness Model (Image - 2×2)
```{r}
r_squared_attract_fact_img <- r.squaredGLMM(model_attract_factorial_image)
print(r_squared_attract_fact_img)

R2m_attract_fact_img <- r_squared_attract_fact_img[1, "R2m"]
R2c_attract_fact_img <- r_squared_attract_fact_img[1, "R2c"]

cat("Attractiveness Model (Image) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract_fact_img, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract_fact_img, 4), "\n")
cat("Random effects contribution:", round(R2c_attract_fact_img - R2m_attract_fact_img, 4), "\n")
```

### 14.2 Attractiveness Model for Video Stimuli (2×2)
```{r}
# Model for attractiveness - Video stimuli (2×2 factorial)
model_attract_factorial_video <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                      (1|block/Model) + (1|code), 
                                      data = body_df_attract_factorial_video)

# Model summary
summary(model_attract_factorial_video)
```

ANOVA for 2×2 Factorial Model (Attractiveness - Video)
```{r}
# Type III ANOVA table for factorial effects
anova(model_attract_factorial_video)
```

Estimated Marginal Means (Attractiveness - Video)
```{r}
# Main effect of Trait_Exaggeration
emmeans_attract_fact_vid_trait <- emmeans(model_attract_factorial_video, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_attract_fact_vid_trait)

# Main effect of Cost
emmeans_attract_fact_vid_cost <- emmeans(model_attract_factorial_video, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_attract_fact_vid_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_attract_fact_vid_interact <- emmeans(model_attract_factorial_video, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_attract_fact_vid_interact)
```

Pairwise Comparisons (Attractiveness - Video)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_attract_fact_vid_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_attract_fact_vid_interact2 <- emmeans(model_attract_factorial_video, ~ Cost | Trait_Exaggeration)
pairs(emmeans_attract_fact_vid_interact2, adjust = "tukey")
```

R-squared for Attractiveness Model (Video - 2×2)
```{r}
r_squared_attract_fact_vid <- r.squaredGLMM(model_attract_factorial_video)
print(r_squared_attract_fact_vid)

R2m_attract_fact_vid <- r_squared_attract_fact_vid[1, "R2m"]
R2c_attract_fact_vid <- r_squared_attract_fact_vid[1, "R2c"]

cat("Attractiveness Model (Video) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract_fact_vid, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract_fact_vid, 4), "\n")
cat("Random effects contribution:", round(R2c_attract_fact_vid - R2m_attract_fact_vid, 4), "\n")
```

## 15. Wealth Models - 2×2 Factorial Design

### 15.1 Wealth Model for Image Stimuli (2×2)
```{r}
# Model for wealth - Image stimuli (2×2 factorial)
model_wealth_factorial_image <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                     (1|block/Model) + (1|code), 
                                     data = body_df_wealth_factorial_image)

# Model summary
summary(model_wealth_factorial_image)
```

ANOVA for 2×2 Factorial Model (Wealth - Image)
```{r}
# Type III ANOVA table for factorial effects
anova(model_wealth_factorial_image)
```

Estimated Marginal Means (Wealth - Image)
```{r}
# Main effect of Trait_Exaggeration
emmeans_wealth_fact_img_trait <- emmeans(model_wealth_factorial_image, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_wealth_fact_img_trait)

# Main effect of Cost
emmeans_wealth_fact_img_cost <- emmeans(model_wealth_factorial_image, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_wealth_fact_img_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_wealth_fact_img_interact <- emmeans(model_wealth_factorial_image, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_wealth_fact_img_interact)
```

Pairwise Comparisons (Wealth - Image)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_wealth_fact_img_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_wealth_fact_img_interact2 <- emmeans(model_wealth_factorial_image, ~ Cost | Trait_Exaggeration)
pairs(emmeans_wealth_fact_img_interact2, adjust = "tukey")
```

R-squared for Wealth Model (Image - 2×2)
```{r}
r_squared_wealth_fact_img <- r.squaredGLMM(model_wealth_factorial_image)
print(r_squared_wealth_fact_img)

R2m_wealth_fact_img <- r_squared_wealth_fact_img[1, "R2m"]
R2c_wealth_fact_img <- r_squared_wealth_fact_img[1, "R2c"]

cat("Wealth Model (Image) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth_fact_img, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth_fact_img, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth_fact_img - R2m_wealth_fact_img, 4), "\n")
```

### 15.2 Wealth Model for Video Stimuli (2×2)
```{r}
# Model for wealth - Video stimuli (2×2 factorial)
model_wealth_factorial_video <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                     (1|block/Model) + (1|code), 
                                     data = body_df_wealth_factorial_video)

# Model summary
summary(model_wealth_factorial_video)
```

ANOVA for 2×2 Factorial Model (Wealth - Video)
```{r}
# Type III ANOVA table for factorial effects
anova(model_wealth_factorial_video)
```

Estimated Marginal Means (Wealth - Video)
```{r}
# Main effect of Trait_Exaggeration
emmeans_wealth_fact_vid_trait <- emmeans(model_wealth_factorial_video, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_wealth_fact_vid_trait)

# Main effect of Cost
emmeans_wealth_fact_vid_cost <- emmeans(model_wealth_factorial_video, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_wealth_fact_vid_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_wealth_fact_vid_interact <- emmeans(model_wealth_factorial_video, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_wealth_fact_vid_interact)
```

Pairwise Comparisons (Wealth - Video)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_wealth_fact_vid_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_wealth_fact_vid_interact2 <- emmeans(model_wealth_factorial_video, ~ Cost | Trait_Exaggeration)
pairs(emmeans_wealth_fact_vid_interact2, adjust = "tukey")
```

R-squared for Wealth Model (Video - 2×2)
```{r}
r_squared_wealth_fact_vid <- r.squaredGLMM(model_wealth_factorial_video)
print(r_squared_wealth_fact_vid)

R2m_wealth_fact_vid <- r_squared_wealth_fact_vid[1, "R2m"]
R2c_wealth_fact_vid <- r_squared_wealth_fact_vid[1, "R2c"]

cat("Wealth Model (Video) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth_fact_vid, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth_fact_vid, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth_fact_vid - R2m_wealth_fact_vid, 4), "\n")
```

## 16. Visualization of 2×2 Factorial Effects
### 16.1 Interaction Plots for All Models


```{r fig.width=7, fig.height=6, out.width="100%", fig.align='center'}
# Prepare data for plotting
prepare_factorial_plot_data <- function(emmeans_obj, dimension, stimuli) {
  df <- as.data.frame(emmeans_obj)
  df$Dimension <- dimension
  df$Stimuli_Type <- stimuli
  return(df)
}

# Attractiveness - Image
attract_img_plot <- prepare_factorial_plot_data(emmeans_attract_fact_img_interact, 
                                                "Attractiveness", "Image")
# Attractiveness - Video
attract_vid_plot <- prepare_factorial_plot_data(emmeans_attract_fact_vid_interact, 
                                                "Attractiveness", "Video")
# Wealth - Image
wealth_img_plot <- prepare_factorial_plot_data(emmeans_wealth_fact_img_interact, 
                                               "Wealth", "Image")
# Wealth - Video
wealth_vid_plot <- prepare_factorial_plot_data(emmeans_wealth_fact_vid_interact, 
                                               "Wealth", "Video")

# Combine all data
factorial_combined <- rbind(attract_img_plot, attract_vid_plot, 
                           wealth_img_plot, wealth_vid_plot)

# Create comprehensive interaction plot
p_factorial_all <- ggplot(factorial_combined, 
                         aes(x = Trait_Exaggeration, y = emmean, 
                             color = Cost, group = Cost,
                             shape = Cost, linetype = Cost)) +
  geom_line(size = 1, position = position_dodge(width = 0.1)) +
  geom_point(size = 3, position = position_dodge(width = 0.1)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0.15, size = 0.7,
                position = position_dodge(width = 0.1)) +
  facet_grid(Dimension ~ Stimuli_Type, scales = "free_y") +
  scale_color_manual(values = c("Economy" = "#D95F02", "Luxury" = "#7570B3"),
                    name = "Cost") +
  scale_shape_manual(values = c("Economy" = 16, "Luxury" = 17),
                    name = "Cost") +
  scale_linetype_manual(values = c("Economy" = "solid", "Luxury" = "dashed"),
                       name = "Cost") +
  labs(x = "Trait Exaggeration",
       y = "Estimated Mean Rating",
       title = "2×2 Factorial Effects: Trait Exaggeration × Cost",
       caption = "Error bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    strip.background = element_rect(fill = "grey95", color = "black", size = 0.8),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.caption = element_text(hjust = 1, color = "grey40")
  )

print(p_factorial_all)

# Save the plot
ggsave("factorial_2x2_interaction_plot.png", p_factorial_all,
      width = 12, height = 10, dpi = 300, bg = "white")
ggsave("factorial_2x2_interaction_plot.pdf", p_factorial_all,
      width = 12, height = 10, bg = "white")
```
Figure B4.1. Interaction between trait exaggeration (heel vs. flat) and cost (economy vs. luxury) across stimulus types and rating dimensions. Error bars represent 95% confidence intervals.


### 16.2 Main Effects Plots
```{r fig.width=7, fig.height=6, out.width="100%", fig.align='center'}
# Prepare main effects data
create_main_effects_data <- function() {
  # Trait Exaggeration effects
  trait_data <- rbind(
    data.frame(as.data.frame(emmeans_attract_fact_img_trait), 
               Dimension = "Attractiveness", Stimuli_Type = "Image", Factor = "Trait Exaggeration"),
    data.frame(as.data.frame(emmeans_attract_fact_vid_trait), 
               Dimension = "Attractiveness", Stimuli_Type = "Video", Factor = "Trait Exaggeration"),
    data.frame(as.data.frame(emmeans_wealth_fact_img_trait), 
               Dimension = "Wealth", Stimuli_Type = "Image", Factor = "Trait Exaggeration"),
    data.frame(as.data.frame(emmeans_wealth_fact_vid_trait), 
               Dimension = "Wealth", Stimuli_Type = "Video", Factor = "Trait Exaggeration")
  )
  trait_data$Level <- trait_data$Trait_Exaggeration
  
  # Cost effects
  cost_data <- rbind(
    data.frame(as.data.frame(emmeans_attract_fact_img_cost), 
               Dimension = "Attractiveness", Stimuli_Type = "Image", Factor = "Cost"),
    data.frame(as.data.frame(emmeans_attract_fact_vid_cost), 
               Dimension = "Attractiveness", Stimuli_Type = "Video", Factor = "Cost"),
    data.frame(as.data.frame(emmeans_wealth_fact_img_cost), 
               Dimension = "Wealth", Stimuli_Type = "Image", Factor = "Cost"),
    data.frame(as.data.frame(emmeans_wealth_fact_vid_cost), 
               Dimension = "Wealth", Stimuli_Type = "Video", Factor = "Cost")
  )
  cost_data$Level <- cost_data$Cost
  
  # Combine
  main_effects_data <- rbind(
    trait_data[, c("emmean", "SE", "asymp.LCL", "asymp.UCL", "Dimension", "Stimuli_Type", "Factor", "Level")],
    cost_data[, c("emmean", "SE", "asymp.LCL", "asymp.UCL", "Dimension", "Stimuli_Type", "Factor", "Level")]
  )
  
  return(main_effects_data)
}

main_effects_data <- create_main_effects_data()

# Plot main effects
p_main_effects <- ggplot(main_effects_data, 
                        aes(x = Level, y = emmean, 
                            color = Stimuli_Type, group = Stimuli_Type)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0.15, size = 0.7) +
  facet_grid(Dimension ~ Factor, scales = "free") +
  scale_color_manual(values = c("Image" = "#1B9E77", "Video" = "#D95F02"),
                    name = "Stimulus Type") +
  labs(x = "Factor Level",
       y = "Estimated Mean Rating",
       title = "Main Effects of Trait Exaggeration and Cost",
       caption = "Error bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    strip.background = element_rect(fill = "grey95", color = "black", size = 0.8),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.caption = element_text(hjust = 1, color = "grey40")
  )

print(p_main_effects)

# Save the plot
ggsave("factorial_2x2_main_effects.png", p_main_effects,
       width = 12, height = 8, dpi = 300, bg = "white")
ggsave("factorial_2x2_main_effects.pdf", p_main_effects,
       width = 12, height = 8, bg = "white")
```
Figure B4.2. Main effects of cost and trait exaggeration across stimulus types for attractiveness and wealth ratings. Error bars represent 95% confidence intervals.


## 17. Effect Size Analysis for 2×2 Factorial Models

### 17.1. Function to Calculate Cohen's d from emmeans
```{r}
# Function to calculate Cohen's d for pairwise comparisons
calculate_cohens_d <- function(emmeans_obj, model_obj) {
  # Get pairwise comparisons
  pairs_result <- pairs(emmeans_obj, adjust = "none")
  pairs_df <- as.data.frame(pairs_result)
  
  # Extract residual standard deviation from model
  sigma_resid <- sigma(model_obj)
  
  # Calculate Cohen's d for each comparison
  pairs_df$cohens_d <- pairs_df$estimate / sigma_resid
  
  # Classify effect sizes
  pairs_df$effect_size_label <- cut(abs(pairs_df$cohens_d),
                                    breaks = c(0, 0.2, 0.5, 0.8, Inf),
                                    labels = c("Negligible", "Small", "Medium", "Large"),
                                    right = FALSE)
  
  return(pairs_df)
}
```

### 17.2 Calculate Effect Sizes for All Models
```{r}
# Attractiveness - Image
cat("\n=== ATTRACTIVENESS - IMAGE STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_attract_img_trait <- calculate_cohens_d(emmeans_attract_fact_img_trait, 
                                          model_attract_factorial_image)
print(d_attract_img_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_attract_img_cost <- calculate_cohens_d(emmeans_attract_fact_img_cost, 
                                         model_attract_factorial_image)
print(d_attract_img_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_attract_img_simple <- calculate_cohens_d(emmeans_attract_fact_img_interact, 
                                           model_attract_factorial_image)
print(d_attract_img_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

# Attractiveness - Video
cat("\n\n=== ATTRACTIVENESS - VIDEO STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_attract_vid_trait <- calculate_cohens_d(emmeans_attract_fact_vid_trait, 
                                          model_attract_factorial_video)
print(d_attract_vid_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_attract_vid_cost <- calculate_cohens_d(emmeans_attract_fact_vid_cost, 
                                         model_attract_factorial_video)
print(d_attract_vid_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_attract_vid_simple <- calculate_cohens_d(emmeans_attract_fact_vid_interact, 
                                           model_attract_factorial_video)
print(d_attract_vid_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

# Wealth - Image
cat("\n\n=== WEALTH - IMAGE STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_wealth_img_trait <- calculate_cohens_d(emmeans_wealth_fact_img_trait, 
                                         model_wealth_factorial_image)
print(d_wealth_img_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_wealth_img_cost <- calculate_cohens_d(emmeans_wealth_fact_img_cost, 
                                        model_wealth_factorial_image)
print(d_wealth_img_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_wealth_img_simple <- calculate_cohens_d(emmeans_wealth_fact_img_interact, 
                                          model_wealth_factorial_image)
print(d_wealth_img_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

# Wealth - Video
cat("\n\n=== WEALTH - VIDEO STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_wealth_vid_trait <- calculate_cohens_d(emmeans_wealth_fact_vid_trait, 
                                         model_wealth_factorial_video)
print(d_wealth_vid_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_wealth_vid_cost <- calculate_cohens_d(emmeans_wealth_fact_vid_cost, 
                                        model_wealth_factorial_video)
print(d_wealth_vid_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_wealth_vid_simple <- calculate_cohens_d(emmeans_wealth_fact_vid_interact, 
                                          model_wealth_factorial_video)
print(d_wealth_vid_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])
```

### 17.3 Partial Eta-Squared from ANOVA Tables
```{r}
# Function to extract and format ANOVA with effect sizes
format_anova_with_effect_sizes <- function(model_obj, model_name) {
  anova_result <- anova(model_obj)
  
  # Calculate partial eta-squared
  anova_result$partial_eta_sq <- anova_result$`Sum Sq` / 
    (anova_result$`Sum Sq` + sum(residuals(model_obj)^2))
  
  # Classify effect sizes
  anova_result$effect_size_label <- cut(anova_result$partial_eta_sq,
                                        breaks = c(0, 0.01, 0.06, 0.14, 1),
                                        labels = c("Negligible", "Small", "Medium", "Large"),
                                        right = FALSE)
  
  cat("\n===", model_name, "===\n")
  print(anova_result[, c("Sum Sq", "Mean Sq", "NumDF", "DenDF", "F value", 
                         "Pr(>F)", "partial_eta_sq", "effect_size_label")])
  
  return(anova_result)
}

# Calculate for all models
eta_attract_img <- format_anova_with_effect_sizes(model_attract_factorial_image, 
                                                   "Attractiveness - Image")
eta_attract_vid <- format_anova_with_effect_sizes(model_attract_factorial_video, 
                                                   "Attractiveness - Video")
eta_wealth_img <- format_anova_with_effect_sizes(model_wealth_factorial_image, 
                                                  "Wealth - Image")
eta_wealth_vid <- format_anova_with_effect_sizes(model_wealth_factorial_video, 
                                                  "Wealth - Video")
```


### 17.4 Comprehensive Summary Table of Effect Sizes
```{r}
# Create a detailed summary table
effect_size_summary <- data.frame(
  Model = c(
    "Attractiveness - Image",
    "Attractiveness - Image", 
    "Attractiveness - Image",
    "Attractiveness - Video",
    "Attractiveness - Video",
    "Attractiveness - Video",
    "Wealth - Image",
    "Wealth - Image",
    "Wealth - Image",
    "Wealth - Video",
    "Wealth - Video",
    "Wealth - Video"
  ),
  Effect = c(
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)",
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)",
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)",
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)"
  ),
  Raw_Difference = c(
    0.325, 0.036, NA,
    -0.183, -0.193, NA,
    0.504, 0.100, NA,
    0.302, -0.051, NA
  ),
  Cohens_d = c(
    0.28, 0.03, NA,
    -0.14, -0.15, NA,
    0.49, 0.10, NA,
    0.25, -0.04, NA
  ),
  Partial_Eta_Sq = c(
    0.0207, 0.0003, 0.0006,
    0.0052, 0.0058, 0.0032,
    0.0601, 0.0025, 0.0018,
    0.0159, 0.0005, 0.0062
  )
)

print(effect_size_summary)

```

### 17.5 Simple Effects Summary for Key Comparisons
```{r}
simple_effects_summary <- data.frame(
  Model = c(
    "Attractiveness - Image: Economy",
    "Attractiveness - Image: Luxury",
    "Attractiveness - Video: Economy",
    "Attractiveness - Video: Luxury",
    "Wealth - Image: Economy",
    "Wealth - Image: Luxury",
    "Wealth - Video: Economy",
    "Wealth - Video: Luxury"
  ),
  Comparison = rep("Heel vs Flat", 8),
  Raw_Difference_Heel_Higher = c(
    0.379, 0.271,  # Attractiveness - Image (heels rated higher)
    -0.041, -0.325,    # Attractiveness - Video (mixed: flat higher in economy, heel higher in luxury)
    0.589, 0.420,  # Wealth - Image (heels rated higher)
    0.490, 0.115   # Wealth - Video (heels rated higher)
  ),
  Cohens_d_abs = c(
    0.33, 0.24,
    0.03, 0.25,
    0.57, 0.41,
    0.40, 0.09
  ),
  Effect_Size_Label = c(
    "Small", "Small",
    "Negligible", "Small",
    "Medium", "Small",
    "Small", "Negligible"
  ),
  p_value = c(
    8.31e-18, 8.13e-10,
    4.15e-01, 6.60e-11,
    1.49e-50, 1.68e-26,
    1.58e-25, 1.43e-02
  ),
  Interpretation = c(
    "Heels INCREASE attractiveness noticeably in images (Economy)",
    "Heels INCREASE attractiveness noticeably in images (Luxury)",
    "No meaningful difference in videos (Economy)",
    "Heels INCREASE attractiveness slightly in videos (Luxury)",
    "Heels SUBSTANTIALLY INCREASE wealth perception in images (Economy)",
    "Heels INCREASE wealth perception in images (Luxury)",
    "Heels INCREASE wealth perception in videos (Economy)",
    "Minimal difference in videos (Luxury)"
  )
)

print(simple_effects_summary)
#write.csv(simple_effects_summary, "simple_effects_summary.csv", row.names = FALSE)
```

### 17.6 Visualization: Effect Sizes Across Models
```{r ig.width=15, fig.height=10, fig.align='center', dpi=300, out.width='80%'}
# Create a comprehensive effect size visualization
# Prepare data for main effects visualization
main_effects_es <- data.frame(
  Model = rep(c("Attract-Image", "Attract-Video", "Wealth-Image", "Wealth-Video"), each = 2),
  Effect = rep(c("Trait Exaggeration", "Cost"), 4),
  Partial_Eta_Sq = c(
    0.0207, 0.0003,  # Attractiveness - Image
    0.0052, 0.0058,  # Attractiveness - Video
    0.0601, 0.0025,  # Wealth - Image
    0.0159, 0.0005   # Wealth - Video
  ),
  Cohens_d = c(
    -0.28, -0.03,
    0.14, 0.15,
    -0.49, -0.10,
    -0.25, 0.04
  )
)

# Add effect size categories
main_effects_es$ES_Category <- cut(main_effects_es$Partial_Eta_Sq,
                                   breaks = c(0, 0.01, 0.06, 0.14, 1),
                                   labels = c("Negligible", "Small", "Medium", "Large"))

# Plot 1: Partial Eta-Squared
p1 <- ggplot(main_effects_es, aes(x = Model, y = Partial_Eta_Sq, fill = ES_Category)) +
  geom_col(position = position_dodge(0.8), width = 0.7, color = "black") +
  geom_hline(yintercept = c(0.01, 0.06, 0.14), linetype = "dashed", color = "red", alpha = 0.5) +
  facet_wrap(~ Effect) +
  scale_fill_manual(values = c("Negligible" = "#999999", 
                               "Small" = "#E69F00", 
                               "Medium" = "#56B4E9", 
                               "Large" = "#009E73"),
                    name = "Effect Size",
                    drop = FALSE) +
  labs(title = "Partial Eta squared by Model and Effect Type",
       y = "Partial Eta squared",
       x = "Model") +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    panel.border = element_rect(color = "black", fill = NA),
    strip.background = element_rect(fill = "grey90", color = "black"),
    strip.text = element_text(face = "bold")
  ) +
  annotate("text", x = 0.5, y = 0.01, label = "Small", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.06, label = "Medium", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.14, label = "Large", hjust = 0, size = 3, color = "red")

print(p1)
```
Figure B4.3. Partial eta-squared (η²) effect sizes for main effects across all 2×2 factorial models. Dashed reference lines indicate small (0.01), medium (0.06), and large (0.14) effect size thresholds.

```{r ig.width=15, fig.height=10, fig.align='center', dpi=300, out.width='80%'}
# Plot 2: Cohen's d
p2 <- ggplot(main_effects_es, aes(x = Model, y = abs(Cohens_d), fill = Effect)) +
  geom_col(position = position_dodge(0.8), width = 0.7, color = "black") +
  geom_hline(yintercept = c(0.2, 0.5, 0.8), linetype = "dashed", color = "red", alpha = 0.5) +
  scale_fill_manual(values = c("Trait Exaggeration" = "#1F77B4", 
                               "Cost" = "#FF7F0E"),
                    name = "Effect Type") +
  labs(title = "Cohen's d (Absolute Values) by Model",
       y = "|Cohen's d|",
       x = "Model") +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    panel.border = element_rect(color = "black", fill = NA)
  ) +
  annotate("text", x = 0.5, y = 0.2, label = "Small", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.5, label = "Medium", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.8, label = "Large", hjust = 0, size = 3, color = "red")

print(p2)

# Save
#ggsave("effect_sizes_comparison.png", 
#       arrangeGrob(p1, p2, ncol = 1),
#       width = 14, height = 10, dpi = 300, bg = "white")
```
Figure B4.4. Cohen's d effect sizes (absolute values) for cost and trait exaggeration main effects across all models. Dashed reference lines indicate small (0.2), medium (0.5), and large (0.8) effect size thresholds.


## 18.  Variance Components Analysis
```{r}

# Function to calculate variance components percentage
calculate_variance_components <- function(model) {
  # Extract random effects variance components
  vc <- as.data.frame(VarCorr(model))
  
# Get fixed effects variance 
  # Calculate residual variance and total variance
  residual_var <- vc$vcov[vc$grp == "Residual"]
  random_vars <- vc$vcov[vc$grp != "Residual"]
  fixed_var <- get_variance_fixed(model)
  total_var <- sum(c(random_vars, residual_var, fixed_var))
  
  # Calculate the percentage for each component
  var_components <- data.frame(
    Component = c(vc$grp[vc$grp != "Residual"], "Fixed Effects", "Residual"),
    Variance = c(random_vars, fixed_var, residual_var),
    Percentage = c(random_vars, fixed_var, residual_var) / total_var * 100
  )
  
  # Round and sort by percentage
  var_components$Percentage <- round(var_components$Percentage, 2)
  var_components <- var_components[order(var_components$Percentage, decreasing = TRUE), ]
  
  return(var_components)
}

# Apply the function to attractiveness and wealth models with interaction
cat("\n============================================================\n")
cat("VARIANCE COMPONENTS ANALYSIS\n")
cat("============================================================\n\n")

cat("ATTRACTIVENESS MODEL VARIANCE COMPONENTS:\n")
attract_components <- calculate_variance_components(model_attract_interact)
print(attract_components)

# Calculate total variance explained by subject (code) vs stimuli structure (block/Model)
rater_variance <- sum(attract_components$Percentage[attract_components$Component == "code"])
stimuli_variance <- sum(attract_components$Percentage[attract_components$Component %in% c("block", "Model:block")])

cat("\nPercentage of variation explained by:\n")
cat("- Individual differences between raters:", rater_variance, "%\n")
cat("- Stimuli structure (block/Model nested):", stimuli_variance, "%\n")
cat("- Fixed effects (experimental conditions):", 
    attract_components$Percentage[attract_components$Component == "Fixed Effects"], "%\n")
cat("- Unexplained variation (residual):", 
    attract_components$Percentage[attract_components$Component == "Residual"], "%\n\n")

cat("WEALTH MODEL VARIANCE COMPONENTS:\n")
wealth_components <- calculate_variance_components(model_wealth_interact)
print(wealth_components)

# Calculate total variance explained by subject (code) vs stimuli structure (block/Model)
rater_variance <- sum(wealth_components$Percentage[wealth_components$Component == "code"])
stimuli_variance <- sum(wealth_components$Percentage[wealth_components$Component %in% c("block", "Model:block")])

cat("\nPercentage of variation explained by:\n")
cat("- Individual differences between raters:", rater_variance, "%\n")
cat("- Stimuli structure (block/Model nested):", stimuli_variance, "%\n")
cat("- Fixed effects (experimental conditions):", 
    wealth_components$Percentage[wealth_components$Component == "Fixed Effects"], "%\n")
cat("- Unexplained variation (residual):", 
    wealth_components$Percentage[wealth_components$Component == "Residual"], "%\n\n")

# Apply to the split models as well
cat("ATTRACTIVENESS MODEL - IMAGES ONLY:\n")
attract_image_components <- calculate_variance_components(model_attract_image)
print(attract_image_components)

cat("\nATTRACTIVENESS MODEL - VIDEOS ONLY:\n")
attract_video_components <- calculate_variance_components(model_attract_video)
print(attract_video_components)

cat("\nWEALTH MODEL - IMAGES ONLY:\n")
wealth_image_components <- calculate_variance_components(model_wealth_image)
print(wealth_image_components)

cat("\nWEALTH MODEL - VIDEOS ONLY:\n")
wealth_video_components <- calculate_variance_components(model_wealth_video)
print(wealth_video_components)

# Create a summary table for comparison
variance_summary <- data.frame(
  Model = c("Attract - Full", "Attract - Image", "Attract - Video", 
            "Wealth - Full", "Wealth - Image", "Wealth - Video"),
  Rater_Variance = c(
    sum(attract_components$Percentage[attract_components$Component == "code"]),
    sum(attract_image_components$Percentage[attract_image_components$Component == "code"]),
    sum(attract_video_components$Percentage[attract_video_components$Component == "code"]),
    sum(wealth_components$Percentage[wealth_components$Component == "code"]),
    sum(wealth_image_components$Percentage[wealth_image_components$Component == "code"]),
    sum(wealth_video_components$Percentage[wealth_video_components$Component == "code"])
  ),
  Stimuli_Variance = c(
    sum(attract_components$Percentage[attract_components$Component %in% c("block", "Model:block")]),
    sum(attract_image_components$Percentage[attract_image_components$Component %in% c("block", "Model:block")]),
    sum(attract_video_components$Percentage[attract_video_components$Component %in% c("block", "Model:block")]),
    sum(wealth_components$Percentage[wealth_components$Component %in% c("block", "Model:block")]),
    sum(wealth_image_components$Percentage[wealth_image_components$Component %in% c("block", "Model:block")]),
    sum(wealth_video_components$Percentage[wealth_video_components$Component %in% c("block", "Model:block")])
  ),
  Fixed_Effects = c(
    attract_components$Percentage[attract_components$Component == "Fixed Effects"],
    attract_image_components$Percentage[attract_image_components$Component == "Fixed Effects"],
    attract_video_components$Percentage[attract_video_components$Component == "Fixed Effects"],
    wealth_components$Percentage[wealth_components$Component == "Fixed Effects"],
    wealth_image_components$Percentage[wealth_image_components$Component == "Fixed Effects"],
    wealth_video_components$Percentage[wealth_video_components$Component == "Fixed Effects"]
  ),
  Residual = c(
    attract_components$Percentage[attract_components$Component == "Residual"],
    attract_image_components$Percentage[attract_image_components$Component == "Residual"],
    attract_video_components$Percentage[attract_video_components$Component == "Residual"],
    wealth_components$Percentage[wealth_components$Component == "Residual"],
    wealth_image_components$Percentage[wealth_image_components$Component == "Residual"],
    wealth_video_components$Percentage[wealth_video_components$Component == "Residual"]
  )
)

# Round values for display
variance_summary[, 2:5] <- round(variance_summary[, 2:5], 2)

cat("\n============================================================\n")
cat("VARIANCE COMPONENTS SUMMARY ACROSS MODELS\n")
cat("============================================================\n\n")
print(variance_summary)

```


