---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,tidy = TRUE,
  tidy.opts = list(width.cutoff = 60),
  out.width = "100%")
```

# **Supplement Section B: Inferential statistics**

## In this document;

##  **• B1:** Comprehensive models with exploratory variables and variable exclusion process
##  **•	B2:** Unsplit models (without stimulus type separation) 
##  **•	B3:** Complete models including control condition 
##  **•	B4:** Factorial 2x2 models
##  **•	B5:** Normality assessments and Model assumptions
##  **•	B6:** Power Analysis
##  **•	B7:** Expected vs. Observed ratings of item photographs

#### **In the .Pdf output file you may find only the outputs generated by the analysis code, in order to keep the supplementary files as concise as possible. However the full code is available on https://github.com/Rezvani-S/Costly-Beauty-ShoeStudy.git**


## 1. Required Packages

```{r}
library(haven)         
library(lme4)           
library(lmerTest)       
library(emmeans)       
library(ggplot2)        
library(dplyr)          
library(ggsignif)
library(MuMIn)          
library(reshape2)
library(gridExtra)
library(effectsize)  
library(ggpattern)
library(gridExtra)
library(grid)
library(insight)
library(car)
library(lattice)
library(tidyr)
library(simr)
library(knitr)
```

## 2. Data Import and Preparation

```{r}
# Reading data file
body_data <-  read.csv("Ratings_data_Shoes_longFormat.csv")

# converting to data frame
body_data <- as.data.frame(body_data)

# Condition (5 levels) converted to factor
body_data$Condition <- factor(body_data$Condition,
                              levels = 1:5,
                              labels = c("Control", 
                                         "Economy Flat",
                                         "Economy Heel", 
                                         "Luxury Flat",
                                         "Luxury Heel"))

# Dimension (2 levels) converted to factor
body_data$Dimension <- factor(body_data$Dimension,
                              levels = 1:2,
                              labels = c("Attractiveness",
                                         "Wealth"))

# Stimuli_Type (2 levels) converted to factor
body_data$Stimuli_Type <- factor(body_data$Stimuli_Type,
                                levels = 1:2,
                                labels = c("Image", 
                                           "Video"))

# Converting empty Income strings to NA
body_data$monthlyincome[body_data$monthlyincome == ""] <- NA
# Then convert to ordered factor with the existing labels
body_data$monthlyincome <- factor(body_data$monthlyincome,
                                 levels = c("up to 15 000 CZK/month",
                                           "15 000-30 000 CZK/month", 
                                           "30 000-50 000 CZK/month",
                                           "over 50 000 CZK/month"),
                                 ordered = TRUE)

# Sex converted to factor
body_data$sex <- factor(body_data$sex,
                        labels = c("Female", "Male"))

# Fixing variable names
names(body_data)[names(body_data) == "rating"] <- "Rating"
names(body_data)[names(body_data) == "Block"] <- "block"
names(body_data)[names(body_data) == "Code"] <- "code"

# The Brand scores were read
# Using the merged knowledge scores
bscore_df <- read.csv("merged_knowledge_scores.csv")

# Only the variables needed were selected from bscore
bscore_subset <- bscore_df[, c("code", "consistency_score", 
                               "merged_score_zscore")]

# The variable "code" was renamed to "Code" to match in both datasets
names(bscore_subset)[names(bscore_subset) == "code"] <- "code"

# The datasets were merged by code
body_data <- merge(body_data, bscore_subset, by = "code", all.x = TRUE)
```

## **PART I:  Supplement B1: Comprehensive models with exploratory variables and variable exclusion process **

## 3. Data Cleaning and Preparation
```{r}
# Rows with NA in relevant columns were removed
body_df_clean <- body_data[complete.cases(body_data[, c("Rating", "Dimension", "Condition", 
                                            "Model", "block", "code", "sex", 
                                            "monthlyincome", "merged_score_zscore", 
                                            "Stimuli_Type")]), ]

# Factors were properly formatted
body_df_clean$Model <- as.factor(body_df_clean$Model)
body_df_clean$block <- as.factor(body_df_clean$block)
body_df_clean$code <- as.factor(body_df_clean$code)

# Block:model interaction for nested structure was created
body_df_clean$block_model <- interaction(body_df_clean$block, body_df_clean$Model)

# Data was split into two dimensions
body_df_attract <- body_df_clean[body_df_clean$Dimension == "Attractiveness", ]
body_df_wealth <- body_df_clean[body_df_clean$Dimension == "Wealth", ]
```

## 4. Comprehensive Attractiveness Model

A comprehensive linear mixed-effects model for attractiveness was constructed, including all potential variables:

```{r}
# Comprehensive model for attractiveness including additional variables
model_attract_comp <- lmer(Rating ~ Condition + sex + monthlyincome + 
                           merged_score_zscore + Stimuli_Type + 
                           (1|block/Model) + (1|code), 
                          data = body_df_attract)

# Model summary was generated
summary(model_attract_comp)
```

### ANOVA for Fixed Effects in Attractiveness Model

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_comp)
```

### Random Effects for Attractiveness Model

```{r}
# Random effects variance was extracted
cat("Random Effects Variance for Comprehensive Attractiveness Model:\n")
print(VarCorr(model_attract_comp))
```

## 5. Comprehensive Wealth Model

A comprehensive linear mixed-effects model for wealth was constructed, including all potential variables:

```{r}
# Comprehensive model for wealth including additional variables
model_wealth_comp <- lmer(Rating ~ Condition + sex + monthlyincome + 
                          merged_score_zscore + Stimuli_Type + 
                          (1|block/Model) + (1|code), 
                         data = body_df_wealth)

# Model summary was generated
summary(model_wealth_comp)
```

### ANOVA for Fixed Effects in Wealth Model

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_comp)
```

### Random Effects for Wealth Model

```{r}
# Random effects variance was extracted
cat("Random Effects Variance for Comprehensive Wealth Model:\n")
print(VarCorr(model_wealth_comp))
```

## 6. Model Comparison: Testing Variable Contributions

To assess the contribution of each additional variable, stepwise comparisons were conducted by removing one variable at a time:

### 6.1 Testing Sex Contribution

```{r}
# Models without sex
model_attract_no_sex <- lmer(Rating ~ Condition + monthlyincome + 
                             merged_score_zscore + Stimuli_Type + 
                             (1|block/Model) + (1|code), 
                            data = body_df_attract)

model_wealth_no_sex <- lmer(Rating ~ Condition + monthlyincome + 
                           merged_score_zscore + Stimuli_Type + 
                           (1|block/Model) + (1|code), 
                          data = body_df_wealth)

# Model comparison for attractiveness
cat("Sex contribution to Attractiveness model:\n")
anova(model_attract_no_sex, model_attract_comp)

# Model comparison for wealth
cat("\nSex contribution to Wealth model:\n")
anova(model_wealth_no_sex, model_wealth_comp)
```

### 6.2 Testing Monthly Income Contribution

```{r}
# Models without monthly income
model_attract_no_income <- lmer(Rating ~ Condition + sex + 
                               merged_score_zscore + Stimuli_Type + 
                               (1|block/Model) + (1|code), 
                              data = body_df_attract)

model_wealth_no_income <- lmer(Rating ~ Condition + sex + 
                              merged_score_zscore + Stimuli_Type + 
                              (1|block/Model) + (1|code), 
                             data = body_df_wealth)

# Model comparison for attractiveness
cat("Monthly Income contribution to Attractiveness model:\n")
anova(model_attract_no_income, model_attract_comp)

# Model comparison for wealth
cat("\nMonthly Income contribution to Wealth model:\n")
anova(model_wealth_no_income, model_wealth_comp)
```

### 6.3 Testing Brand Knowledge Score Contribution

```{r}
# Models without brand knowledge score
model_attract_no_brand <- lmer(Rating ~ Condition + sex + monthlyincome + 
                              Stimuli_Type + (1|block/Model) + (1|code), 
                             data = body_df_attract)

model_wealth_no_brand <- lmer(Rating ~ Condition + sex + monthlyincome + 
                             Stimuli_Type + (1|block/Model) + (1|code), 
                            data = body_df_wealth)

# Model comparison for attractiveness
cat("Brand Knowledge Score contribution to Attractiveness model:\n")
anova(model_attract_no_brand, model_attract_comp)

# Model comparison for wealth
cat("\nBrand Knowledge Score contribution to Wealth model:\n")
anova(model_wealth_no_brand, model_wealth_comp)
```

### 6.4 Testing Stimuli Type Contribution

```{r}
# Models without stimuli type
model_attract_no_stimuli <- lmer(Rating ~ Condition + sex + monthlyincome + 
                                merged_score_zscore + (1|block/Model) + (1|code), 
                               data = body_df_attract)

model_wealth_no_stimuli <- lmer(Rating ~ Condition + sex + monthlyincome + 
                               merged_score_zscore + (1|block/Model) + (1|code), 
                              data = body_df_wealth)

# Model comparison for attractiveness
cat("Stimuli Type contribution to Attractiveness model:\n")
anova(model_attract_no_stimuli, model_attract_comp)

# Model comparison for wealth
cat("\nStimuli Type contribution to Wealth model:\n")
anova(model_wealth_no_stimuli, model_wealth_comp)
```

### 6.5 Testing Model (nested in block) Contribution

```{r}
# Models with only block (without nested Model)
model_attract_no_nested <- lmer(Rating ~ Condition + sex + monthlyincome + 
                               merged_score_zscore + Stimuli_Type + 
                               (1|block) + (1|code), 
                              data = body_df_attract)

model_wealth_no_nested <- lmer(Rating ~ Condition + sex + monthlyincome + 
                              merged_score_zscore + Stimuli_Type + 
                              (1|block) + (1|code), 
                             data = body_df_wealth)

# Model comparison for attractiveness
cat("Nested Model contribution to Attractiveness model:\n")
anova(model_attract_no_nested, model_attract_comp)

# Model comparison for wealth
cat("\nNested Model contribution to Wealth model:\n")
anova(model_wealth_no_nested, model_wealth_comp)
```

## 7. AIC and BIC Comparison for Model Selection

To further evaluate model selection, AIC and BIC values were compared between the comprehensive and simplified models:

```{r}
# Simplified models
model_attract_simple <- lmer(Rating ~ Condition + (1|block) + (1|code), 
                            data = body_df_attract)

model_wealth_simple <- lmer(Rating ~ Condition + (1|block) + (1|code), 
                           data = body_df_wealth)

# AIC and BIC comparison for attractiveness
cat("AIC and BIC comparison for Attractiveness models:\n")
AIC_BIC_attract <- data.frame(
  Model = c("Comprehensive", "Simple"),
  AIC = c(AIC(model_attract_comp), AIC(model_attract_simple)),
  BIC = c(BIC(model_attract_comp), BIC(model_attract_simple))
)
print(AIC_BIC_attract)

# AIC and BIC comparison for wealth
cat("\nAIC and BIC comparison for Wealth models:\n")
AIC_BIC_wealth <- data.frame(
  Model = c("Comprehensive", "Simple"),
  AIC = c(AIC(model_wealth_comp), AIC(model_wealth_simple)),
  BIC = c(BIC(model_wealth_comp), BIC(model_wealth_simple))
)
print(AIC_BIC_wealth)
```

## **PART II:  Supplement B2: Unsplit models (without stimulus type separation)**

### Data Cleaning and Preparation
```{r}
# Rows with NA in relevant columns were removed
body_df_clean <- body_data[complete.cases(body_data[, c("Rating", "Dimension", "Condition", 
                                            "Model", "block", "code", "Stimuli_Type")]), ]

# Factors were properly formatted
body_df_clean$Model <- as.factor(body_df_clean$Model)
body_df_clean$block <- as.factor(body_df_clean$block)
body_df_clean$code <- as.factor(body_df_clean$code)

# Data was split into two dimensions
body_df_attract <- body_df_clean[body_df_clean$Dimension == "Attractiveness", ]
body_df_wealth <- body_df_clean[body_df_clean$Dimension == "Wealth", ]
```

## 8. Attractiveness Model with Interaction

A linear mixed-effects model for attractiveness was constructed including the interaction between Condition and Stimuli_Type:

```{r}
# Model for attractiveness with interaction
model_attract_interact <- lmer(Rating ~ Condition * Stimuli_Type + 
                              (1|block/Model) + (1|code), 
                              data = body_df_attract)

# Model summary was generated
summary(model_attract_interact)
```

### ANOVA for Fixed Effects in Attractiveness Model with Interaction

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_interact)
```

### Estimated Marginal Means for Condition by Stimuli_Type in Attractiveness Model

```{r}
# Estimated marginal means for Condition by Stimuli_Type interaction
emmeans_attract_interact <- emmeans(model_attract_interact, ~ Condition | Stimuli_Type)
print(emmeans_attract_interact)
```

### Calculate R-squared values for the attractiveness model
```{r}
r_squared_attract <- r.squaredGLMM(model_attract_interact)
print(r_squared_attract)

# Extract specific values
R2m_attract <- r_squared_attract[1, "R2m"]  # Marginal R²
R2c_attract <- r_squared_attract[1, "R2c"]  # Conditional R²

# Display results
cat("Attractiveness Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract, 4), "\n")
cat("Random effects contribution:", round(R2c_attract - R2m_attract, 4), "\n")
```

### Visualizing Attractiveness Results by Condition and Stimuli_Type

```{r, fig.width=10, fig.height=6}
# The results for Condition by Stimuli_Type interaction were plotted
attract_interact_results <- as.data.frame(emmeans_attract_interact)
p_attract_interact <- ggplot(attract_interact_results, aes(x=Condition, y=emmean, color=Stimuli_Type, group=Stimuli_Type)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Interaction of Condition and Stimuli Type on Attractiveness Ratings") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_attract_interact)
```
Figure B2.1. Interaction between footwear condition and stimulus type (image vs. video) on attractiveness ratings. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition by Stimuli_Type in Attractiveness Model

```{r}
# Pairwise comparisons for Condition within each Stimuli_Type
pairs(emmeans_attract_interact, adjust = "tukey")
```

## 9. Wealth Model with Interaction

A linear mixed-effects model for wealth was constructed including the interaction between Condition and Stimuli_Type:

```{r}
# Model for wealth with interaction
model_wealth_interact <- lmer(Rating ~ Condition * Stimuli_Type + 
                            (1|block/Model) + (1|code), 
                            data = body_df_wealth)

# Model summary was generated
summary(model_wealth_interact)
```

### ANOVA for Fixed Effects in Wealth Model with Interaction

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_interact)
```

### Estimated Marginal Means for Condition by Stimuli_Type in Wealth Model

```{r}
# Estimated marginal means for Condition by Stimuli_Type interaction
emmeans_wealth_interact <- emmeans(model_wealth_interact, ~ Condition | Stimuli_Type)
print(emmeans_wealth_interact)
```
### Calculate R-squared values for the wealth model
```{r}
r_squared_wealth <- r.squaredGLMM(model_wealth_interact)
print(r_squared_wealth)

# Extract specific values
R2m_wealth <- r_squared_wealth[1, "R2m"]  # Marginal R²
R2c_wealth <- r_squared_wealth[1, "R2c"]  # Conditional R²

# Display results
cat("Wealth Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth - R2m_wealth, 4), "\n")
```


### Visualizing Wealth Results by Condition and Stimuli_Type

```{r, fig.width=10, fig.height=6}
# The results for Condition by Stimuli_Type interaction were plotted
wealth_interact_results <- as.data.frame(emmeans_wealth_interact)
p_wealth_interact <- ggplot(wealth_interact_results, aes(x=Condition, y=emmean, color=Stimuli_Type, group=Stimuli_Type)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Interaction of Condition and Stimuli Type on Wealth Ratings") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_wealth_interact)
```
Figure B2.2. Interaction between footwear condition and stimulus type (image vs. video) on wealth perception ratings. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition by Stimuli_Type in Wealth Model

```{r}
# Pairwise comparisons for Condition within each Stimuli_Type
pairs(emmeans_wealth_interact, adjust = "tukey")
```

## 10. Combined Plot: Condition × Dimension × Stimuli_Type

A combined plot was created to visualize the interaction between Condition, Dimension, and Stimuli_Type:

```{r, fig.width=12, fig.height=8}
# Combine results from attractiveness and wealth models
combined_interact_results <- rbind(
  transform(attract_interact_results, Dimension = "Attractiveness"),
  transform(wealth_interact_results, Dimension = "Wealth")
)

# Create a comprehensive plot
p_combined_interact <- ggplot(combined_interact_results, aes(x=Condition, y=emmean, color=Dimension, group=interaction(Dimension, Stimuli_Type), linetype=Stimuli_Type)) +
  geom_point(position = position_dodge(width = 0.5), size = 3) +
  geom_line(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), position = position_dodge(width = 0.5), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "right") +
  ggtitle("Condition × Dimension × Stimuli Type Interaction") +
  xlab("Condition") +
  ylab("Estimated Mean Rating") +
  scale_linetype_manual(values = c("solid", "dashed")) +
  scale_color_manual(values = c("blue", "red"))

print(p_combined_interact)
```
Figure B2.3. Three-way interaction between footwear condition, dimension (attractiveness vs. wealth), and stimulus type. Solid lines represent image stimuli; dashed lines represent video stimuli. Error bars represent 95% confidence intervals.





## **PART III:  Supplement	B3: Complete models including control condition (Split by StimuliType)**

## 11. Models for Image Stimuli Only

```{r}
# Filter data for Image stimuli only
body_df_attract_image <- body_df_attract[body_df_attract$Stimuli_Type == "Image", ]
body_df_wealth_image <- body_df_wealth[body_df_wealth$Stimuli_Type == "Image", ]
```

### Attractiveness Model for Image Stimuli

```{r}
# Model for attractiveness - Image stimuli only
model_attract_image <- lmer(Rating ~ Condition + 
                           (1|block/Model) + (1|code), 
                           data = body_df_attract_image)

# Model summary was generated
summary(model_attract_image)
```

### ANOVA for Fixed Effects in Attractiveness Model (Image Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_image)
```

### Estimated Marginal Means for Condition in Attractiveness Model (Image Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_attract_image <- emmeans(model_attract_image, ~ Condition)
print(emmeans_attract_image)
```
### Calculate R-squared values for the attractiveness model
```{r}
r_squared_attract <- r.squaredGLMM(model_attract_image)
print(r_squared_attract)

# Extract specific values
R2m_attract <- r_squared_attract[1, "R2m"]  # Marginal R²
R2c_attract <- r_squared_attract[1, "R2c"]  # Conditional R²

# Display results
cat("Attractiveness Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract, 4), "\n")
cat("Random effects contribution:", round(R2c_attract - R2m_attract, 4), "\n")
```

### Visualizing Attractiveness Results for Image Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
attract_image_results <- as.data.frame(emmeans_attract_image)
p_attract_image <- ggplot(attract_image_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Attractiveness Ratings (Image Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_attract_image)
```
Figure B3.1. Effect of footwear conditions on attractiveness ratings for image stimuli, including control condition. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition in Attractiveness Model (Image Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_attract_image, adjust = "tukey")
```

### Wealth Model for Image Stimuli

```{r}
# Model for wealth - Image stimuli only
model_wealth_image <- lmer(Rating ~ Condition + 
                          (1|block/Model) + (1|code), 
                          data = body_df_wealth_image)

# Model summary was generated
summary(model_wealth_image)
```

### ANOVA for Fixed Effects in Wealth Model (Image Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_image)
```

### Estimated Marginal Means for Condition in Wealth Model (Image Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_wealth_image <- emmeans(model_wealth_image, ~ Condition)
print(emmeans_wealth_image)
```
### Calculate R-squared values for the wealth model
```{r}
r_squared_wealth <- r.squaredGLMM(model_wealth_image)
print(r_squared_wealth)

# Extract specific values
R2m_wealth <- r_squared_wealth[1, "R2m"]  # Marginal R²
R2c_wealth <- r_squared_wealth[1, "R2c"]  # Conditional R²

# Display results
cat("Wealth Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth - R2m_wealth, 4), "\n")
```

### Visualizing Wealth Results for Image Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
wealth_image_results <- as.data.frame(emmeans_wealth_image)
p_wealth_image <- ggplot(wealth_image_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Wealth Ratings (Image Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_wealth_image)
```
Figure B3.2. Effect of footwear conditions on wealth perception ratings for image stimuli, including control condition. Error bars represent 95% confidence intervals.


### Pairwise Comparisons for Condition in Wealth Model (Image Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_wealth_image, adjust = "tukey")
```

### Comparison Between Dimensions for Image Stimuli

```{r, fig.width=10, fig.height=6}
# Results from both dimensions were combined
combined_image_results <- rbind(
  transform(attract_image_results, Dimension = "Attractiveness"),
  transform(wealth_image_results, Dimension = "Wealth")
)

# The comparison plot was created
p_combined_image <- ggplot(combined_image_results, aes(x = Condition, y = emmean, color = Dimension, group = Dimension)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Comparison of Condition Effects Between Dimensions (Image Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_combined_image)
```
Figure B3.3. Comparison of footwear condition effects between attractiveness and wealth dimensions for image stimuli. Error bars represent 95% confidence intervals.


## 12. Models for Video Stimuli Only

Next, the data was filtered to include only Video stimuli:

```{r}
# Filter data for Video stimuli only
body_df_attract_video <- body_df_attract[body_df_attract$Stimuli_Type == "Video", ]
body_df_wealth_video <- body_df_wealth[body_df_wealth$Stimuli_Type == "Video", ]
```

### Attractiveness Model for Video Stimuli

```{r}
# Model for attractiveness - Video stimuli only
model_attract_video <- lmer(Rating ~ Condition + 
                           (1|block/Model) + (1|code), 
                           data = body_df_attract_video)

# Model summary was generated
summary(model_attract_video)
```

### ANOVA for Fixed Effects in Attractiveness Model (Video Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_attract_video)
```

### Estimated Marginal Means for Condition in Attractiveness Model (Video Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_attract_video <- emmeans(model_attract_video, ~ Condition)
print(emmeans_attract_video)
```
### Calculate R-squared values for the attractiveness model
```{r}
r_squared_attract <- r.squaredGLMM(model_attract_video)
print(r_squared_attract)

# Extract specific values
R2m_attract <- r_squared_attract[1, "R2m"]  # Marginal R²
R2c_attract <- r_squared_attract[1, "R2c"]  # Conditional R²

# Display results
cat("Attractiveness Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract, 4), "\n")
cat("Random effects contribution:", round(R2c_attract - R2m_attract, 4), "\n")
```

### Visualizing Attractiveness Results for Video Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
attract_video_results <- as.data.frame(emmeans_attract_video)
p_attract_video <- ggplot(attract_video_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Attractiveness Ratings (Video Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_attract_video)
```
Figure B3.4. Effect of footwear conditions on attractiveness ratings for video stimuli, including control condition. Error bars represent 95% confidence intervals.


### Pairwise Comparisons for Condition in Attractiveness Model (Video Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_attract_video, adjust = "tukey")
```

### Wealth Model for Video Stimuli

```{r}
# Model for wealth - Video stimuli only
model_wealth_video <- lmer(Rating ~ Condition + 
                          (1|block/Model) + (1|code), 
                          data = body_df_wealth_video)

# Model summary was generated
summary(model_wealth_video)
```

### ANOVA for Fixed Effects in Wealth Model (Video Stimuli)

```{r}
# Type III ANOVA table for fixed effects
anova(model_wealth_video)
```

### Estimated Marginal Means for Condition in Wealth Model (Video Stimuli)

```{r}
# Estimated marginal means for Condition
emmeans_wealth_video <- emmeans(model_wealth_video, ~ Condition)
print(emmeans_wealth_video)
```
### Calculate R-squared values for the wealth model
```{r}
r_squared_wealth <- r.squaredGLMM(model_wealth_video)
print(r_squared_wealth)

# Extract specific values
R2m_wealth <- r_squared_wealth[1, "R2m"]  # Marginal R²
R2c_wealth <- r_squared_wealth[1, "R2c"]  # Conditional R²

# Display results
cat("Wealth Model R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth - R2m_wealth, 4), "\n")
```

### Visualizing Wealth Results for Video Stimuli

```{r, fig.width=8, fig.height=6}
# The results for Condition were plotted
wealth_video_results <- as.data.frame(emmeans_wealth_video)
p_wealth_video <- ggplot(wealth_video_results, aes(x=reorder(Condition, emmean), y=emmean)) +
  geom_point(size=3) +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Effect of Conditions on Wealth Ratings (Video Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_wealth_video)
```
Figure B3.5. Effect of footwear conditions on wealth perception ratings for video stimuli, including control condition. Error bars represent 95% confidence intervals.



### Pairwise Comparisons for Condition in Wealth Model (Video Stimuli)

```{r}
# Pairwise comparisons for Condition
pairs(emmeans_wealth_video, adjust = "tukey")
```

### Comparison Between Dimensions for Video Stimuli

```{r, fig.width=10, fig.height=6}
# Results from both dimensions were combined
combined_video_results <- rbind(
  transform(attract_video_results, Dimension = "Attractiveness"),
  transform(wealth_video_results, Dimension = "Wealth")
)

# The comparison plot was created
p_combined_video <- ggplot(combined_video_results, aes(x = Condition, y = emmean, color = Dimension, group = Dimension)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = 0.3), width = 0.2) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Comparison of Condition Effects Between Dimensions (Video Stimuli Only)") +
  xlab("Condition") +
  ylab("Estimated Mean Rating")

print(p_combined_video)
```
Figure B3.6. Comparison of footwear condition effects between attractiveness and wealth dimensions for video stimuli. Error bars represent 95% confidence intervals.


Creating comparison plot for Dimention x StimuliType
```{r fig.width=7, fig.height=6, out.width="100%", fig.align='center'}
# Extract data from the emmeans objects for the interaction models
attract_interact_data <- as.data.frame(emmeans_attract_interact)
wealth_interact_data <- as.data.frame(emmeans_wealth_interact)

# Add dimension labels
attract_interact_data$Dimension <- "Attractiveness"
wealth_interact_data$Dimension <- "Wealth"

# Combine the data
combined_plot_data <- rbind(attract_interact_data, wealth_interact_data)

# Ensure proper factor levels
combined_plot_data$Condition <- factor(combined_plot_data$Condition,
                                     levels = c("Control", "Economy Flat", "Economy Heel", 
                                              "Luxury Flat", "Luxury Heel"))
combined_plot_data$Stimuli_Type <- factor(combined_plot_data$Stimuli_Type, 
                                        levels = c("Image", "Video"))
combined_plot_data$Dimension <- factor(combined_plot_data$Dimension,
                                     levels = c("Attractiveness", "Wealth"))

# Create the plot
p_interaction_comparison <- ggplot(combined_plot_data, 
                                 aes(x = Condition, y = emmean, 
                                     color = Stimuli_Type, 
                                     linetype = Stimuli_Type,
                                     shape = Stimuli_Type,
                                     group = Stimuli_Type)) +
  geom_line(size = .8, position = position_dodge(width = 0.1)) +
  geom_point(size = 3, position = position_dodge(width = 0.1)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0.2, size = 0.5, 
                position = position_dodge(width = 0.1)) +
  scale_color_manual(values = c("Image" = "black", "Video" = "black"),
                     name = "Stimulus Type") +
  scale_linetype_manual(values = c("Image" = "solid", "Video" = "dashed"),
                        name = "Stimulus Type") +
  scale_shape_manual(values = c("Image" = 16, "Video" = 15),  # 16 = circle, 15 = square
                     name = "Stimulus Type") +
  scale_x_discrete(labels = c("Control" = "Control",
                             "Economy Flat" = "Economy\nFlat",
                             "Economy Heel" = "Economy\nHeel",
                             "Luxury Flat" = "Luxury\nFlat",
                             "Luxury Heel" = "Luxury\nHeel")) +
  scale_y_continuous(limits = c(4.0, 5.8), 
                     breaks = seq(4.0, 5.8, by = 0.4)) +
  facet_wrap(~ Dimension, ncol = 2, scales = "free_y") +
  labs(x = "Condition",
       y = "Estimated Mean Rating",
       caption = "Error bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    # Panel styling
    panel.grid.major = element_line(color = "grey94", size = 0.4),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    
    # Strip (facet label) styling
    strip.background = element_rect(fill = "white", color = "black", size = 0.8),
    strip.text = element_text(size = 12, face = "bold"),
    
    # Axis styling
    axis.title = element_text(size = 8),
    axis.text = element_text(size = 8, color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks = element_line(color = "black", size = 0.5),
    
    # Legend styling
    legend.position = "top",
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    legend.key.width = unit(1.5, "cm"),
    legend.margin = margin(b = 10),
    
    # Caption styling
    plot.caption = element_text(size = 8, hjust = 1, 
                           color = "grey30",
                           margin = margin(t = 10)),
    
    # Overall margins
    plot.margin = margin(10, 10, 10, 10)
  )

# Display the plot
print(p_interaction_comparison)

# Save high-quality version
ggsave("condition_stimulus_interaction.png", p_interaction_comparison,
       width = 12, height = 6, dpi = 300, bg = "white")
ggsave("condition_stimulus_interaction.pdf", p_interaction_comparison,
       width = 12, height = 6, bg = "white")
```
Figure B3.7. Comparison of footwear condition effects across stimulus types (image vs. video) and dimensions (attractiveness vs. wealth). Error bars represent 95% confidence intervals.


## **PART IV:  Supplement B4: 2×2 Factorial Analysis (Excluding Control Condition)**


## 13. Data Preparation for 2×2 Factorial Design
```{r}

# Filter out Control condition and create factorial variables
body_df_attract_factorial <- body_df_attract[body_df_attract$Condition != "Control", ]
body_df_wealth_factorial <- body_df_wealth[body_df_wealth$Condition != "Control", ]

# Create Trait_Exaggeration factor (Heel vs Flat)
body_df_attract_factorial$Trait_Exaggeration <- factor(
  ifelse(grepl("Heel", body_df_attract_factorial$Condition), "Heel", "Flat"),
  levels = c("Flat", "Heel")
)

body_df_wealth_factorial$Trait_Exaggeration <- factor(
  ifelse(grepl("Heel", body_df_wealth_factorial$Condition), "Heel", "Flat"),
  levels = c("Flat", "Heel")
)

# Create Cost factor (Economy vs Luxury)
body_df_attract_factorial$Cost <- factor(
  ifelse(grepl("Economy", body_df_attract_factorial$Condition), "Economy", "Luxury"),
  levels = c("Economy", "Luxury")
)

body_df_wealth_factorial$Cost <- factor(
  ifelse(grepl("Economy", body_df_wealth_factorial$Condition), "Economy", "Luxury"),
  levels = c("Economy", "Luxury")
)

# Set sum coding (effects coding) for both factors
contrasts(body_df_attract_factorial$Trait_Exaggeration) <- contr.sum(2)
contrasts(body_df_attract_factorial$Cost) <- contr.sum(2)
contrasts(body_df_wealth_factorial$Trait_Exaggeration) <- contr.sum(2)
contrasts(body_df_wealth_factorial$Cost) <- contr.sum(2)

# Split by Stimuli_Type
body_df_attract_factorial_image <- body_df_attract_factorial[body_df_attract_factorial$Stimuli_Type == "Image", ]
body_df_attract_factorial_video <- body_df_attract_factorial[body_df_attract_factorial$Stimuli_Type == "Video", ]
body_df_wealth_factorial_image <- body_df_wealth_factorial[body_df_wealth_factorial$Stimuli_Type == "Image", ]
body_df_wealth_factorial_video <- body_df_wealth_factorial[body_df_wealth_factorial$Stimuli_Type == "Video", ]
```

## 14. Attractiveness Models - 2×2 Factorial Design

### 14.1 Attractiveness Model for Image Stimuli (2×2)
```{r}
# Model for attractiveness - Image stimuli (2×2 factorial)
model_attract_factorial_image <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                      (1|block/Model) + (1|code), 
                                      data = body_df_attract_factorial_image)

# Model summary
summary(model_attract_factorial_image)
```

ANOVA for 2×2 Factorial Model (Attractiveness - Image)
```{r}
# Type III ANOVA table for factorial effects
anova(model_attract_factorial_image)
```

Estimated Marginal Means (Attractiveness - Image)
```{r}
# Main effect of Trait_Exaggeration
emmeans_attract_fact_img_trait <- emmeans(model_attract_factorial_image, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_attract_fact_img_trait)

# Main effect of Cost
emmeans_attract_fact_img_cost <- emmeans(model_attract_factorial_image, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_attract_fact_img_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_attract_fact_img_interact <- emmeans(model_attract_factorial_image, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_attract_fact_img_interact)
```

Pairwise Comparisons (Attractiveness - Image)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_attract_fact_img_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_attract_fact_img_interact2 <- emmeans(model_attract_factorial_image, ~ Cost | Trait_Exaggeration)
pairs(emmeans_attract_fact_img_interact2, adjust = "tukey")
```

R-squared for Attractiveness Model (Image - 2×2)
```{r}
r_squared_attract_fact_img <- r.squaredGLMM(model_attract_factorial_image)
print(r_squared_attract_fact_img)

R2m_attract_fact_img <- r_squared_attract_fact_img[1, "R2m"]
R2c_attract_fact_img <- r_squared_attract_fact_img[1, "R2c"]

cat("Attractiveness Model (Image) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract_fact_img, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract_fact_img, 4), "\n")
cat("Random effects contribution:", round(R2c_attract_fact_img - R2m_attract_fact_img, 4), "\n")
```

### 14.2 Attractiveness Model for Video Stimuli (2×2)
```{r}
# Model for attractiveness - Video stimuli (2×2 factorial)
model_attract_factorial_video <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                      (1|block/Model) + (1|code), 
                                      data = body_df_attract_factorial_video)

# Model summary
summary(model_attract_factorial_video)
```

ANOVA for 2×2 Factorial Model (Attractiveness - Video)
```{r}
# Type III ANOVA table for factorial effects
anova(model_attract_factorial_video)
```

Estimated Marginal Means (Attractiveness - Video)
```{r}
# Main effect of Trait_Exaggeration
emmeans_attract_fact_vid_trait <- emmeans(model_attract_factorial_video, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_attract_fact_vid_trait)

# Main effect of Cost
emmeans_attract_fact_vid_cost <- emmeans(model_attract_factorial_video, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_attract_fact_vid_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_attract_fact_vid_interact <- emmeans(model_attract_factorial_video, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_attract_fact_vid_interact)
```

Pairwise Comparisons (Attractiveness - Video)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_attract_fact_vid_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_attract_fact_vid_interact2 <- emmeans(model_attract_factorial_video, ~ Cost | Trait_Exaggeration)
pairs(emmeans_attract_fact_vid_interact2, adjust = "tukey")
```

R-squared for Attractiveness Model (Video - 2×2)
```{r}
r_squared_attract_fact_vid <- r.squaredGLMM(model_attract_factorial_video)
print(r_squared_attract_fact_vid)

R2m_attract_fact_vid <- r_squared_attract_fact_vid[1, "R2m"]
R2c_attract_fact_vid <- r_squared_attract_fact_vid[1, "R2c"]

cat("Attractiveness Model (Video) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_attract_fact_vid, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_attract_fact_vid, 4), "\n")
cat("Random effects contribution:", round(R2c_attract_fact_vid - R2m_attract_fact_vid, 4), "\n")
```

## 15. Wealth Models - 2×2 Factorial Design

### 15.1 Wealth Model for Image Stimuli (2×2)
```{r}
# Model for wealth - Image stimuli (2×2 factorial)
model_wealth_factorial_image <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                     (1|block/Model) + (1|code), 
                                     data = body_df_wealth_factorial_image)

# Model summary
summary(model_wealth_factorial_image)
```

ANOVA for 2×2 Factorial Model (Wealth - Image)
```{r}
# Type III ANOVA table for factorial effects
anova(model_wealth_factorial_image)
```

Estimated Marginal Means (Wealth - Image)
```{r}
# Main effect of Trait_Exaggeration
emmeans_wealth_fact_img_trait <- emmeans(model_wealth_factorial_image, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_wealth_fact_img_trait)

# Main effect of Cost
emmeans_wealth_fact_img_cost <- emmeans(model_wealth_factorial_image, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_wealth_fact_img_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_wealth_fact_img_interact <- emmeans(model_wealth_factorial_image, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_wealth_fact_img_interact)
```

Pairwise Comparisons (Wealth - Image)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_wealth_fact_img_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_wealth_fact_img_interact2 <- emmeans(model_wealth_factorial_image, ~ Cost | Trait_Exaggeration)
pairs(emmeans_wealth_fact_img_interact2, adjust = "tukey")
```

R-squared for Wealth Model (Image - 2×2)
```{r}
r_squared_wealth_fact_img <- r.squaredGLMM(model_wealth_factorial_image)
print(r_squared_wealth_fact_img)

R2m_wealth_fact_img <- r_squared_wealth_fact_img[1, "R2m"]
R2c_wealth_fact_img <- r_squared_wealth_fact_img[1, "R2c"]

cat("Wealth Model (Image) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth_fact_img, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth_fact_img, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth_fact_img - R2m_wealth_fact_img, 4), "\n")
```

### 15.2 Wealth Model for Video Stimuli (2×2)
```{r}
# Model for wealth - Video stimuli (2×2 factorial)
model_wealth_factorial_video <- lmer(Rating ~ Trait_Exaggeration * Cost + 
                                     (1|block/Model) + (1|code), 
                                     data = body_df_wealth_factorial_video)

# Model summary
summary(model_wealth_factorial_video)
```

ANOVA for 2×2 Factorial Model (Wealth - Video)
```{r}
# Type III ANOVA table for factorial effects
anova(model_wealth_factorial_video)
```

Estimated Marginal Means (Wealth - Video)
```{r}
# Main effect of Trait_Exaggeration
emmeans_wealth_fact_vid_trait <- emmeans(model_wealth_factorial_video, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_wealth_fact_vid_trait)

# Main effect of Cost
emmeans_wealth_fact_vid_cost <- emmeans(model_wealth_factorial_video, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_wealth_fact_vid_cost)

# Interaction: Trait_Exaggeration × Cost
emmeans_wealth_fact_vid_interact <- emmeans(model_wealth_factorial_video, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration × Cost:")
print(emmeans_wealth_fact_vid_interact)
```

Pairwise Comparisons (Wealth - Video)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_wealth_fact_vid_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_wealth_fact_vid_interact2 <- emmeans(model_wealth_factorial_video, ~ Cost | Trait_Exaggeration)
pairs(emmeans_wealth_fact_vid_interact2, adjust = "tukey")
```

R-squared for Wealth Model (Video - 2×2)
```{r}
r_squared_wealth_fact_vid <- r.squaredGLMM(model_wealth_factorial_video)
print(r_squared_wealth_fact_vid)

R2m_wealth_fact_vid <- r_squared_wealth_fact_vid[1, "R2m"]
R2c_wealth_fact_vid <- r_squared_wealth_fact_vid[1, "R2c"]

cat("Wealth Model (Video) R-squared:\n")
cat("R²m (Fixed effects only):", round(R2m_wealth_fact_vid, 4), "\n")
cat("R²c (Fixed + Random effects):", round(R2c_wealth_fact_vid, 4), "\n")
cat("Random effects contribution:", round(R2c_wealth_fact_vid - R2m_wealth_fact_vid, 4), "\n")
```

## 16. Visualization of 2×2 Factorial Effects
### 16.1 Interaction Plots for All Models


```{r fig.width=7, fig.height=6, out.width="100%", fig.align='center'}
# Prepare data for plotting
prepare_factorial_plot_data <- function(emmeans_obj, dimension, stimuli) {
  df <- as.data.frame(emmeans_obj)
  df$Dimension <- dimension
  df$Stimuli_Type <- stimuli
  return(df)
}

# Attractiveness - Image
attract_img_plot <- prepare_factorial_plot_data(emmeans_attract_fact_img_interact, 
                                                "Attractiveness", "Image")
# Attractiveness - Video
attract_vid_plot <- prepare_factorial_plot_data(emmeans_attract_fact_vid_interact, 
                                                "Attractiveness", "Video")
# Wealth - Image
wealth_img_plot <- prepare_factorial_plot_data(emmeans_wealth_fact_img_interact, 
                                               "Wealth", "Image")
# Wealth - Video
wealth_vid_plot <- prepare_factorial_plot_data(emmeans_wealth_fact_vid_interact, 
                                               "Wealth", "Video")

# Combine all data
factorial_combined <- rbind(attract_img_plot, attract_vid_plot, 
                           wealth_img_plot, wealth_vid_plot)

# Create comprehensive interaction plot
p_factorial_all <- ggplot(factorial_combined, 
                         aes(x = Trait_Exaggeration, y = emmean, 
                             color = Cost, group = Cost,
                             shape = Cost, linetype = Cost)) +
  geom_line(size = 1, position = position_dodge(width = 0.1)) +
  geom_point(size = 3, position = position_dodge(width = 0.1)) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0.15, size = 0.7,
                position = position_dodge(width = 0.1)) +
  facet_grid(Dimension ~ Stimuli_Type, scales = "free_y") +
  scale_color_manual(values = c("Economy" = "#D95F02", "Luxury" = "#7570B3"),
                    name = "Cost") +
  scale_shape_manual(values = c("Economy" = 16, "Luxury" = 17),
                    name = "Cost") +
  scale_linetype_manual(values = c("Economy" = "solid", "Luxury" = "dashed"),
                       name = "Cost") +
  labs(x = "Trait Exaggeration",
       y = "Estimated Mean Rating",
       title = "2×2 Factorial Effects: Trait Exaggeration × Cost",
       caption = "Error bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    strip.background = element_rect(fill = "grey95", color = "black", size = 0.8),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.caption = element_text(hjust = 1, color = "grey40")
  )

print(p_factorial_all)

# Save the plot
ggsave("factorial_2x2_interaction_plot.png", p_factorial_all,
      width = 12, height = 10, dpi = 300, bg = "white")
ggsave("factorial_2x2_interaction_plot.pdf", p_factorial_all,
      width = 12, height = 10, bg = "white")
```
Figure B4.1. Interaction between trait exaggeration (heel vs. flat) and cost (economy vs. luxury) across stimulus types and rating dimensions. Error bars represent 95% confidence intervals.


### 16.2 Main Effects Plots
```{r fig.width=7, fig.height=6, out.width="100%", fig.align='center'}
# Prepare main effects data
create_main_effects_data <- function() {
  # Trait Exaggeration effects
  trait_data <- rbind(
    data.frame(as.data.frame(emmeans_attract_fact_img_trait), 
               Dimension = "Attractiveness", Stimuli_Type = "Image", Factor = "Trait Exaggeration"),
    data.frame(as.data.frame(emmeans_attract_fact_vid_trait), 
               Dimension = "Attractiveness", Stimuli_Type = "Video", Factor = "Trait Exaggeration"),
    data.frame(as.data.frame(emmeans_wealth_fact_img_trait), 
               Dimension = "Wealth", Stimuli_Type = "Image", Factor = "Trait Exaggeration"),
    data.frame(as.data.frame(emmeans_wealth_fact_vid_trait), 
               Dimension = "Wealth", Stimuli_Type = "Video", Factor = "Trait Exaggeration")
  )
  trait_data$Level <- trait_data$Trait_Exaggeration
  
  # Cost effects
  cost_data <- rbind(
    data.frame(as.data.frame(emmeans_attract_fact_img_cost), 
               Dimension = "Attractiveness", Stimuli_Type = "Image", Factor = "Cost"),
    data.frame(as.data.frame(emmeans_attract_fact_vid_cost), 
               Dimension = "Attractiveness", Stimuli_Type = "Video", Factor = "Cost"),
    data.frame(as.data.frame(emmeans_wealth_fact_img_cost), 
               Dimension = "Wealth", Stimuli_Type = "Image", Factor = "Cost"),
    data.frame(as.data.frame(emmeans_wealth_fact_vid_cost), 
               Dimension = "Wealth", Stimuli_Type = "Video", Factor = "Cost")
  )
  cost_data$Level <- cost_data$Cost
  
  # Combine
  main_effects_data <- rbind(
    trait_data[, c("emmean", "SE", "asymp.LCL", "asymp.UCL", "Dimension", "Stimuli_Type", "Factor", "Level")],
    cost_data[, c("emmean", "SE", "asymp.LCL", "asymp.UCL", "Dimension", "Stimuli_Type", "Factor", "Level")]
  )
  
  return(main_effects_data)
}

main_effects_data <- create_main_effects_data()

# Plot main effects
p_main_effects <- ggplot(main_effects_data, 
                        aes(x = Level, y = emmean, 
                            color = Stimuli_Type, group = Stimuli_Type)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL), 
                width = 0.15, size = 0.7) +
  facet_grid(Dimension ~ Factor, scales = "free") +
  scale_color_manual(values = c("Image" = "#1B9E77", "Video" = "#D95F02"),
                    name = "Stimulus Type") +
  labs(x = "Factor Level",
       y = "Estimated Mean Rating",
       title = "Main Effects of Trait Exaggeration and Cost",
       caption = "Error bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    strip.background = element_rect(fill = "grey95", color = "black", size = 0.8),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.caption = element_text(hjust = 1, color = "grey40")
  )

print(p_main_effects)

# Save the plot
ggsave("factorial_2x2_main_effects.png", p_main_effects,
       width = 12, height = 8, dpi = 300, bg = "white")
ggsave("factorial_2x2_main_effects.pdf", p_main_effects,
       width = 12, height = 8, bg = "white")
```
Figure B4.2. Main effects of cost and trait exaggeration across stimulus types for attractiveness and wealth ratings. Error bars represent 95% confidence intervals.


## 17. Effect Size Analysis for 2×2 Factorial Models

### 17.1. Function to Calculate Cohen's d from emmeans
```{r}
# Function to calculate Cohen's d for pairwise comparisons
calculate_cohens_d <- function(emmeans_obj, model_obj) {
  # Get pairwise comparisons
  pairs_result <- pairs(emmeans_obj, adjust = "none")
  pairs_df <- as.data.frame(pairs_result)
  
  # Extract residual standard deviation from model
  sigma_resid <- sigma(model_obj)
  
  # Calculate Cohen's d for each comparison
  pairs_df$cohens_d <- pairs_df$estimate / sigma_resid
  
  # Classify effect sizes
  pairs_df$effect_size_label <- cut(abs(pairs_df$cohens_d),
                                    breaks = c(0, 0.22, 0.39, 0.60, Inf),
                                    labels = c("Very Small", "Small", "Medium", "Large"),
                                    right = FALSE)
  
  return(pairs_df)
}
```

### 17.2 Calculate Effect Sizes for All Models
```{r}
# Attractiveness - Image
cat("\n=== ATTRACTIVENESS - IMAGE STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_attract_img_trait <- calculate_cohens_d(emmeans_attract_fact_img_trait, 
                                          model_attract_factorial_image)
print(d_attract_img_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_attract_img_cost <- calculate_cohens_d(emmeans_attract_fact_img_cost, 
                                         model_attract_factorial_image)
print(d_attract_img_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_attract_img_simple <- calculate_cohens_d(emmeans_attract_fact_img_interact, 
                                           model_attract_factorial_image)
print(d_attract_img_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

# Attractiveness - Video
cat("\n\n=== ATTRACTIVENESS - VIDEO STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_attract_vid_trait <- calculate_cohens_d(emmeans_attract_fact_vid_trait, 
                                          model_attract_factorial_video)
print(d_attract_vid_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_attract_vid_cost <- calculate_cohens_d(emmeans_attract_fact_vid_cost, 
                                         model_attract_factorial_video)
print(d_attract_vid_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_attract_vid_simple <- calculate_cohens_d(emmeans_attract_fact_vid_interact, 
                                           model_attract_factorial_video)
print(d_attract_vid_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

# Wealth - Image
cat("\n\n=== WEALTH - IMAGE STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_wealth_img_trait <- calculate_cohens_d(emmeans_wealth_fact_img_trait, 
                                         model_wealth_factorial_image)
print(d_wealth_img_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_wealth_img_cost <- calculate_cohens_d(emmeans_wealth_fact_img_cost, 
                                        model_wealth_factorial_image)
print(d_wealth_img_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_wealth_img_simple <- calculate_cohens_d(emmeans_wealth_fact_img_interact, 
                                          model_wealth_factorial_image)
print(d_wealth_img_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

# Wealth - Video
cat("\n\n=== WEALTH - VIDEO STIMULI ===\n")
cat("\nMain Effect: Trait Exaggeration\n")
d_wealth_vid_trait <- calculate_cohens_d(emmeans_wealth_fact_vid_trait, 
                                         model_wealth_factorial_video)
print(d_wealth_vid_trait[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nMain Effect: Cost\n")
d_wealth_vid_cost <- calculate_cohens_d(emmeans_wealth_fact_vid_cost, 
                                        model_wealth_factorial_video)
print(d_wealth_vid_cost[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])

cat("\nSimple Effects: Trait Exaggeration within Cost levels\n")
d_wealth_vid_simple <- calculate_cohens_d(emmeans_wealth_fact_vid_interact, 
                                          model_wealth_factorial_video)
print(d_wealth_vid_simple[, c("contrast", "estimate", "cohens_d", "effect_size_label", "p.value")])
```

### 17.3 Partial Eta-squared from ANOVA Tables
```{r}
# Function to extract and format ANOVA with effect sizes
format_anova_with_effect_sizes <- function(model_obj, model_name) {
  anova_result <- anova(model_obj)
  
  # Calculate partial eta-squared
  anova_result$partial_eta_sq <- anova_result$`Sum Sq` / 
    (anova_result$`Sum Sq` + sum(residuals(model_obj)^2))
  
  # Classify effect sizes
  anova_result$effect_size_label <- cut(anova_result$partial_eta_sq,
                                        breaks = c(0, 0.012, 0.037, 0.082, 1),
                                        labels = c("Very Small", "Small", "Medium", "Large"),
                                        right = FALSE)
  
  cat("\n===", model_name, "===\n")
  print(anova_result[, c("Sum Sq", "Mean Sq", "NumDF", "DenDF", "F value", 
                         "Pr(>F)", "partial_eta_sq", "effect_size_label")])
  
  return(anova_result)
}

# Calculate for all models
eta_attract_img <- format_anova_with_effect_sizes(model_attract_factorial_image, 
                                                   "Attractiveness - Image")
eta_attract_vid <- format_anova_with_effect_sizes(model_attract_factorial_video, 
                                                   "Attractiveness - Video")
eta_wealth_img <- format_anova_with_effect_sizes(model_wealth_factorial_image, 
                                                  "Wealth - Image")
eta_wealth_vid <- format_anova_with_effect_sizes(model_wealth_factorial_video, 
                                                  "Wealth - Video")
```


### 17.4 Comprehensive Summary Table of Effect Sizes
```{r}
# Create a detailed summary table
effect_size_summary <- data.frame(
  Model = c(
    "Attractiveness - Image",
    "Attractiveness - Image", 
    "Attractiveness - Image",
    "Attractiveness - Video",
    "Attractiveness - Video",
    "Attractiveness - Video",
    "Wealth - Image",
    "Wealth - Image",
    "Wealth - Image",
    "Wealth - Video",
    "Wealth - Video",
    "Wealth - Video"
  ),
  Effect = c(
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)",
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)",
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)",
    "Trait Exaggeration (Main)",
    "Cost (Main)",
    "Trait × Cost (Interaction)"
  ),
  Raw_Difference = c(
    0.325, 0.036, NA,
    -0.183, -0.193, NA,
    0.504, 0.100, NA,
    0.302, -0.051, NA
  ),
  Cohens_d = c(
    0.28, 0.03, NA,
    -0.14, -0.15, NA,
    0.49, 0.10, NA,
    0.25, -0.04, NA
  ),
  Partial_Eta_Sq = c(
    0.0207, 0.0003, 0.0006,
    0.0052, 0.0058, 0.0032,
    0.0601, 0.0025, 0.0018,
    0.0159, 0.0005, 0.0062
  )
)

print(effect_size_summary)

```

### 17.5 Simple Effects Summary for Key Comparisons
```{r}
simple_effects_summary <- data.frame(
  Model = c(
    "Attractiveness - Image: Economy",
    "Attractiveness - Image: Luxury",
    "Attractiveness - Video: Economy",
    "Attractiveness - Video: Luxury",
    "Wealth - Image: Economy",
    "Wealth - Image: Luxury",
    "Wealth - Video: Economy",
    "Wealth - Video: Luxury"
  ),
  Comparison = rep("Heel vs Flat", 8),
  Raw_Difference_Heel_Higher = c(
    0.379, 0.271,  # Attractiveness - Image (heels rated higher)
    -0.041, -0.325,    # Attractiveness - Video (mixed: flat higher in economy, heel higher in luxury)
    0.589, 0.420,  # Wealth - Image (heels rated higher)
    0.490, 0.115   # Wealth - Video (heels rated higher)
  ),
  Cohens_d_abs = c(
    0.33, 0.24,
    0.03, 0.25,
    0.57, 0.41,
    0.40, 0.09
  ),
  Effect_Size_Label = c(
    "Small", "Small",
    "Negligible", "Small",
    "Medium", "Small",
    "Small", "Negligible"
  ),
  p_value = c(
    8.31e-18, 8.13e-10,
    4.15e-01, 6.60e-11,
    1.49e-50, 1.68e-26,
    1.58e-25, 1.43e-02
  ),
  Interpretation = c(
    "Heels INCREASE attractiveness noticeably in images (Economy)",
    "Heels INCREASE attractiveness noticeably in images (Luxury)",
    "No meaningful difference in videos (Economy)",
    "Heels INCREASE attractiveness slightly in videos (Luxury)",
    "Heels SUBSTANTIALLY INCREASE wealth perception in images (Economy)",
    "Heels INCREASE wealth perception in images (Luxury)",
    "Heels INCREASE wealth perception in videos (Economy)",
    "Minimal difference in videos (Luxury)"
  )
)

print(simple_effects_summary)
#write.csv(simple_effects_summary, "simple_effects_summary.csv", row.names = FALSE)
```

### 17.6 Visualization: Effect Sizes Across Models
```{r ig.width=15, fig.height=10, fig.align='center', dpi=300, out.width='80%'}
# Create a comprehensive effect size visualization
# Prepare data for main effects visualization
main_effects_es <- data.frame(
  Model = rep(c("Attract-Image", "Attract-Video", "Wealth-Image", "Wealth-Video"), each = 2),
  Effect = rep(c("Trait Exaggeration", "Cost"), 4),
  Partial_Eta_Sq = c(
    0.0207, 0.0003,  # Attractiveness - Image
    0.0052, 0.0058,  # Attractiveness - Video
    0.0601, 0.0025,  # Wealth - Image
    0.0159, 0.0005   # Wealth - Video
  ),
  Cohens_d = c(
    -0.28, -0.03,
    0.14, 0.15,
    -0.49, -0.10,
    -0.25, 0.04
  )
)

# Add effect size categories
main_effects_es$ES_Category <- cut(main_effects_es$Partial_Eta_Sq,
                                   breaks = c(0, 0.012, 0.037, 0.082, 1),
                                   labels = c("Very Small", "Small", "Medium", "Large"))



# Plot 1: Partial Eta-Squared
p1 <- ggplot(main_effects_es, aes(x = Model, y = Partial_Eta_Sq, color = ES_Category, shape = ES_Category)) +
  geom_point(position = position_dodge(0.8), size = 4) +
  geom_hline(yintercept = c(0.012, 0.037, 0.082), linetype = "dashed", color = "red", alpha = 0.5) +
  facet_wrap(~ Effect) +
  scale_color_manual(values = c("Very Small" = "#999999", 
                                "Small" = "#E69F00", 
                                "Medium" = "#56B4E9", 
                                "Large" = "#009E73"),
                     name = "Effect Size"
                    ) +
  scale_shape_manual(values = c("Very Small" = 16, "Small" = 17, "Medium" = 15, "Large" = 18),
                     name = "Effect Size"
                     ) +
  labs(title = "Partial Eta-squared by Model and Effect Type",
       y = "Partial Eta-squared",
       x = "Model") +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    panel.border = element_rect(color = "black", fill = NA),
    strip.background = element_rect(fill = "grey90", color = "black"),
    strip.text = element_text(face = "bold")
  ) +
  annotate("text", x = 0.5, y = 0.012, label = "Small", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.037, label = "Medium", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.082, label = "Large", hjust = 0, size = 3, color = "red")

print(p1)
```
Figure B4.3. Partial Eta-squared effect sizes for main effects across all 2×2 factorial models. Dashed reference lines indicate small (0.012), medium (0.037), and large (0.082) effect size thresholds. For Effect Size Interpretation Guidelines see Supplement Section A3. 

```{r ig.width=15, fig.height=10, fig.align='center', dpi=300, out.width='80%'}
# Plot 2: Cohen's d
p2 <- ggplot(main_effects_es, aes(x = Model, y = abs(Cohens_d), color = Effect, shape = Effect)) +
  geom_point(position = position_dodge(0.8), size = 4) +
  geom_hline(yintercept = c(0.22, 0.39, 0.60), linetype = "dashed", color = "red", alpha = 0.5) +
  scale_color_manual(values = c("Trait Exaggeration" = "#1F77B4", 
                                "Cost" = "#FF7F0E"),
                     name = "Effect Type") +
  scale_shape_manual(values = c("Trait Exaggeration" = 16, "Cost" = 17),
                     name = "Effect Type") +
  labs(title = "Cohen's d (Absolute Values) by Model",
       y = "|Cohen's d|",
       x = "Model") +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    panel.border = element_rect(color = "black", fill = NA)
  ) +
  annotate("text", x = 0.5, y = 0.22, label = "Small", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.39, label = "Medium", hjust = 0, size = 3, color = "red") +
  annotate("text", x = 0.5, y = 0.60, label = "Large", hjust = 0, size = 3, color = "red")

print(p2)
```
Figure B4.4. Cohen's d effect sizes (absolute values) for cost and trait exaggeration main effects across all models. Dashed reference lines indicate small (0.22), medium (0.39), and large (0.60) effect size thresholds.For Effect Size Interpretation Guidelines see Supplement Section A3.

```{r}
# Reshape data for combined plot
main_effects_long <- main_effects_es %>%
  select(Model, Effect, Cohens_d, Partial_Eta_Sq, ES_Category) %>%
  pivot_longer(
    cols = c(Cohens_d, Partial_Eta_Sq),
    names_to = "Metric",
    values_to = "Value"
  ) %>%
  mutate(
    Metric = factor(Metric, 
                   levels = c("Cohens_d", "Partial_Eta_Sq"),
                   labels = c("Cohen's d", "Partial Eta-squared")),
    Value_abs = ifelse(Metric == "Cohen's d", abs(Value), Value)
  )

# Create separate data frames for annotations
annotations_d <- data.frame(
  Metric = "Cohen's d",
  yint = c(0.22, 0.39, 0.60),
  label = c("Small", "Medium", "Large")
)

annotations_eta <- data.frame(
  Metric = "Partial Eta-squared",
  yint = c(0.012, 0.037, 0.082),
  label = c("Small", "Medium", "Large")
)

annotations_all <- rbind(annotations_d, annotations_eta)

# Combined plot with proper free scales
p_combined <- ggplot(main_effects_long, aes(x = Model, y = Value_abs, color = Effect, shape = Effect)) +
  geom_point(position = position_dodge(0.8), size = 4) +
  facet_wrap(~ Metric, scales = "free_y") +
  geom_hline(data = annotations_all,
             aes(yintercept = yint), 
             linetype = "dashed", color = "red", alpha = 0.5) +
  geom_text(data = annotations_all,
            aes(x = 0.5, y = yint, label = label),
            hjust = 0, size = 3, color = "red", inherit.aes = FALSE) +
  scale_color_manual(values = c("Trait Exaggeration" = "#1F77B4", 
                                "Cost" = "#FF7F0E"),
                     name = "Effect Type") +
  scale_shape_manual(values = c("Trait Exaggeration" = 16, "Cost" = 17),
                     name = "Effect Type") +
  labs(title = "Effect Sizes by Model and Metric",
       y = "Effect Size",
       x = "Model") +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    panel.border = element_rect(color = "black", fill = NA),
    strip.background = element_rect(fill = "grey90", color = "black"),
    strip.text = element_text(face = "bold")
  )

print(p_combined)

# Save
ggsave("effect_sizes_comparison.png", 
      arrangeGrob(p_combined),
      width = 14, height = 10, dpi = 300, bg = "white")
ggsave("effect_sizes_comparison.pdf", arrangeGrob(p_combined),
      width = 12, height = 10, bg = "white")
```

Figure B4.5. Effect sizes for main effects across all 2×2 factorial models, shown as Cohen's d (left panel) and partial Eta-squared (right panel). Dashed reference lines indicate small, medium, and large effect size thresholds for each metric (d: 0.22, 0.39, 0.60; Eta-squared: 0.012, 0.037, 0.082). For Effect Size Interpretation Guidelines see Supplement Section A3.

## 18.  Variance Components Analysis
```{r}

# Function to calculate variance components percentage
calculate_variance_components <- function(model) {
  # Extract random effects variance components
  vc <- as.data.frame(VarCorr(model))
  
# Get fixed effects variance 
  # Calculate residual variance and total variance
  residual_var <- vc$vcov[vc$grp == "Residual"]
  random_vars <- vc$vcov[vc$grp != "Residual"]
  fixed_var <- get_variance_fixed(model)
  total_var <- sum(c(random_vars, residual_var, fixed_var))
  
  # Calculate the percentage for each component
  var_components <- data.frame(
    Component = c(vc$grp[vc$grp != "Residual"], "Fixed Effects", "Residual"),
    Variance = c(random_vars, fixed_var, residual_var),
    Percentage = c(random_vars, fixed_var, residual_var) / total_var * 100
  )
  
  # Round and sort by percentage
  var_components$Percentage <- round(var_components$Percentage, 2)
  var_components <- var_components[order(var_components$Percentage, decreasing = TRUE), ]
  
  return(var_components)
}

# Apply the function to attractiveness and wealth models with interaction
cat("\n============================================================\n")
cat("VARIANCE COMPONENTS ANALYSIS\n")
cat("============================================================\n\n")

cat("ATTRACTIVENESS MODEL VARIANCE COMPONENTS:\n")
attract_components <- calculate_variance_components(model_attract_interact)
print(attract_components)

# Calculate total variance explained by subject (code) vs stimuli structure (block/Model)
rater_variance <- sum(attract_components$Percentage[attract_components$Component == "code"])
stimuli_variance <- sum(attract_components$Percentage[attract_components$Component %in% c("block", "Model:block")])

cat("\nPercentage of variation explained by:\n")
cat("- Individual differences between raters:", rater_variance, "%\n")
cat("- Stimuli structure (block/Model nested):", stimuli_variance, "%\n")
cat("- Fixed effects (experimental conditions):", 
    attract_components$Percentage[attract_components$Component == "Fixed Effects"], "%\n")
cat("- Unexplained variation (residual):", 
    attract_components$Percentage[attract_components$Component == "Residual"], "%\n\n")

cat("WEALTH MODEL VARIANCE COMPONENTS:\n")
wealth_components <- calculate_variance_components(model_wealth_interact)
print(wealth_components)

# Calculate total variance explained by subject (code) vs stimuli structure (block/Model)
rater_variance <- sum(wealth_components$Percentage[wealth_components$Component == "code"])
stimuli_variance <- sum(wealth_components$Percentage[wealth_components$Component %in% c("block", "Model:block")])

cat("\nPercentage of variation explained by:\n")
cat("- Individual differences between raters:", rater_variance, "%\n")
cat("- Stimuli structure (block/Model nested):", stimuli_variance, "%\n")
cat("- Fixed effects (experimental conditions):", 
    wealth_components$Percentage[wealth_components$Component == "Fixed Effects"], "%\n")
cat("- Unexplained variation (residual):", 
    wealth_components$Percentage[wealth_components$Component == "Residual"], "%\n\n")

# Apply to the split models as well
cat("ATTRACTIVENESS MODEL - IMAGES ONLY:\n")
attract_image_components <- calculate_variance_components(model_attract_image)
print(attract_image_components)

cat("\nATTRACTIVENESS MODEL - VIDEOS ONLY:\n")
attract_video_components <- calculate_variance_components(model_attract_video)
print(attract_video_components)

cat("\nWEALTH MODEL - IMAGES ONLY:\n")
wealth_image_components <- calculate_variance_components(model_wealth_image)
print(wealth_image_components)

cat("\nWEALTH MODEL - VIDEOS ONLY:\n")
wealth_video_components <- calculate_variance_components(model_wealth_video)
print(wealth_video_components)

# Create a summary table for comparison
variance_summary <- data.frame(
  Model = c("Attract - Full", "Attract - Image", "Attract - Video", 
            "Wealth - Full", "Wealth - Image", "Wealth - Video"),
  Rater_Variance = c(
    sum(attract_components$Percentage[attract_components$Component == "code"]),
    sum(attract_image_components$Percentage[attract_image_components$Component == "code"]),
    sum(attract_video_components$Percentage[attract_video_components$Component == "code"]),
    sum(wealth_components$Percentage[wealth_components$Component == "code"]),
    sum(wealth_image_components$Percentage[wealth_image_components$Component == "code"]),
    sum(wealth_video_components$Percentage[wealth_video_components$Component == "code"])
  ),
  Stimuli_Variance = c(
    sum(attract_components$Percentage[attract_components$Component %in% c("block", "Model:block")]),
    sum(attract_image_components$Percentage[attract_image_components$Component %in% c("block", "Model:block")]),
    sum(attract_video_components$Percentage[attract_video_components$Component %in% c("block", "Model:block")]),
    sum(wealth_components$Percentage[wealth_components$Component %in% c("block", "Model:block")]),
    sum(wealth_image_components$Percentage[wealth_image_components$Component %in% c("block", "Model:block")]),
    sum(wealth_video_components$Percentage[wealth_video_components$Component %in% c("block", "Model:block")])
  ),
  Fixed_Effects = c(
    attract_components$Percentage[attract_components$Component == "Fixed Effects"],
    attract_image_components$Percentage[attract_image_components$Component == "Fixed Effects"],
    attract_video_components$Percentage[attract_video_components$Component == "Fixed Effects"],
    wealth_components$Percentage[wealth_components$Component == "Fixed Effects"],
    wealth_image_components$Percentage[wealth_image_components$Component == "Fixed Effects"],
    wealth_video_components$Percentage[wealth_video_components$Component == "Fixed Effects"]
  ),
  Residual = c(
    attract_components$Percentage[attract_components$Component == "Residual"],
    attract_image_components$Percentage[attract_image_components$Component == "Residual"],
    attract_video_components$Percentage[attract_video_components$Component == "Residual"],
    wealth_components$Percentage[wealth_components$Component == "Residual"],
    wealth_image_components$Percentage[wealth_image_components$Component == "Residual"],
    wealth_video_components$Percentage[wealth_video_components$Component == "Residual"]
  )
)

# Round values for display
variance_summary[, 2:5] <- round(variance_summary[, 2:5], 2)

cat("\n============================================================\n")
cat("VARIANCE COMPONENTS SUMMARY ACROSS MODELS\n")
cat("============================================================\n\n")
print(variance_summary)

```

## **PART V: Supplement B5: Normality Assumption Checks for Mixed-Effects Models with Nested Structure**

### 20. Function to calculate standardized residuals (Pearson residuals scaled by their standard deviation)

```{r}

# Extract different types of residuals
extract_residuals <- function(model, model_name) {
  # Standardized residuals (accounts for random effects variance)
  std_resid <- residuals(model, type = "pearson", scaled = TRUE)
  
  # Raw residuals
  raw_resid <- residuals(model)
  
  # Create data frame for plotting
  resid_data <- data.frame(
    standardized = std_resid,
    raw = raw_resid,
    fitted = fitted(model)
  )
  
  return(list(data = resid_data, name = model_name))
}

# Function to create comprehensive normality plots
check_residual_normality <- function(resid_info) {
  resid_data <- resid_info$data
  model_name <- resid_info$name
  
  # Q-Q plot for standardized residuals
  p1 <- ggplot(resid_data, aes(sample = standardized)) +
    stat_qq() +
    stat_qq_line(color = "red") +
    ggtitle(paste("Q-Q Plot:", model_name, "- Standardized Residuals")) +
    theme_minimal()
  
  # Histogram of standardized residuals
  p2 <- ggplot(resid_data, aes(x = standardized)) +
    geom_histogram(aes(y = ..density..), bins = 30, alpha = 0.7) +
    geom_density(color = "red", size = 1) +
    stat_function(fun = dnorm, args = list(mean = 0, sd = 1), 
                  color = "blue", linetype = "dashed") +
    ggtitle(paste("Histogram:", model_name, "- Standardized Residuals")) +
    xlab("Standardized Residuals") +
    theme_minimal()
  
  # Residuals vs Fitted (to check homoscedasticity too)
  p3 <- ggplot(resid_data, aes(x = fitted, y = standardized)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "loess", se = FALSE, color = "red") +
    geom_hline(yintercept = 0, linetype = "dashed") +
    ggtitle(paste("Residuals vs Fitted:", model_name)) +
    xlab("Fitted Values") +
    ylab("Standardized Residuals") +
    theme_minimal()
  
  return(list(qq = p1, hist = p2, fitted = p3))
}

```
### 21. Function to Check normality of random intercepts for each grouping factor 
```{r}

# Function to extract and check random effects normality
check_random_effects_normality <- function(model, model_name) {
  # Extract random effects
  random_effects <- ranef(model)
  
  plots_list <- list()
  
  # For each grouping factor
  for(group_name in names(random_effects)) {
    re_data <- random_effects[[group_name]]
    
    # Q-Q plot for random effects
    if(ncol(re_data) > 0) {
      # For intercept-only random effects
      re_values <- re_data[,1]  # Assuming intercept is first column
      
      qq_data <- data.frame(sample = re_values)
      
      p_qq <- ggplot(qq_data, aes(sample = sample)) +
        stat_qq() +
        stat_qq_line(color = "red") +
        ggtitle(paste("Random Effects Q-Q:", model_name, "-", group_name)) +
        theme_minimal()
      
      # Histogram
      p_hist <- ggplot(qq_data, aes(x = sample)) +
        geom_histogram(aes(y = ..density..), bins = 15, alpha = 0.7) +
        geom_density(color = "red", size = 1) +
        stat_function(fun = dnorm, 
                      args = list(mean = mean(re_values), sd = sd(re_values)), 
                      color = "blue", linetype = "dashed") +
        ggtitle(paste("Random Effects Histogram:", model_name, "-", group_name)) +
        theme_minimal()
      
      plots_list[[paste0(group_name, "_qq")]] <- p_qq
      plots_list[[paste0(group_name, "_hist")]] <- p_hist
    }
  }
  
  return(plots_list)
}
```

### 22. Function to perform formal normality tests
```{r}
# Function for formal normality tests
formal_normality_tests <- function(model, model_name) {
  # Standardized residuals
  std_resid <- residuals(model, type = "pearson", scaled = TRUE)
  
  # Shapiro-Wilk test (careful with large samples)
  if(length(std_resid) <= 5000) {
    shapiro_result <- shapiro.test(std_resid)
  } else {
    # For large samples, take a random subset
    set.seed(123)
    sample_resid <- sample(std_resid, 5000)
    shapiro_result <- shapiro.test(sample_resid)
    cat("Note: Shapiro-Wilk performed on random sample of 5000 residuals\n")
  }
  
  # Anderson-Darling test (more powerful for large samples)
  if(require(nortest, quietly = TRUE)) {
    ad_result <- ad.test(std_resid)
  } else {
    ad_result <- NULL
    cat("Install 'nortest' package for Anderson-Darling test\n")
  }
  
  # Random effects tests
  random_effects <- ranef(model)
  re_tests <- list()
  
  for(group_name in names(random_effects)) {
    re_values <- random_effects[[group_name]][,1]
    
    # Check if we have enough observations and variance
    if(length(re_values) > 3) {  # Need at least 4 observations for Shapiro
      # Check if values are not all identical (variance > 0)
      if(var(re_values) > 1e-10) {  # Small threshold for numerical precision
        if(length(re_values) <= 5000) {
          tryCatch({
            re_tests[[group_name]] <- shapiro.test(re_values)
          }, error = function(e) {
            cat("Warning: Shapiro test failed for", group_name, ":", e$message, "\n")
            re_tests[[group_name]] <<- list(statistic = NA, p.value = NA, note = "Test failed")
          })
        } else {
          cat("Too many random effects for", group_name, "- skipping test\n")
          re_tests[[group_name]] <- list(statistic = NA, p.value = NA, note = "Too many observations")
        }
      } else {
        cat("Random effects for", group_name, "have zero variance (boundary fit) - skipping normality test\n")
        re_tests[[group_name]] <- list(statistic = NA, p.value = NA, note = "Zero variance")
      }
    } else {
      cat("Too few random effects for", group_name, "- skipping test\n")
      re_tests[[group_name]] <- list(statistic = NA, p.value = NA, note = "Too few observations")
    }
  }
  
  return(list(
    model = model_name,
    residuals_shapiro = shapiro_result,
    residuals_ad = ad_result,
    random_effects = re_tests
  ))
}
```

### 23. applying the functions to the models from section III
```{r}
# Check attractiveness model
cat("=== ATTRACTIVENESS IMAGE MODEL NORMALITY CHECKS ===\n")
attract_resid <- extract_residuals(model_attract_image, "Attractiveness, Image")
attract_plots <- check_residual_normality(attract_resid)
attract_re_plots <- check_random_effects_normality(model_attract_image, "Attractiveness, Image")
attract_tests <- formal_normality_tests(model_attract_image, "Attractiveness, Image")

# Check wealth model
cat("\n=== WEALTH MODEL NORMALITY CHECKS ===\n")
wealth_resid <- extract_residuals(model_wealth_image, "Wealth, Image")
wealth_plots <- check_residual_normality(wealth_resid)
wealth_re_plots <- check_random_effects_normality(model_wealth_image, "Wealth, Image")
wealth_tests <- formal_normality_tests(model_wealth_image, "Wealth, Image")
```

### 24. Visualizing the results
```{r}
# Print test results
print_normality_results <- function(test_results) {
  cat("Model:", test_results$model, "\n")
  cat("Residuals Shapiro-Wilk: W =", round(test_results$residuals_shapiro$statistic, 4),
      ", p =", round(test_results$residuals_shapiro$p.value, 6), "\n")
  
  if(!is.null(test_results$residuals_ad)) {
    cat("Residuals Anderson-Darling: A =", round(test_results$residuals_ad$statistic, 4),
        ", p =", round(test_results$residuals_ad$p.value, 6), "\n")
  }
  
  cat("Random Effects Tests:\n")
  for(group in names(test_results$random_effects)) {
    result <- test_results$random_effects[[group]]
    if(!is.na(result$statistic)) {
      cat("  ", group, ": W =", round(result$statistic, 4),
          ", p =", round(result$p.value, 4), "\n")
    } else {
      cat("  ", group, ": Test not performed -", result$note, "\n")
    }
  }
  cat("\n")
}

print_normality_results(attract_tests)
print_normality_results(wealth_tests)

# Display plots 
attract_plots$qq
cat("Figure B5.1. Q-Q plot of standardized residuals for attractiveness ratings (image stimuli). 
    Points closely following the reference line (red), 
    indicate approximate normality of residuals.")
attract_plots$hist
cat("Figure B5.2. Histogram of standardized residuals for attractiveness ratings (image stimuli). 
    Red line shows kernel density estimate; 
    blue dashed line shows theoretical normal distribution (μ=0, σ=1).")
attract_plots$fitted
cat("Figure B5.3. Standardized residuals versus fitted values for attractiveness ratings (image stimuli). 
    Red loess curve and horizontal reference line assess homoscedasticity assumption. 
    No systematic patterns indicate appropriate model fit.")
attract_re_plots$`Model:block_qq`
cat("Figure B5.4. Q-Q plot of random intercepts for Model:block grouping factor (attractiveness, image stimuli). 
    Assesses normality assumption for nested random effects structure.")
attract_re_plots$code_qq
cat("Figure B5.5. Q-Q plot of random intercepts for rater (code) grouping factor (attractiveness, image stimuli). 
    Assesses normality assumption for individual rater effects.")
wealth_plots$qq
cat("Figure B5.6. Q-Q plot of standardized residuals for wealth perception ratings (image stimuli).
    Points closely following the reference line (red), 
    indicate approximate normality of residuals.")
wealth_plots$hist
cat("Figure B5.7. Histogram of standardized residuals for wealth perception ratings (image stimuli). 
    Red line shows kernel density estimate; 
    blue dashed line shows theoretical normal distribution (μ=0, σ=1).")
wealth_plots$fitted
cat("Figure B5.8. Standardized residuals versus fitted values for wealth perception ratings (image stimuli). 
    Red loess curve and horizontal reference line assess homoscedasticity assumption.")
wealth_re_plots$`Model:block_qq`
cat("Figure B5.9. Q-Q plot of random intercepts for Model:block grouping factor (wealth, image stimuli). 
    Assesses normality assumption for nested random effects structure.")
wealth_re_plots$code_qq
cat("Figure B5.10. Q-Q plot of random intercepts for rater (code) grouping factor (wealth, image stimuli). 
    Assesses normality assumption for individual rater effects.")
```

### 25. Diagnostic for Boundary fits and random effects variance
```{r}
# Function to examine random effects variance components
examine_random_effects <- function(model, model_name) {
  cat("=== RANDOM EFFECTS EXAMINATION:", model_name, "===\n")
  
  # Check if model has boundary fit
  if(isSingular(model)) {
    cat("WARNING: Model has singular/boundary fit - some variance components are zero\n")
  }
  
  # Variance components
  vc <- VarCorr(model)
  cat("Variance Components:\n")
  print(vc)
  
  # Extract and examine random effects
  random_effects <- ranef(model)
  
  for(group_name in names(random_effects)) {
    re_values <- random_effects[[group_name]][,1]
    cat("\nRandom Effects for", group_name, ":\n")
    cat("  Number of levels:", length(re_values), "\n")
    cat("  Range:", round(range(re_values), 4), "\n")
    cat("  Mean:", round(mean(re_values), 4), "\n")
    cat("  SD:", round(sd(re_values), 4), "\n")
    cat("  Variance:", round(var(re_values), 6), "\n")
    
    # Check if effectively zero variance
    if(var(re_values) < 1e-10) {
      cat("  ** Near-zero variance detected (boundary fit)\n")
    }
    
    # Quick normality check for non-zero variance groups
    if(var(re_values) > 1e-10 && length(re_values) > 5) {
      cat("  Quick normality assessment:\n")
      cat("    Skewness:", round(moments::skewness(re_values), 3), "\n")
      cat("    Kurtosis:", round(moments::kurtosis(re_values), 3), "\n")
    }
  }
  cat("\n")
}

# Alternative visualization showing residuals by nested structure
plot_residuals_by_structure <- function(model, model_name) {
  # Get residuals and group information
  model_data <- model@frame
  resids <- residuals(model, type = "pearson", scaled = TRUE)
  
  # Add residuals to data
  plot_data <- data.frame(
    residuals = resids,
    block = model_data$block,
    Model = model_data$Model,
    code = model_data$code
  )
  
  # Residuals by block/Model
  p1 <- xyplot(residuals ~ as.numeric(Model) | block, 
               data = plot_data,
               type = c("p", "smooth"),
               main = paste("Residuals by Block/Model:", model_name),
               xlab = "Model", ylab = "Standardized Residuals")
  
  return(p1)
}

# Example usage after running the main analysis:
examine_random_effects(model_attract_image, "Attractiveness")
examine_random_effects(model_wealth_image, "Wealth")
plot_residuals_by_structure(model_attract_image, "Attractiveness")
cat("Figure B5.11. Standardized residuals by nested structure (Block/Model) for attractiveness ratings. 
    Panel plot shows residual patterns across experimental blocks
    with loess smoothing curves to detect systematic variation.")
plot_residuals_by_structure(model_wealth_image, "Wealth")
cat("Figure B5.12. Standardized residuals by nested structure (Block/Model) for wealth perception ratings.
    Panel plot shows residual patterns across experimental blocks
    with loess smoothing curves to detect systematic variation.")

```



## **PART VI: Supplement section B6: Power Analysis** 

### Stimulus-Level Power Sensitivity Analysis
```{r}
# vary effect size to find minimum detectable
powerCurve(model_attract_factorial_image, 
           test = fixed("Condition"), 
           along = "Model",  # varying number of models
           breaks = c(20, 30, 40, 50, 55))

powerCurve(model_wealth_factorial_image, 
           test = fixed("Condition"),
           along = "Model",  # varying number of models
           breaks = c(20, 30, 40, 50, 55))
```


### Rater level sample power analysis
```{r}
# Power Analysis for 2x2 Factorial Mixed Models

# PART 1: EXTRACT PARAMETERS FROM FITTED MODELS

cat("2x2 Factorial Design: Trait_Exaggeration × Cost\n")

# Function to extract all relevant information from a fitted model
extract_model_info <- function(model, model_name) {
  cat("\n", rep("=", 70), "\n", sep = "")
  cat("MODEL:", model_name, "\n")
  cat(rep("=", 70), "\n\n", sep = "")
  
  # Fixed effects
  fixed_effects <- fixef(model)
  
  # Get summary for standard errors and p-values
  model_summary <- summary(model)
  
  # Random effects (variance components)
  random_effects <- VarCorr(model)
  
  # Residual variance
  residual_sd <- sigma(model)
  
  return(list(
    fixed = fixed_effects,
    summary = model_summary,
    random = random_effects,
    residual_sd = residual_sd,
    n_obs = nobs(model)
  ))
}

# Extract information from both models
info_attract <- extract_model_info(model_attract_factorial_image, 
                                   "ATTRACTIVENESS - IMAGE STIMULI")
info_wealth <- extract_model_info(model_wealth_factorial_image, 
                                  "WEALTH - IMAGE STIMULI")


# PART 2: ACHIEVED POWER ANALYSIS (Power for observed effect sizes)

cat("\n", rep("=", 70), "\n", sep = "")
cat("STEP 2: ACHIEVED POWER ANALYSIS\n")
cat("(Power achieved with observed effect sizes)\n")
cat(rep("=", 70), "\n\n", sep = "")

# Function to calculate achieved power for main effects
calculate_achieved_power <- function(model, model_name, n_sim = 1000) {
  
  cat("\nCalculating achieved power for:", model_name, "\n")
  cat("Number of simulations:", n_sim, "\n")
  cat("This may take a few minutes...\n\n")
  
  results <- list()
  
  # Power for Trait_Exaggeration main effect
  cat("Analyzing: Main effect of Trait_Exaggeration...\n")
  power_trait <- tryCatch({
    powerSim(model, 
             test = fixed("Trait_Exaggeration1", "z"),
             nsim = n_sim,
             progress = TRUE,
             seed = 123)
  }, error = function(e) {
    cat("Error in Trait_Exaggeration power calculation:", e$message, "\n")
    return(NULL)
  })
  
  if(!is.null(power_trait)) {
    results$trait_exaggeration <- power_trait
    cat("\nTrait_Exaggeration Power Results:\n")
    print(power_trait)
    cat("\n")
  }
  
  # Power for Cost main effect
  cat("\nAnalyzing: Main effect of Cost...\n")
  power_cost <- tryCatch({
    powerSim(model, 
             test = fixed("Cost1", "z"),
             nsim = n_sim,
             progress = TRUE,
             seed = 124)
  }, error = function(e) {
    cat("Error in Cost power calculation:", e$message, "\n")
    return(NULL)
  })
  
  if(!is.null(power_cost)) {
    results$cost <- power_cost
    cat("\nCost Power Results:\n")
    print(power_cost)
    cat("\n")
  }
  
  return(results)
}

# Calculate achieved power (using fewer simulations for speed, increase for final analysis)
achieved_power_attract <- calculate_achieved_power(
  model_attract_factorial_image, 
  "ATTRACTIVENESS - IMAGE",
  n_sim = 1000  # Increase to 1000+ for final analysis
)

achieved_power_wealth <- calculate_achieved_power(
  model_wealth_factorial_image, 
  "WEALTH - IMAGE",
  n_sim = 1000  # Increase to 1000+ for final analysis
)


# PART 3: MINIMUM DETECTABLE EFFECT SIZE (MDES) ANALYSIS

cat("\n", rep("=", 70), "\n", sep = "")
cat("STEP 3: MINIMUM DETECTABLE EFFECT SIZE ANALYSIS\n")
cat("(Smallest effect detectable with 80% power)\n")
cat(rep("=", 70), "\n\n", sep = "")

# Function to find minimum detectable effect size for 80% power
find_mdes <- function(model, effect_name, model_name, 
                      target_power = 0.80, n_sim = 200) {
  
  cat("\nFinding MDES for:", effect_name, "in", model_name, "\n")
  cat("Target power:", target_power, "\n")
  cat("This will test multiple effect sizes...\n\n")
  
  # Get the observed effect size
  observed_effect <- fixef(model)[effect_name]
  cat("Observed effect size:", round(observed_effect, 4), "\n")
  
  # Create a power curve by testing different effect sizes
  # Test from 20% to 200% of observed effect
  effect_multipliers <- seq(0.2, 2.0, by = 0.2)
  
  power_curve_results <- data.frame(
    effect_size = numeric(),
    power = numeric(),
    lower_ci = numeric(),
    upper_ci = numeric()
  )
  
  for (mult in effect_multipliers) {
    test_effect <- observed_effect * mult
    
    cat("Testing effect size:", round(test_effect, 4), 
        "(", round(mult * 100, 0), "% of observed)...\n", sep = "")
    
    # Modify the model with the new effect size
    model_test <- model
    fixef(model_test)[effect_name] <- test_effect
    
    # Calculate power
    power_result <- tryCatch({
      powerSim(model_test, 
               test = fixed(effect_name, "z"),
               nsim = n_sim,
               progress = FALSE,
               seed = 125)
    }, error = function(e) {
      cat("Error:", e$message, "\n")
      return(NULL)
    })
    
    if(!is.null(power_result)) {
      power_value <- summary(power_result)$mean
      ci <- confint(power_result)
      
      power_curve_results <- rbind(power_curve_results, 
                                   data.frame(
                                     effect_size = test_effect,
                                     power = power_value,
                                     lower_ci = ci[1],
                                     upper_ci = ci[2]
                                   ))
      
      cat("  Power:", round(power_value, 3), 
          " [", round(ci[1], 3), ", ", round(ci[2], 3), "]\n", sep = "")
    }
  }
  
  # Find the effect size closest to target power
  if(nrow(power_curve_results) > 0) {
    power_diff <- abs(power_curve_results$power - target_power)
    mdes_idx <- which.min(power_diff)
    mdes <- power_curve_results$effect_size[mdes_idx]
    mdes_power <- power_curve_results$power[mdes_idx]
    
    cat("\n** MINIMUM DETECTABLE EFFECT SIZE **\n")
    cat("Effect size for ~", round(target_power * 100, 0), "% power: ", 
        round(mdes, 4), "\n", sep = "")
    cat("Achieved power at this effect size: ", round(mdes_power, 3), "\n", sep = "")
    cat("This is ", round((mdes / observed_effect) * 100, 1), 
        "% of the observed effect\n\n", sep = "")
  }
  
  return(power_curve_results)
}

# Calculate MDES for Attractiveness model
cat("\n")
cat(rep("-", 70), "\n", sep = "")
cat("ATTRACTIVENESS MODEL - MDES Analysis\n")
cat(rep("-", 70), "\n", sep = "")

mdes_attract_trait <- find_mdes(
  model_attract_factorial_image,
  "Trait_Exaggeration1",
  "ATTRACTIVENESS - Trait_Exaggeration",
  target_power = 0.80,
  n_sim = 200  # Increase for more precise estimates
)

mdes_attract_cost <- find_mdes(
  model_attract_factorial_image,
  "Cost1",
  "ATTRACTIVENESS - Cost",
  target_power = 0.80,
  n_sim = 200
)

# Calculate MDES for Wealth model
cat("\n")
cat(rep("-", 70), "\n", sep = "")
cat("WEALTH MODEL - MDES Analysis\n")
cat(rep("-", 70), "\n", sep = "")

mdes_wealth_trait <- find_mdes(
  model_wealth_factorial_image,
  "Trait_Exaggeration1",
  "WEALTH - Trait_Exaggeration",
  target_power = 0.80,
  n_sim = 200
)

mdes_wealth_cost <- find_mdes(
  model_wealth_factorial_image,
  "Cost1",
  "WEALTH - Cost",
  target_power = 0.80,
  n_sim = 200
)


# PART 4: CREATE VISUALIZATION OF POWER CURVES


cat("\n", rep("=", 70), "\n", sep = "")
cat("STEP 4: CREATING POWER CURVE VISUALIZATIONS\n")
cat(rep("=", 70), "\n\n", sep = "")

# Function to create power curve plot
create_power_plot <- function(power_data, effect_name, model_name, 
                              observed_effect, filename) {
  
  if(nrow(power_data) == 0) {
    cat("No data to plot for", effect_name, "\n")
    return(NULL)
  }
  
  # Create plot
  p <- ggplot(power_data, aes(x = effect_size, y = power)) +
    geom_line(color = "blue", size = 1.2) +
    geom_ribbon(aes(ymin = lower_ci, ymax = upper_ci), 
                alpha = 0.2, fill = "blue") +
    geom_point(color = "blue", size = 2) +
    geom_hline(yintercept = 0.80, linetype = "dashed", 
               color = "red", size = 0.8) +
    geom_vline(xintercept = observed_effect, linetype = "dashed", 
               color = "darkgreen", size = 0.8) +
    annotate("text", x = observed_effect, y = 0.05, 
             label = paste("Observed effect\n", round(observed_effect, 3)),
             color = "darkgreen", hjust = -0.1, size = 3) +
    annotate("text", x = min(power_data$effect_size), y = 0.82, 
             label = "80% power target", 
             color = "red", hjust = 0, size = 3) +
    labs(title = paste("Power Curve:", model_name, "-", effect_name),
         subtitle = "Shaded area represents 95% confidence interval",
         x = "Effect Size (Model Coefficient)",
         y = "Statistical Power") +
    theme_minimal() +
    theme(plot.title = element_text(face = "bold", size = 14),
          plot.subtitle = element_text(size = 10),
          axis.title = element_text(size = 12),
          panel.grid.minor = element_blank())
  
  ggsave(filename, p, width = 10, height = 6, dpi = 300)
  cat("Saved plot:", filename, "\n")
  
  return(p)
}

# Create plots for all effects
plot_attract_trait <- create_power_plot(
  mdes_attract_trait,
  "Trait Exaggeration",
  "Attractiveness",
  fixef(model_attract_factorial_image)["Trait_Exaggeration1"],
  "power_curve_attractiveness_trait.png"
)

plot_attract_cost <- create_power_plot(
  mdes_attract_cost,
  "Cost",
  "Attractiveness",
  fixef(model_attract_factorial_image)["Cost1"],
  "power_curve_attractiveness_cost.png"
)

plot_wealth_trait <- create_power_plot(
  mdes_wealth_trait,
  "Trait Exaggeration",
  "Wealth",
  fixef(model_wealth_factorial_image)["Trait_Exaggeration1"],
  "power_curve_wealth_trait.png"
)

plot_wealth_cost <- create_power_plot(
  mdes_wealth_cost,
  "Cost",
  "Wealth",
  fixef(model_wealth_factorial_image)["Cost1"],
  "power_curve_wealth_cost.png"
)



# PART 5: SUMMARY REPORT


cat("\n", rep("=", 70), "\n", sep = "")
cat("FINAL SUMMARY REPORT\n")
cat(rep("=", 70), "\n\n", sep = "")

# Function to create summary table
create_summary_table <- function(model, model_name, achieved_power, mdes_trait, mdes_cost) {
  
  cat("\n", model_name, "\n", sep = "")
  cat(rep("-", 70), "\n", sep = "")
  
  # Get observed effects
  obs_trait <- fixef(model)["Trait_Exaggeration1"]
  obs_cost <- fixef(model)["Cost1"]
  
  # Get achieved power
  power_trait <- if(!is.null(achieved_power$trait_exaggeration)) {
    summary(achieved_power$trait_exaggeration)$mean
  } else NA
  
  power_cost <- if(!is.null(achieved_power$cost)) {
    summary(achieved_power$cost)$mean
  } else NA
  
  # Get MDES (closest to 80% power)
  mdes_trait_80 <- if(nrow(mdes_trait) > 0) {
    idx <- which.min(abs(mdes_trait$power - 0.80))
    mdes_trait$effect_size[idx]
  } else NA
  
  mdes_cost_80 <- if(nrow(mdes_cost) > 0) {
    idx <- which.min(abs(mdes_cost$power - 0.80))
    mdes_cost$effect_size[idx]
  } else NA
  
  # Create summary data frame
  summary_df <- data.frame(
    Effect = c("Trait_Exaggeration", "Cost"),
    Observed_Effect = round(c(obs_trait, obs_cost), 4),
    Achieved_Power = round(c(power_trait, power_cost), 3),
    MDES_80pct_Power = round(c(mdes_trait_80, mdes_cost_80), 4),
    MDES_as_pct_of_observed = round(c(mdes_trait_80/obs_trait, 
                                       mdes_cost_80/obs_cost) * 100, 1)
  )
  
  print(summary_df)
  cat("\n")
  
  return(summary_df)
}

summary_attract <- create_summary_table(
  model_attract_factorial_image,
  "ATTRACTIVENESS MODEL",
  achieved_power_attract,
  mdes_attract_trait,
  mdes_attract_cost
)

summary_wealth <- create_summary_table(
  model_wealth_factorial_image,
  "WEALTH MODEL",
  achieved_power_wealth,
  mdes_wealth_trait,
  mdes_wealth_cost
)
```


## **PART VII: Supplement B7: Expected versus Observed Ratings of Isolated Item Photographs**

At the end of each rating session, participants additionally viewed standardised close-up photographs of the four experimental footwear items (Economy Flat, Economy Heel, Luxury Flat, Luxury Heel), presented independently of any model, and rated on the same Likert scales responding to estimate the appearance of attractiveness and wealth of an average hypothetical user. These isolated item ratings provide an **Expected** score, which can be contrasted with the **Observed** score obtained when the corresponding item was actually worn by a stimulus model. This section reports the data preparation, comparison, and inferential testing of these Expected versus Observed difference scores.

The Expected and Observed difference scores are defined as follows:

**Expected [per item] = Isolated item-photograph rating − Control condition mean (image stimuli)**
**Observed [per condition] = Worn-item condition mean rating − Control condition mean**

Both scores are referenced against the same control (no footwear) baseline, so that a divergence between Expected and Observed indicates that the isolated appraisal of an item over- or under-predicts its effect once embodied by a person.

### 26. Data Preparation for the Expected versus Observed Comparison

```{r}
# Aggregating worn-item mean ratings per participant, condition, stimulus type,
# and dimension, using abbreviated codes consistent with the difference-score
# naming convention (C/EF/EH/LF/LH; Img/Vid; Att/Wlt)
body_data_wide_means <- body_data %>%
  mutate(
    Condition_short = case_when(
      Condition == "Control"      ~ "C",
      Condition == "Economy Flat" ~ "EF",
      Condition == "Economy Heel" ~ "EH",
      Condition == "Luxury Flat"  ~ "LF",
      Condition == "Luxury Heel"  ~ "LH",
      TRUE ~ NA_character_
    ),
    Stimuli_short = case_when(
      Stimuli_Type == "Image" ~ "Img",
      Stimuli_Type == "Video" ~ "Vid",
      TRUE ~ NA_character_
    ),
    Dimension_short = case_when(
      Dimension == "Attractiveness" ~ "Att",
      Dimension == "Wealth"         ~ "Wlt",
      TRUE ~ NA_character_
    )
  ) %>%
  group_by(code, Condition_short, Stimuli_short, Dimension_short) %>%
  summarise(mean_rating = mean(Rating, na.rm = TRUE), .groups = "drop") %>%
  unite("variable_name", c(Condition_short, Stimuli_short, Dimension_short), sep = "_") %>%
  pivot_wider(
    id_cols = code,
    names_from = variable_name,
    values_from = mean_rating,
    names_prefix = "MeanR_"
  )

# Extracting the isolated item-photograph ratings and relevant covariates
# (one row per participant, as these ratings were collected once per session)
item_ratings_df <- body_data %>%
  select(code, sex, age, monthlyincome,
         Economy_Flat_Att, Economy_Flat_Wlt,
         Economy_Heel_Att, Economy_Heel_Wlt,
         Luxury_Flat_Att, Luxury_Flat_Wlt,
         Luxury_Heel_Att, Luxury_Heel_Wlt) %>%
  distinct(code, .keep_all = TRUE)

# Merging isolated item ratings with worn-item condition means
exp_obs_df <- item_ratings_df %>%
  left_join(body_data_wide_means, by = "code")

# Calculating Expected differences (isolated item rating - control mean, image stimuli)
exp_obs_df <- exp_obs_df %>%
  mutate(
    Exp_EF_Att = Economy_Flat_Att - MeanR_C_Img_Att,
    Exp_EH_Att = Economy_Heel_Att - MeanR_C_Img_Att,
    Exp_LF_Att = Luxury_Flat_Att  - MeanR_C_Img_Att,
    Exp_LH_Att = Luxury_Heel_Att  - MeanR_C_Img_Att,

    Exp_EF_Wlt = Economy_Flat_Wlt - MeanR_C_Img_Wlt,
    Exp_EH_Wlt = Economy_Heel_Wlt - MeanR_C_Img_Wlt,
    Exp_LF_Wlt = Luxury_Flat_Wlt  - MeanR_C_Img_Wlt,
    Exp_LH_Wlt = Luxury_Heel_Wlt  - MeanR_C_Img_Wlt
  )

# Calculating Observed differences (worn-item condition mean - control mean),
# separately for image and video stimuli
exp_obs_df <- exp_obs_df %>%
  mutate(
    Obs_EF_Img_Att = MeanR_EF_Img_Att - MeanR_C_Img_Att,
    Obs_EH_Img_Att = MeanR_EH_Img_Att - MeanR_C_Img_Att,
    Obs_LF_Img_Att = MeanR_LF_Img_Att - MeanR_C_Img_Att,
    Obs_LH_Img_Att = MeanR_LH_Img_Att - MeanR_C_Img_Att,

    Obs_EF_Vid_Att = MeanR_EF_Vid_Att - MeanR_C_Vid_Att,
    Obs_EH_Vid_Att = MeanR_EH_Vid_Att - MeanR_C_Vid_Att,
    Obs_LF_Vid_Att = MeanR_LF_Vid_Att - MeanR_C_Vid_Att,
    Obs_LH_Vid_Att = MeanR_LH_Vid_Att - MeanR_C_Vid_Att,

    Obs_EF_Img_Wlt = MeanR_EF_Img_Wlt - MeanR_C_Img_Wlt,
    Obs_EH_Img_Wlt = MeanR_EH_Img_Wlt - MeanR_C_Img_Wlt,
    Obs_LF_Img_Wlt = MeanR_LF_Img_Wlt - MeanR_C_Img_Wlt,
    Obs_LH_Img_Wlt = MeanR_LH_Img_Wlt - MeanR_C_Img_Wlt,

    Obs_EF_Vid_Wlt = MeanR_EF_Vid_Wlt - MeanR_C_Vid_Wlt,
    Obs_EH_Vid_Wlt = MeanR_EH_Vid_Wlt - MeanR_C_Vid_Wlt,
    Obs_LF_Vid_Wlt = MeanR_LF_Vid_Wlt - MeanR_C_Vid_Wlt,
    Obs_LH_Vid_Wlt = MeanR_LH_Vid_Wlt - MeanR_C_Vid_Wlt
  )

# Ensuring sex is a properly labelled factor for subsequent stratified analyses
exp_obs_df <- exp_obs_df %>%
  mutate(sex = factor(sex, levels = c("Female", "Male")))


# Constructing long-format Expected-score data for the 2x2 factorial analysis
# (Section 29), analogous to the Trait_Exaggeration x Cost structure used for
# the Observed data in Supplement B4
exp_long_att <- exp_obs_df %>%
  select(code, Exp_EF_Att, Exp_EH_Att, Exp_LF_Att, Exp_LH_Att) %>%
  pivot_longer(cols = starts_with("Exp_"), names_to = "Condition_code", values_to = "Rating") %>%
  mutate(
    Condition_code = gsub("Exp_|_Att", "", Condition_code),
    Trait_Exaggeration = factor(ifelse(grepl("H", Condition_code), "Heel", "Flat"),
                                 levels = c("Flat", "Heel")),
    Cost = factor(ifelse(grepl("^E", Condition_code), "Economy", "Luxury"),
                   levels = c("Economy", "Luxury"))
  )

exp_long_wlt <- exp_obs_df %>%
  select(code, Exp_EF_Wlt, Exp_EH_Wlt, Exp_LF_Wlt, Exp_LH_Wlt) %>%
  pivot_longer(cols = starts_with("Exp_"), names_to = "Condition_code", values_to = "Rating") %>%
  mutate(
    Condition_code = gsub("Exp_|_Wlt", "", Condition_code),
    Trait_Exaggeration = factor(ifelse(grepl("H", Condition_code), "Heel", "Flat"),
                                 levels = c("Flat", "Heel")),
    Cost = factor(ifelse(grepl("^E", Condition_code), "Economy", "Luxury"),
                   levels = c("Economy", "Luxury"))
  )

# Sum coding (effects coding), consistent with the B4 factorial models
contrasts(exp_long_att$Trait_Exaggeration) <- contr.sum(2)
contrasts(exp_long_att$Cost) <- contr.sum(2)
contrasts(exp_long_wlt$Trait_Exaggeration) <- contr.sum(2)
contrasts(exp_long_wlt$Cost) <- contr.sum(2)
```

### 27. Paired-Samples Comparisons: Expected versus Observed Differences (Overall Sample)

Paired-samples *t*-tests were conducted for each condition, separately for the Attractiveness and Wealth dimensions and for image and video stimuli, testing whether the Expected difference score (isolated item photograph) differed statistically significantly from the Observed difference score (worn item).

```{r}
# Function to extract and format paired t-test results into a summary table
extract_paired_results <- function(test_list) {
  results_df <- data.frame(
    Condition = names(test_list),
    t_value   = sapply(test_list, function(x) round(x$statistic, 3)),
    df        = sapply(test_list, function(x) round(x$parameter, 1)),
    p_value   = sapply(test_list, function(x) round(x$p.value, 4)),
    mean_diff = sapply(test_list, function(x) round(x$estimate, 3)),
    significance = sapply(test_list, function(x)
      ifelse(x$p.value < 0.001, "***",
             ifelse(x$p.value < 0.01, "**",
                    ifelse(x$p.value < 0.05, "*", "ns"))))
  )
  results_df$Condition <- factor(results_df$Condition,
                                  levels = c("EF", "EH", "LF", "LH"),
                                  labels = c("Economy Flat", "Economy Heel",
                                             "Luxury Flat", "Luxury Heel"))
  return(results_df)
}

# Attractiveness - Image stimuli
att_img_paired_tests <- list(
  EF = t.test(exp_obs_df$Exp_EF_Att, exp_obs_df$Obs_EF_Img_Att, paired = TRUE),
  EH = t.test(exp_obs_df$Exp_EH_Att, exp_obs_df$Obs_EH_Img_Att, paired = TRUE),
  LF = t.test(exp_obs_df$Exp_LF_Att, exp_obs_df$Obs_LF_Img_Att, paired = TRUE),
  LH = t.test(exp_obs_df$Exp_LH_Att, exp_obs_df$Obs_LH_Img_Att, paired = TRUE)
)

# Attractiveness - Video stimuli
att_vid_paired_tests <- list(
  EF = t.test(exp_obs_df$Exp_EF_Att, exp_obs_df$Obs_EF_Vid_Att, paired = TRUE),
  EH = t.test(exp_obs_df$Exp_EH_Att, exp_obs_df$Obs_EH_Vid_Att, paired = TRUE),
  LF = t.test(exp_obs_df$Exp_LF_Att, exp_obs_df$Obs_LF_Vid_Att, paired = TRUE),
  LH = t.test(exp_obs_df$Exp_LH_Att, exp_obs_df$Obs_LH_Vid_Att, paired = TRUE)
)

# Wealth - Image stimuli
wlt_img_paired_tests <- list(
  EF = t.test(exp_obs_df$Exp_EF_Wlt, exp_obs_df$Obs_EF_Img_Wlt, paired = TRUE),
  EH = t.test(exp_obs_df$Exp_EH_Wlt, exp_obs_df$Obs_EH_Img_Wlt, paired = TRUE),
  LF = t.test(exp_obs_df$Exp_LF_Wlt, exp_obs_df$Obs_LF_Img_Wlt, paired = TRUE),
  LH = t.test(exp_obs_df$Exp_LH_Wlt, exp_obs_df$Obs_LH_Img_Wlt, paired = TRUE)
)

# Wealth - Video stimuli
wlt_vid_paired_tests <- list(
  EF = t.test(exp_obs_df$Exp_EF_Wlt, exp_obs_df$Obs_EF_Vid_Wlt, paired = TRUE),
  EH = t.test(exp_obs_df$Exp_EH_Wlt, exp_obs_df$Obs_EH_Vid_Wlt, paired = TRUE),
  LF = t.test(exp_obs_df$Exp_LF_Wlt, exp_obs_df$Obs_LF_Vid_Wlt, paired = TRUE),
  LH = t.test(exp_obs_df$Exp_LH_Wlt, exp_obs_df$Obs_LH_Vid_Wlt, paired = TRUE)
)

kable(extract_paired_results(att_img_paired_tests),
      caption = "Attractiveness (Image Stimuli): Expected vs. Observed Differences")
kable(extract_paired_results(att_vid_paired_tests),
      caption = "Attractiveness (Video Stimuli): Expected vs. Observed Differences")
kable(extract_paired_results(wlt_img_paired_tests),
      caption = "Wealth (Image Stimuli): Expected vs. Observed Differences")
kable(extract_paired_results(wlt_vid_paired_tests),
      caption = "Wealth (Video Stimuli): Expected vs. Observed Differences")
```

### 28. Effect Sizes (Cohen's d) for Expected versus Observed Comparisons

```{r}
# Function to calculate Cohen's d for paired samples, handling missing data
get_paired_cohens_d <- function(x, y) {
  complete_cases <- complete.cases(x, y)
  x_clean <- x[complete_cases]
  y_clean <- y[complete_cases]
  diff_scores <- x_clean - y_clean
  round(mean(diff_scores) / sd(diff_scores), 3)
}

build_effect_size_table <- function(exp_prefix, obs_suffix, dimension_label) {
  data.frame(
    Condition = c("Economy Flat", "Economy Heel", "Luxury Flat", "Luxury Heel"),
    Cohens_d = c(
      get_paired_cohens_d(exp_obs_df[[paste0("Exp_EF_", exp_prefix)]], exp_obs_df[[paste0("Obs_EF_", obs_suffix)]]),
      get_paired_cohens_d(exp_obs_df[[paste0("Exp_EH_", exp_prefix)]], exp_obs_df[[paste0("Obs_EH_", obs_suffix)]]),
      get_paired_cohens_d(exp_obs_df[[paste0("Exp_LF_", exp_prefix)]], exp_obs_df[[paste0("Obs_LF_", obs_suffix)]]),
      get_paired_cohens_d(exp_obs_df[[paste0("Exp_LH_", exp_prefix)]], exp_obs_df[[paste0("Obs_LH_", obs_suffix)]])
    )
  )
}

att_img_es <- build_effect_size_table("Att", "Img_Att", "Attractiveness - Image")
att_vid_es <- build_effect_size_table("Att", "Vid_Att", "Attractiveness - Video")
wlt_img_es <- build_effect_size_table("Wlt", "Img_Wlt", "Wealth - Image")
wlt_vid_es <- build_effect_size_table("Wlt", "Vid_Wlt", "Wealth - Video")

kable(att_img_es, caption = "Effect Sizes: Attractiveness (Image Stimuli)")
kable(att_vid_es, caption = "Effect Sizes: Attractiveness (Video Stimuli)")
kable(wlt_img_es, caption = "Effect Sizes: Wealth (Image Stimuli)")
kable(wlt_vid_es, caption = "Effect Sizes: Wealth (Video Stimuli)")
```

### 29. 2×2 Factorial Analysis of Expected Scores (Trait Exaggeration × Cost)

To formally test whether the ordinal pattern visible in the Expected scores conforms to the hypothesized structure (H1A: Trait Exaggeration enhances Attractiveness; H1B: Cost enhances Wealth; H2: Trait Exaggeration × Cost interaction), a 2×2 factorial linear mixed-effects model was fitted to the Expected scores for each dimension, mirroring the model specification used for the Observed data in Supplement B4 (`Rating ~ Trait_Exaggeration * Cost`). A single random intercept for participant was retained; the `(1 | block/Model)` term used in B4 was omitted here, as the isolated item photographs were not associated with a specific stimulus model or presentation block. Because the Cost main effect on the Wealth model directly indexes whether participants correctly distinguished the luxury and economy items in isolation, this analysis additionally serves as a manipulation check on the cost manipulation; analogously, the Trait Exaggeration main effect on the Attractiveness model serves as a manipulation check on the heel manipulation.

**Attractiveness Model (Expected Scores)**
```{r}
model_exp_att_factorial <- lmer(Rating ~ Trait_Exaggeration * Cost + (1 | code), data = exp_long_att)
summary(model_exp_att_factorial)
```

ANOVA for 2×2 Factorial Model (Expected Attractiveness)
```{r}
anova(model_exp_att_factorial)
```

Estimated Marginal Means (Expected Attractiveness)
```{r}
emmeans_exp_att_trait <- emmeans(model_exp_att_factorial, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_exp_att_trait)

emmeans_exp_att_cost <- emmeans(model_exp_att_factorial, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_exp_att_cost)

emmeans_exp_att_interact <- emmeans(model_exp_att_factorial, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration x Cost:")
print(emmeans_exp_att_interact)
```

Pairwise Comparisons (Expected Attractiveness)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_exp_att_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_exp_att_interact2 <- emmeans(model_exp_att_factorial, ~ Cost | Trait_Exaggeration)
pairs(emmeans_exp_att_interact2, adjust = "tukey")
```

R-squared for Expected Attractiveness Model
```{r}
r_squared_exp_att <- r.squaredGLMM(model_exp_att_factorial)
print(r_squared_exp_att)
```

**Wealth Model (Expected Scores)**
```{r}
model_exp_wlt_factorial <- lmer(Rating ~ Trait_Exaggeration * Cost + (1 | code), data = exp_long_wlt)
summary(model_exp_wlt_factorial)
```

ANOVA for 2×2 Factorial Model (Expected Wealth)
```{r}
anova(model_exp_wlt_factorial)
```

Estimated Marginal Means (Expected Wealth)
```{r}
emmeans_exp_wlt_trait <- emmeans(model_exp_wlt_factorial, ~ Trait_Exaggeration)
print("Main Effect of Trait Exaggeration:")
print(emmeans_exp_wlt_trait)

emmeans_exp_wlt_cost <- emmeans(model_exp_wlt_factorial, ~ Cost)
print("Main Effect of Cost:")
print(emmeans_exp_wlt_cost)

emmeans_exp_wlt_interact <- emmeans(model_exp_wlt_factorial, ~ Trait_Exaggeration | Cost)
print("Interaction: Trait Exaggeration x Cost:")
print(emmeans_exp_wlt_interact)
```

Pairwise Comparisons (Expected Wealth)
```{r}
# Simple effects of Trait_Exaggeration within each Cost level
pairs(emmeans_exp_wlt_interact, adjust = "tukey")

# Simple effects of Cost within each Trait_Exaggeration level
emmeans_exp_wlt_interact2 <- emmeans(model_exp_wlt_factorial, ~ Cost | Trait_Exaggeration)
pairs(emmeans_exp_wlt_interact2, adjust = "tukey")
```

R-squared for Expected Wealth Model
```{r}
r_squared_exp_wlt <- r.squaredGLMM(model_exp_wlt_factorial)
print(r_squared_exp_wlt)
```

### 30. Descriptive Statistics for Expected and Observed Difference Scores

```{r}
get_diff_score_descriptives <- function(data, vars) {
  stats <- psych::describe(data[, vars])
  data.frame(
    Variable = rownames(stats),
    Mean = round(stats$mean, 2),
    SD = round(stats$sd, 2),
    Median = round(stats$median, 2),
    Min = round(stats$min, 2),
    Max = round(stats$max, 2)
  )
}

att_img_vars <- c("Exp_EF_Att", "Obs_EF_Img_Att", "Exp_EH_Att", "Obs_EH_Img_Att",
                   "Exp_LF_Att", "Obs_LF_Img_Att", "Exp_LH_Att", "Obs_LH_Img_Att")
att_vid_vars <- c("Exp_EF_Att", "Obs_EF_Vid_Att", "Exp_EH_Att", "Obs_EH_Vid_Att",
                   "Exp_LF_Att", "Obs_LF_Vid_Att", "Exp_LH_Att", "Obs_LH_Vid_Att")
wlt_img_vars <- c("Exp_EF_Wlt", "Obs_EF_Img_Wlt", "Exp_EH_Wlt", "Obs_EH_Img_Wlt",
                   "Exp_LF_Wlt", "Obs_LF_Img_Wlt", "Exp_LH_Wlt", "Obs_LH_Img_Wlt")
wlt_vid_vars <- c("Exp_EF_Wlt", "Obs_EF_Vid_Wlt", "Exp_EH_Wlt", "Obs_EH_Vid_Wlt",
                   "Exp_LF_Wlt", "Obs_LF_Vid_Wlt", "Exp_LH_Wlt", "Obs_LH_Vid_Wlt")

kable(get_diff_score_descriptives(exp_obs_df, att_img_vars), caption = "Descriptives: Attractiveness (Image Stimuli)")
kable(get_diff_score_descriptives(exp_obs_df, att_vid_vars), caption = "Descriptives: Attractiveness (Video Stimuli)")
kable(get_diff_score_descriptives(exp_obs_df, wlt_img_vars), caption = "Descriptives: Wealth (Image Stimuli)")
kable(get_diff_score_descriptives(exp_obs_df, wlt_vid_vars), caption = "Descriptives: Wealth (Video Stimuli)")
```

### 31. Visualization of Expected versus Observed Differences

The following plots follow the visual conventions established in Section B4 (`theme_minimal`, bordered facet panels, top-aligned bold legend) to maintain a consistent style across the supplementary analyses.

```{r fig.width=9, fig.height=7, out.width="100%", fig.align='center'}
# Preparing long-format summary data (mean and 95% CI) for plotting
prepare_exp_obs_plot_data <- function(data, exp_vars, obs_vars, dimension, stimuli) {
  summarise_ci <- function(x) {
    x <- x[!is.na(x)]
    n <- length(x)
    m <- mean(x)
    se <- sd(x) / sqrt(n)
    data.frame(mean = m, ci_lower = m - 1.96 * se, ci_upper = m + 1.96 * se)
  }

  exp_summary <- do.call(rbind, lapply(exp_vars, function(v) {
    cbind(Condition = v, Type = "Expected", summarise_ci(data[[v]]))
  }))
  obs_summary <- do.call(rbind, lapply(obs_vars, function(v) {
    cbind(Condition = v, Type = "Observed", summarise_ci(data[[v]]))
  }))

  combined <- rbind(exp_summary, obs_summary)
  combined$Condition <- factor(
    regmatches(combined$Condition, regexpr("EF|EH|LF|LH", combined$Condition)),
    levels = c("EF", "EH", "LF", "LH"),
    labels = c("Economy Flat", "Economy Heel", "Luxury Flat", "Luxury Heel")
  )
  combined$Type <- factor(combined$Type, levels = c("Expected", "Observed"))
  combined$Dimension <- dimension
  combined$Stimuli_Type <- stimuli
  return(combined)
}

plot_data_att_img <- prepare_exp_obs_plot_data(
  exp_obs_df,
  c("Exp_EF_Att", "Exp_EH_Att", "Exp_LF_Att", "Exp_LH_Att"),
  c("Obs_EF_Img_Att", "Obs_EH_Img_Att", "Obs_LF_Img_Att", "Obs_LH_Img_Att"),
  "Attractiveness", "Image"
)
plot_data_att_vid <- prepare_exp_obs_plot_data(
  exp_obs_df,
  c("Exp_EF_Att", "Exp_EH_Att", "Exp_LF_Att", "Exp_LH_Att"),
  c("Obs_EF_Vid_Att", "Obs_EH_Vid_Att", "Obs_LF_Vid_Att", "Obs_LH_Vid_Att"),
  "Attractiveness", "Video"
)
plot_data_wlt_img <- prepare_exp_obs_plot_data(
  exp_obs_df,
  c("Exp_EF_Wlt", "Exp_EH_Wlt", "Exp_LF_Wlt", "Exp_LH_Wlt"),
  c("Obs_EF_Img_Wlt", "Obs_EH_Img_Wlt", "Obs_LF_Img_Wlt", "Obs_LH_Img_Wlt"),
  "Wealth", "Image"
)
plot_data_wlt_vid <- prepare_exp_obs_plot_data(
  exp_obs_df,
  c("Exp_EF_Wlt", "Exp_EH_Wlt", "Exp_LF_Wlt", "Exp_LH_Wlt"),
  c("Obs_EF_Vid_Wlt", "Obs_EH_Vid_Wlt", "Obs_LF_Vid_Wlt", "Obs_LH_Vid_Wlt"),
  "Wealth", "Video"
)

exp_obs_plot_data <- rbind(plot_data_att_img, plot_data_att_vid,
                            plot_data_wlt_img, plot_data_wlt_vid)

p_exp_obs <- ggplot(exp_obs_plot_data,
                     aes(x = Condition, y = mean, color = Type, group = Type)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                width = 0.15, size = 0.7, position = position_dodge(width = 0.4)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey30", size = 0.6) +
  facet_grid(Dimension ~ Stimuli_Type, scales = "free_y") +
  scale_color_manual(values = c("Expected" = "#1B9E77", "Observed" = "#D95F02"),
                      name = "Score Type") +
  labs(x = NULL,
       y = "Difference from Control Rating",
       title = "Expected vs. Observed Differences from Control Condition",
       caption = "Dashed line represents the control condition baseline\nError bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    strip.background = element_rect(fill = "grey95", color = "black", size = 0.8),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
    plot.caption = element_text(hjust = 1, color = "grey40"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_exp_obs)

ggsave("expected_observed_comparison.png", p_exp_obs, width = 12, height = 9, dpi = 300, bg = "white")
ggsave("expected_observed_comparison.pdf", p_exp_obs, width = 12, height = 9, bg = "white")
```
Figure B7.1. Expected (isolated item photograph) versus Observed (worn item) differences from the control condition, by footwear condition, rating dimension, and stimulus type. Error bars represent 95% confidence intervals.

```{r fig.width=5, fig.height=7, out.width="70%", fig.align='center'}
# Image-only version of the Expected vs. Observed comparison, prepared for
# direct use in the manuscript main text. Video stimuli are excluded here,
# consistent with the Discussion's focus on Image stimuli given the
# walking-proficiency confound present in the Video condition.
exp_obs_plot_data_image <- rbind(plot_data_att_img, plot_data_wlt_img)

p_exp_obs_image <- ggplot(exp_obs_plot_data_image,
                           aes(x = Condition, y = mean, color = Type, group = Type)) +
  geom_point(size = 3, position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                width = 0.15, size = 0.7, position = position_dodge(width = 0.4)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey30", size = 0.6) +
  facet_grid(Dimension ~ ., scales = "free_y") +
  scale_color_manual(values = c("Expected" = "#1B9E77", "Observed" = "#D95F02"),
                      name = "Score Type") +
  labs(x = NULL,
       y = "Difference from Control Rating",
       title = "Expected vs. Observed Differences\nfrom Control Condition (Image Stimuli)",
       caption = "Dashed line represents the control condition baseline\nError bars represent 95% confidence intervals") +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA, size = 0.8),
    strip.background = element_rect(fill = "grey95", color = "black", size = 0.8),
    strip.text = element_text(size = 11, face = "bold"),
    legend.position = "top",
    legend.title = element_text(face = "bold"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 13),
    plot.caption = element_text(hjust = 1, color = "grey40"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

print(p_exp_obs_image)

ggsave("expected_observed_comparison_image_only.png", p_exp_obs_image,
       width = 6, height = 8, dpi = 300, bg = "white")
ggsave("expected_observed_comparison_image_only.pdf", p_exp_obs_image,
       width = 6, height = 8, bg = "white")
```
Figure B7.2. Expected versus Observed differences from the control condition, Image stimuli only. Error bars represent 95% confidence intervals.