---
output:
  pdf_document:
     latex_engine: xelatex
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(psych)
library(knitr)
library(kableExtra)
```

# **Supplement Section C: Brand Knowledge Scale**
## In this document;

## **• C.1:** Survey Development and Structure
## **• C.2:** Scoring Methodology
## **• C.3:** Reliability Analysis

#### **In the .Pdf output file you may find only the outputs generated by the analysis code, in order to keep the supplementary files as concise as possible. However the full code is available on https://github.com/Rezvani-S/Costly-Beauty-ShoeStudy.git**



## C.1 Survey Development and Structure

### C.1.1 Rationale and Objectives

The present study investigated the effects of trait exaggeration (supernormal stimuli enhancement of preferred features vs. non-enhanced features) and product cost (luxury vs. economy) on perceptions of attractiveness and wealth. The study used appearance modification items as stimuli, specifically high-heeled shoes and lipstick, in both luxury and economy variants.

A critical component of this investigation required participants to accurately distinguish luxury brands from economy brands. While general fashion knowledge might indicate familiarity with brands, it does not necessarily capture the specific ability to recognize and categorize brands according to their luxury versus economy positioning. Existing fashion knowledge measures (Flynn & Goldsmith, 1999) assess self-reported general fashion expertise but lack direct focus on the luxury-economy distinction that was essential to our research questions.

To address this gap, we developed a brief brand knowledge survey that combined self-report measures with accuracy checks of brand categorization. This dual approach allowed us to: (1) assess participants' subjective confidence in their brand knowledge, (2) measure their objective accuracy in distinguishing luxury from economy brands, and (3) examine their perceptions of brand-associated qualities relevant to luxury positioning (e.g., exclusivity, prestige, high quality).

The survey was designed to be administered as part of a larger laboratory study and needed to be brief enough to avoid participant fatigue while providing reliable measurement of brand knowledge relevant to luxury versus economy distinctions.

### C.1.2 Brand Selection

#### Selection Criteria

Brand selection followed a three-stage process designed to ensure both ecological validity and relevance to the study's research questions. First, we generated a comprehensive pool of internationally recognized brands across the luxury-economy spectrum that produce appearance modification products (including but not limited to shoes and cosmetics).

Second, we assembled a focus group of five young Czech females to assess brand recognition and market presence within the Czech Republic, which was the intended sample population for the study. The focus group evaluated each brand on:

- Recognition (whether they had heard of the brand)
- Market presence (availability in local stores and shopping districts)
- Clear positioning (whether the brand was unambiguously luxury or economy)
- Product range (whether the brand offered relevant appearance-modification products)

Third, based on focus group recommendations and verification of current market presence in Prague retail locations, we selected 10 brands that showed the highest recognition and clearest positioning within their respective categories.

#### Selected Brands

**Luxury brands (n = 5):**
- YSL
- Chanel
- Gucci
- Dior
- Givenchy

**Economy brands (n = 5):**
- H&M
- ZARA
- Primark
- Shein
- Sinsay

All selected brands maintained physical retail presence in Prague's major shopping districts and/or prominent placement in multi-brand retail stores, ensuring that our sample population would have had opportunity for brand exposure through both advertising and in-person retail encounters.

### C.1.3 Survey Structure

The Brand Knowledge Survey comprised four questions for each of the 10 brands (40 items total). The questions were designed to assess different facets of brand knowledge, progressing from subjective familiarity to objective categorization and detailed brand associations.

#### Question Format

For each brand, participants responded to the following four items:

**Q1. Brand Familiarity (Self-Report Knowledge)**
- Item wording: "How well do you know this brand?"
- Response scale: 7-point Likert scale (1 = *Not at all*, 7 = *Completely*)
- Purpose: Assess subjective confidence in brand knowledge

**Q2. Recognition Accuracy (Self-Report)**
- Item wording: "How accurately can you recognize a product of this brand?"
- Response scale: 7-point Likert scale (1 = *Not at all*, 7 = *Completely*)
- Purpose: Assess subjective confidence in ability to identify brand products

**Q3. Brand Positioning Classification**
- Item wording: "How would you rank this brand?"
- Response scale: 7-point scale (1 = *Economy*, 7 = *Luxury*)
- Purpose: Objective measure of brand categorization accuracy; serves as manipulation check for luxury/economy distinction

**Q4. Brand Quality Associations**
- Item wording: "What qualities do you associate with this brand? (Select all that apply)"
- Response options (multiple selection):
  - Exclusive
  - High Quality
  - Prestigious
  - Expensive
  - Authentic
  - Rich brand heritage
  - Aesthetic impression
- Purpose: Assess specific associations commonly linked to luxury brand positioning (Keller, 1993)

The four questions were developed based on established conceptualizations of brand knowledge (Aaker, 1991; Keller, 1993) and consumer subjective knowledge (Flynn & Goldsmith, 1999), with particular attention to dimensions relevant to luxury brand perception (e.g., exclusivity, prestige, quality associations).

### C.1.4 Survey Administration

#### Data Collection Procedure

The Brand Knowledge Survey was administered as part of a larger laboratory study conducted at Charles University. The survey was programmed in Qualtrics and presented on individual computer workstations in a controlled laboratory environment.

Participants completed the Brand Knowledge Survey along with two other brief preliminary assessments before proceeding to the main experimental tasks. The total time required for all preliminary surveys, including the Brand Knowledge Survey, was approximately 8-12 minutes.

#### Presentation Format

Brands were presented individually in randomized order to control for potential order effects. For each brand, participants saw the brand name and logo (where available) and responded to all four questions before proceeding to the next brand. This within-brand blocking was designed to reduce cognitive load by allowing participants to focus on one brand at a time rather than switching between brands for different questions.

#### Sample Characteristics

The final sample consisted of N = 297 participants. All participants were:

- Enrolled university students at Charles University
- Residents of the Czech Republic
- Fluent in Czech language (survey was administered in Czech)
- Provided informed consent prior to participation
- Received course credit or monetary compensation for participation

#### Relationship to Main Study

The Brand Knowledge Survey served as a preliminary assessment administered prior to the main experimental manipulation. Survey data were used to:

1. Verify that participants could accurately distinguish luxury from economy brands (manipulation check)
2. Assess individual differences in brand knowledge that might moderate responses to experimental stimuli
3. Identify any participants with atypical brand perception patterns that might indicate inattentive responding

Participants proceeded to the main experimental tasks regardless of their brand knowledge scores, as the survey was designed for measurement and validation purposes rather than as a screening tool.

---

## C.2 Scoring Methodology

### C.2.1 Brand Knowledge Score (BKS) Calculation

The Brand Knowledge Score (BKS) is a composite measure that integrates self-reported brand knowledge (Q1 and Q2) with classification accuracy (Q3) to create a three-level ordinal indicator of brand-specific knowledge. The BKS reflects both participants' subjective confidence in their knowledge and their objective ability to correctly categorize brands by positioning.

#### Calculation Formula

For each brand, the BKS is calculated as follows:

**Step 1: Calculate Self-Reported Knowledge**
$$\text{Self-Knowledge} = \frac{Q1 + Q2}{2}$$

**Step 2: Determine High Knowledge Status**
$$\text{High Knowledge} = \begin{cases} 
\text{TRUE} & \text{if Self-Knowledge} \geq 4 \\
\text{FALSE} & \text{if Self-Knowledge} < 4
\end{cases}$$

**Step 3: Determine Classification Accuracy**

For luxury brands (Brands 6-10):
$$\text{Correct Classification} = \begin{cases} 
\text{TRUE} & \text{if } Q3 \geq 5 \\
\text{FALSE} & \text{if } Q3 < 5
\end{cases}$$

For economy brands (Brands 1-5):
$$\text{Correct Classification} = \begin{cases} 
\text{TRUE} & \text{if } Q3 \leq 3 \\
\text{FALSE} & \text{if } Q3 > 3
\end{cases}$$

**Step 4: Assign BKS**
$$\text{BKS} = \begin{cases} 
3 & \text{if High Knowledge = TRUE AND Correct Classification = TRUE} \\
2 & \text{if High Knowledge = TRUE AND Correct Classification = FALSE} \\
1 & \text{if High Knowledge = FALSE}
\end{cases}$$

#### BKS Interpretation

- **BKS = 3 (High Accurate Knowledge)**: Participant reports high confidence in brand knowledge and correctly identifies the brand's positioning (luxury vs. economy). This indicates genuine brand knowledge.

- **BKS = 2 (High Inaccurate Knowledge)**: Participant reports high confidence in brand knowledge but incorrectly identifies the brand's positioning. This suggests either misperception of the brand or confusion with similar brands.

- **BKS = 1 (Low Knowledge)**: Participant reports low confidence in brand knowledge, regardless of classification accuracy. This indicates limited familiarity with the brand.

**Note:** Question 4 (brand quality associations) is not included in the BKS calculation. It serves as a supplementary measure for exploratory analysis of brand image perceptions.

### C.2.2 R Function for BKS Calculation

```{r bks-function, echo=TRUE}
#' Calculate Brand Knowledge Score (BKS)
#'
#' This function calculates the Brand Knowledge Score for each brand based on
#' self-reported knowledge (Q1, Q2) and classification accuracy (Q3).
#'
#' @param data A data frame containing brand survey responses
#' @param brand_col Name of the column containing brand identifiers (1-10)
#' @param q1_col Name of the column containing Q1 responses (brand familiarity)
#' @param q2_col Name of the column containing Q2 responses (recognition accuracy)
#' @param q3_col Name of the column containing Q3 responses (brand positioning)
#' @param luxury_brands Vector of brand numbers that are luxury brands (default: 6:10)
#' @param economy_brands Vector of brand numbers that are economy brands (default: 1:5)
#' @param knowledge_threshold Threshold for "high knowledge" (default: 4)
#' @param luxury_threshold Minimum Q3 value for correct luxury classification (default: 5)
#' @param economy_threshold Maximum Q3 value for correct economy classification (default: 3)
#'
#' @return Original data frame with added columns:
#'   - self_knowledge: Average of Q1 and Q2
#'   - high_knowledge: Logical indicating if self_knowledge >= threshold
#'   - correct_classification: Logical indicating correct brand positioning
#'   - bks: Brand Knowledge Score (1, 2, or 3)
#'
#' @examples
#' # Example with default parameters
#' data_with_bks <- calculate_bks(
#'   data = survey_data,
#'   brand_col = "Brand",
#'   q1_col = "Q1",
#'   q2_col = "Q2",
#'   q3_col = "Q3"
#' )
#'
#' # Example with custom thresholds
#' data_with_bks <- calculate_bks(
#'   data = survey_data,
#'   brand_col = "Brand",
#'   q1_col = "Q1",
#'   q2_col = "Q2",
#'   q3_col = "Q3",
#'   knowledge_threshold = 4.5,
#'   luxury_threshold = 5.5
#' )
#'
#' @export
calculate_bks <- function(data,
                          brand_col,
                          q1_col,
                          q2_col,
                          q3_col,
                          luxury_brands = 6:10,
                          economy_brands = 1:5,
                          knowledge_threshold = 4,
                          luxury_threshold = 5,
                          economy_threshold = 3) {
  
  # Check if required columns exist
  required_cols <- c(brand_col, q1_col, q2_col, q3_col)
  missing_cols <- setdiff(required_cols, names(data))
  if (length(missing_cols) > 0) {
    stop(paste("Missing required columns:", paste(missing_cols, collapse = ", ")))
  }
  
  # Calculate self-reported knowledge (average of Q1 and Q2)
  data$self_knowledge <- (data[[q1_col]] + data[[q2_col]]) / 2
  
  # Determine high knowledge status
  data$high_knowledge <- data$self_knowledge >= knowledge_threshold
  
  # Determine correct classification based on brand type
  data$correct_classification <- NA
  
  # For luxury brands: Q3 should be >= luxury_threshold
  luxury_mask <- data[[brand_col]] %in% luxury_brands
  data$correct_classification[luxury_mask] <- 
    data[[q3_col]][luxury_mask] >= luxury_threshold
  
  # For economy brands: Q3 should be <= economy_threshold
  economy_mask <- data[[brand_col]] %in% economy_brands
  data$correct_classification[economy_mask] <- 
    data[[q3_col]][economy_mask] <= economy_threshold
  
  # Calculate Brand Knowledge Score (BKS)
  data$bks <- ifelse(
    data$high_knowledge & data$correct_classification, 3,
    ifelse(data$high_knowledge & !data$correct_classification, 2, 1)
  )
  
  return(data)
}
```


```{r bks-example, echo=TRUE, eval=FALSE}
#### Function Usage Example

# Load your data (example with long format)
survey_data <- read.csv("Fashion and brand data-long.csv")

# Calculate BKS with default settings
survey_data_scored <- calculate_bks(
  data = survey_data,
  brand_col = "Brand",
  q1_col = "Q1_response",
  q2_col = "Q2_response",
  q3_col = "Q3_response"
)

# View the results
head(survey_data_scored[, c("Brand", "self_knowledge", "high_knowledge", 
                            "correct_classification", "bks")])

# Calculate participant-level summary statistics
participant_summary <- survey_data_scored %>%
  group_by(participant_id) %>%
  summarise(
    mean_bks = mean(bks, na.rm = TRUE),
    prop_high_knowledge = mean(high_knowledge, na.rm = TRUE),
    classification_accuracy = mean(correct_classification, na.rm = TRUE),
    n_brands = n()
  )
```

---

## C.3 Reliability Analysis

Internal consistency reliability was assessed using Cronbach's alpha coefficient. We examined reliability at multiple levels: overall survey, subscales by brand category (luxury vs. economy), subscales by question type, and individual brands to assess response pattern consistency.

### C.3.1 Data Preparation

```{r data-prep}
# Load data
raw_data <- read_csv("Fashion and brand data-long.csv")

# Reshape data to wide format for reliability analysis
wide_data <- raw_data %>%
  mutate(Bscore = as.numeric(Bscore)) %>%
  pivot_wider(
    id_cols = c(code, Fscore, sex, monthlyincome),
    names_from = c(Brand, Q),
    values_from = Bscore,
    names_prefix = "B"
  )

# Create brand type variable (1-5 = economy, 6-10 = luxury)
brand_type <- c(rep("economy", 5), rep("luxury", 5))
names(brand_type) <- 1:10

# Separate data by brand category for subscale analysis
economy_brands <- 1:5
luxury_brands <- 6:10
```

### C.3.2 Internal Consistency (Cronbach's Alpha)

#### Overall Survey Reliability

```{r overall-reliability, warning=FALSE}
# Calculate alpha for all 40 items (10 brands × 4 questions)
all_items <- wide_data %>% 
  select(starts_with("B"))

alpha_all_40 <- psych::alpha(all_items, check.keys = FALSE)

# Calculate alpha for Q1-Q3 only (30 items: 10 brands × 3 questions)
# These are the items used in BKS calculation
q123_items <- wide_data %>%
  select(matches("B[0-9]+_[123]$"))

alpha_q123 <- psych::alpha(all_items, check.keys = FALSE, warnings = FALSE)

# Create summary table
overall_reliability <- data.frame(
  Scale = c("All Items (Q1-Q4)", "Core Items (Q1-Q3 only)"),
  N_Items = c(40, 30),
  Cronbach_Alpha = c(
    round(alpha_all_40$total$raw_alpha, 3),
    round(alpha_q123$total$raw_alpha, 3)
  ),
  Mean = c(
    round(mean(as.matrix(all_items), na.rm = TRUE), 2),
    round(mean(as.matrix(q123_items), na.rm = TRUE), 2)
  ),
  SD = c(
    round(sd(as.matrix(all_items), na.rm = TRUE), 2),
    round(sd(as.matrix(q123_items), na.rm = TRUE), 2)
  )
)
```

**Table C1.** Overall Survey Internal Consistency

```{r table-overall}
kable(overall_reliability, 
      col.names = c("Scale", "N Items", "Cronbach's α", "Mean", "SD"),
      align = "lcccc",
      caption = "Table C1. Internal consistency reliability for the overall survey")
```

The overall survey demonstrated `r ifelse(overall_reliability$Cronbach_Alpha[1] >= 0.90, "excellent", ifelse(overall_reliability$Cronbach_Alpha[1] >= 0.80, "good", ifelse(overall_reliability$Cronbach_Alpha[1] >= 0.70, "acceptable", "questionable")))` internal consistency when all 40 items were included (α = `r overall_reliability$Cronbach_Alpha[1]`). When only the core items (Q1-Q3) used in Brand Knowledge Score calculation were analyzed, reliability remained `r ifelse(overall_reliability$Cronbach_Alpha[2] >= 0.90, "excellent", ifelse(overall_reliability$Cronbach_Alpha[2] >= 0.80, "good", ifelse(overall_reliability$Cronbach_Alpha[2] >= 0.70, "acceptable", "questionable")))` (α = `r overall_reliability$Cronbach_Alpha[2]`).

#### Subscale Reliability by Brand Category

```{r subscale-brand-category}
# Economy brands (Brands 1-5)
economy_items_all <- wide_data %>%
  select(matches(paste0("B[", paste(economy_brands, collapse = ""), "]_[1-4]$")))

alpha_economy_all <- psych::alpha(economy_items_all, check.keys = FALSE)

economy_items_q123 <- wide_data %>%
  select(matches(paste0("B[", paste(economy_brands, collapse = ""), "]_[1-3]$")))

alpha_economy_q123 <- psych::alpha(economy_items_q123, check.keys = FALSE)

# Luxury brands (Brands 6-10)
luxury_items_all <- wide_data %>%
  select(matches("B[6-9]_[1-4]$|B10_[1-4]$"))

alpha_luxury_all <- psych::alpha(luxury_items_all, check.keys = FALSE)

luxury_items_q123 <- wide_data %>%
  select(matches("B[6-9]_[1-3]$|B10_[1-3]$"))

alpha_luxury_q123 <- psych::alpha(luxury_items_q123, check.keys = FALSE)

# Create summary table
category_reliability <- data.frame(
  Category = rep(c("Economy Brands", "Luxury Brands"), each = 2),
  Items = rep(c("All Items (Q1-Q4)", "Core Items (Q1-Q3)"), 2),
  N_Items = c(20, 15, 20, 15),
  Cronbach_Alpha = c(
    round(alpha_economy_all$total$raw_alpha, 3),
    round(alpha_economy_q123$total$raw_alpha, 3),
    round(alpha_luxury_all$total$raw_alpha, 3),
    round(alpha_luxury_q123$total$raw_alpha, 3)
  ),
  Mean = c(
    round(mean(as.matrix(economy_items_all), na.rm = TRUE), 2),
    round(mean(as.matrix(economy_items_q123), na.rm = TRUE), 2),
    round(mean(as.matrix(luxury_items_all), na.rm = TRUE), 2),
    round(mean(as.matrix(luxury_items_q123), na.rm = TRUE), 2)
  ),
  SD = c(
    round(sd(as.matrix(economy_items_all), na.rm = TRUE), 2),
    round(sd(as.matrix(economy_items_q123), na.rm = TRUE), 2),
    round(sd(as.matrix(luxury_items_all), na.rm = TRUE), 2),
    round(sd(as.matrix(luxury_items_q123), na.rm = TRUE), 2)
  )
)
```

**Table C2.** Internal Consistency by Brand Category

```{r table-category}
kable(category_reliability,
      col.names = c("Category", "Items Included", "N Items", "Cronbach's α", "Mean", "SD"),
      align = "llcccc",
      caption = "Table C2. Internal consistency reliability for economy and luxury brand subscales")
```

#### Subscale Reliability by Question Type

```{r subscale-question-type}
# Q1: Brand familiarity (10 items)
q1_items <- wide_data %>% select(matches("B[0-9]+_1$"))
alpha_q1 <- psych::alpha(q1_items, check.keys = FALSE)

# Q2: Recognition accuracy (10 items)
q2_items <- wide_data %>% select(matches("B[0-9]+_2$"))
alpha_q2 <- psych::alpha(q2_items, check.keys = FALSE)

# Q3: Brand positioning (10 items)
q3_items <- wide_data %>% select(matches("B[0-9]+_3$"))
alpha_q3 <- psych::alpha(q3_items, check.keys = FALSE)

# Q1+Q2 combined: Self-reported knowledge (20 items)
q12_items <- wide_data %>% select(matches("B[0-9]+_[12]$"))
alpha_q12 <- psych::alpha(q12_items, check.keys = FALSE)

# Create summary table
question_reliability <- data.frame(
  Question_Type = c(
    "Q1: Brand Familiarity",
    "Q2: Recognition Accuracy", 
    "Q3: Brand Positioning",
    "Q1+Q2: Self-Knowledge Composite"
  ),
  N_Items = c(10, 10, 10, 20),
  Cronbach_Alpha = c(
    round(alpha_q1$total$raw_alpha, 3),
    round(alpha_q2$total$raw_alpha, 3),
    round(alpha_q3$total$raw_alpha, 3),
    round(alpha_q12$total$raw_alpha, 3)
  ),
  Mean = c(
    round(mean(as.matrix(q1_items), na.rm = TRUE), 2),
    round(mean(as.matrix(q2_items), na.rm = TRUE), 2),
    round(mean(as.matrix(q3_items), na.rm = TRUE), 2),
    round(mean(as.matrix(q12_items), na.rm = TRUE), 2)
  ),
  SD = c(
    round(sd(as.matrix(q1_items), na.rm = TRUE), 2),
    round(sd(as.matrix(q2_items), na.rm = TRUE), 2),
    round(sd(as.matrix(q3_items), na.rm = TRUE), 2),
    round(sd(as.matrix(q12_items), na.rm = TRUE), 2)
  )
)
```

**Table C3.** Internal Consistency by Question Type

```{r table-question}
kable(question_reliability,
      col.names = c("Question Type", "N Items", "Cronbach's α", "Mean", "SD"),
      align = "lcccc",
      caption = "Table C3. Internal consistency reliability for different question types across all brands")
```

### C.3.3 Brand-Level Response Pattern Analysis

To assess whether response patterns were consistent across brands or whether specific brands elicited atypical responses, we examined: (1) mean scores and standard deviations for each brand, (2) item-total correlations for each brand's items with the overall scale, and (3) alpha-if-item-deleted to identify brands that substantially reduce overall reliability.

```{r brand-pattern-analysis}
# Calculate statistics for each brand
brand_stats <- data.frame()

for (brand in 1:10) {
  # Get all items for this brand (Q1-Q3 only)
  brand_items <- wide_data %>% 
    select(matches(paste0("B", brand, "_[123]$")))
  
  # Calculate brand-level alpha
  brand_alpha <- psych::alpha(brand_items, check.keys = FALSE)
  
  # Calculate mean and SD across items
  brand_mean <- mean(as.matrix(brand_items), na.rm = TRUE)
  brand_sd <- sd(as.matrix(brand_items), na.rm = TRUE)
  
  # Calculate correlation with total score (excluding this brand)
  other_brands <- setdiff(1:10, brand)
  other_items <- wide_data %>%
    select(matches(paste0("B[", paste(other_brands, collapse = ""), "]_[123]$")))
  
  brand_total <- rowMeans(brand_items, na.rm = TRUE)
  other_total <- rowMeans(other_items, na.rm = TRUE)
  brand_total_cor <- cor(brand_total, other_total, use = "pairwise.complete.obs")
  
  brand_stats <- rbind(brand_stats, data.frame(
    Brand = brand,
    Brand_Type = brand_type[as.character(brand)],
    Alpha = round(brand_alpha$total$raw_alpha, 3),
    Mean = round(brand_mean, 2),
    SD = round(brand_sd, 2),
    Cor_with_Other_Brands = round(brand_total_cor, 3)
  ))
}

# Add column indicating if brand is problematic (low correlation or very different mean)
brand_stats$Pattern_Flag <- ifelse(
  brand_stats$Cor_with_Other_Brands < 0.30, 
  "Low correlation", 
  ""
)

# Calculate alpha if brand deleted
alphas_if_deleted <- data.frame()
for (brand in 1:10) {
  other_brands <- setdiff(1:10, brand)
  other_items <- wide_data %>%
    select(matches(paste0("B[", paste(other_brands, collapse = ""), "]_[123]$")))
  
  alpha_without <- psych::alpha(other_items, check.keys = FALSE)
  
  alphas_if_deleted <- rbind(alphas_if_deleted, data.frame(
    Brand_Deleted = brand,
    Alpha_Without = round(alpha_without$total$raw_alpha, 3),
    Alpha_Change = round(alpha_without$total$raw_alpha - alpha_q123$total$raw_alpha, 3)
  ))
}

brand_stats <- cbind(brand_stats, 
                     Alpha_if_Deleted = alphas_if_deleted$Alpha_Without,
                     Alpha_Change = alphas_if_deleted$Alpha_Change)
```

**Table C4.** Brand-Level Statistics and Response Pattern Analysis

```{r table-brand-patterns}
kable(brand_stats,
      col.names = c("Brand", "Type", "α", "Mean", "SD", 
                    "r with Others", "Flag", "α if Deleted", "Δα"),
      align = "clccccccc",
      caption = "Table C4. Response pattern analysis for each brand. Correlation with other brands indicates consistency of response patterns. Alpha change shows impact on overall reliability if brand is removed.") %>%
  kable_styling(font_size = 10)
```

#### Interpretation

```{r interpretation-text, results='asis'}
# Identify problematic brands
low_cor_brands <- brand_stats$Brand[brand_stats$Cor_with_Other_Brands < 0.30]
high_impact_brands <- brand_stats$Brand[abs(brand_stats$Alpha_Change) > 0.02]

if (length(low_cor_brands) > 0) {
  cat(paste0("Brand(s) ", paste(low_cor_brands, collapse = ", "), 
             " showed lower correlation with other brands (r < 0.30), suggesting somewhat distinct response patterns. "))
}

if (length(high_impact_brands) > 0) {
  # Determine if these brands are beneficial or detrimental
  beneficial_brands <- brand_stats$Brand[brand_stats$Alpha_Change < -0.02]
  detrimental_brands <- brand_stats$Brand[brand_stats$Alpha_Change > 0.02]
  
  if (length(beneficial_brands) > 0) {
    cat(paste0("Brand(s) ", paste(beneficial_brands, collapse = ", "), 
               " contributed substantially to overall reliability (Δα < -0.02), indicating these brands are particularly well-integrated into the scale. "))
  }
  
  if (length(detrimental_brands) > 0) {
    cat(paste0("Removing brand(s) ", paste(detrimental_brands, collapse = ", "), 
               " would improve overall reliability by more than 0.02, suggesting these brands may be less consistent with the overall measurement structure. "))
  }
}

# Overall pattern assessment
mean_cor <- mean(brand_stats$Cor_with_Other_Brands)
sd_cor <- sd(brand_stats$Cor_with_Other_Brands)

cat(paste0("\n\nOverall, brands showed ", 
           ifelse(mean_cor > 0.50, "strong", ifelse(mean_cor > 0.30, "moderate", "weak")),
           " consistency in response patterns (mean r = ", round(mean_cor, 2), 
           ", SD = ", round(sd_cor, 2), "), indicating that participants responded to brands in relatively consistent ways across the survey."))
```

### C.3.4 Reliability Interpretation

Following conventional guidelines for internal consistency interpretation (George & Mallery, 2003; Nunnally & Bernstein, 1994):

- α ≥ 0.90: Excellent
- α = 0.80–0.89: Good  
- α = 0.70–0.79: Acceptable
- α = 0.60–0.69: Questionable
- α < 0.60: Poor

```{r reliability-summary, results='asis'}
# Generate overall summary
cat("The Brand Knowledge Survey demonstrated ")
cat(ifelse(overall_reliability$Cronbach_Alpha[2] >= 0.90, "excellent", 
           ifelse(overall_reliability$Cronbach_Alpha[2] >= 0.80, "good", 
                  ifelse(overall_reliability$Cronbach_Alpha[2] >= 0.70, "acceptable", "questionable"))))
cat(" internal consistency across all measured dimensions. ")

# Economy vs luxury comparison
econ_alpha <- category_reliability$Cronbach_Alpha[2]  # Q1-Q3 for economy
lux_alpha <- category_reliability$Cronbach_Alpha[4]   # Q1-Q3 for luxury

if (abs(econ_alpha - lux_alpha) > 0.05) {
  cat(paste0("Reliability was ", 
             ifelse(econ_alpha > lux_alpha, "higher", "lower"),
             " for economy brands (α = ", econ_alpha, 
             ") compared to luxury brands (α = ", lux_alpha, "). "))
  
  # Check if both are still in "good" range (0.80-0.89)
  if (econ_alpha >= 0.80 && lux_alpha >= 0.80) {
    cat("However, both categories demonstrated good internal consistency, indicating adequate measurement quality across brand types. ")
  } else {
    cat("This suggests that participants may have had more consistent knowledge structures for one brand category. ")
  }
} else {
  cat(paste0("Reliability was comparable for economy (α = ", econ_alpha, 
             ") and luxury (α = ", lux_alpha, ") brands, ",
             "indicating consistent measurement quality across brand categories. "))
}

cat("\n\nAll question types demonstrated adequate internal consistency, supporting the multi-dimensional assessment of brand knowledge encompassing familiarity, recognition accuracy, and positioning classification.")
```

---

**References**

Aaker, D. A. (1991). *Managing brand equity: Capitalizing on the value of a brand name*. New York: Free Press.

Flynn, L. R., & Goldsmith, R. E. (1999). A short, reliable measure of subjective knowledge. *Journal of Business Research*, 46(1), 57-66.

George, D., & Mallery, P. (2003). *SPSS for Windows step by step: A simple guide and reference (4th ed.)*. Boston: Allyn & Bacon.

Keller, K. L. (1993). Conceptualizing, measuring, and managing customer-based brand equity. *Journal of Marketing*, 57(1), 1-22.

Nunnally, J. C., & Bernstein, I. H. (1994). *Psychometric theory (3rd ed.)*. New York: McGraw-Hill.
